### 2018-10-15 article/main.tex
Setting up development environment

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{booktabs}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{pgfplots}
\pgfplotsset{compat=1.12}
\usepackage[group-separator={,}]{siunitx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{breqn}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{wrapfig}
\usepackage{eufrak}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\lstdefinelanguage{JavaScript}{
	keywords={typeof, contract, struct, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
	keywordstyle=\color{blue}\bfseries,
	ndkeywords={class, export, boolean, throw, implements, import, this},
	ndkeywordstyle=\color{darkgray}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{purple}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=JavaScript,
	backgroundcolor=\color{lightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

\usepackage{graphicx}
\usepackage[
n,
operators,
advantage,
sets,
adversary,
landau,
probability,
notions,	
logic,
ff,
mm,
primitives,
events,
complexity,
asymptotics,
keys]{cryptocode}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}

\def\bitcoinA{%
	\leavevmode
	\vtop{\offinterlineskip %\bfseries
		\setbox0=\hbox{B}%
		\setbox2=\hbox to\wd0{\hfil\hskip-.03em
			\vrule height .3ex width .15ex\hskip .08em
			\vrule height .3ex width .15ex\hfil}
		\vbox{\copy2\box0}\box2}}

\DeclareMathOperator{\EX}{\mathbb{E}}% expected value
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

\renewcommand{\lstlistingname}{Figure}% Listing -> Algorithm
\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms

\title{MixEth: efficient trustless coin mixing service for Ethereum}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

\textbf{Note: this is an early-stage work-in-progress! Security proofs, implementation and many more are yet to come!} 
\begin{abstract}
Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to this transparent nature of the ledger, privacy is notably reduced. If the link between users' public key and their physical identity is exposed  their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain. It achieves strong notions of anonimity and is able to resist denial-of-service attacks.      
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}

\section{Introduction}
Bitcoin \cite{nakamoto2008bitcoin} and other cryptocurrencies are pseudonymous. Users' public keys are used as pseudonyms in these systems. Transactions essentially record a flow of cryptocurrency from one (or more) public keys to another public key (or more). Flow of cryptocurrency can be easily tracked due to the open and transparent nature of cryptocurrencies' transaction ledger. Moreover, coherent public keys, which are used by the same user, can be clustered merely by analyzing the ledger. Recently several tools and algorithms were proposed to diminish users' privacy (\cite{meiklejohn2013fistful},\cite{moser2013inquiry}, \cite{moreno2016listening}). Such deanomyzation attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.

One of the methods to increase users' privacy is coin mixing or tumbling. This technique provides \textit{k-anonymity} or \textit{plausible deniability}. The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys. This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.

Several coin mixing protocols were proposed in the literature both centralized (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}, \cite{heilman2017tumblebit}) and decentralized (\cite{maxwell2013coinjoin}, \cite{ruffing2014coinshuffle}, \cite{miximus2018}, \cite{meiklejohn2018mobius}, \cite{bissias2014sybil}). A major drawback of centralized coin mixing is that the availability of the tumbler is entirely dependent on the trusted party and in most cases theft prevention can not be guaranteed (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}). On the other hand decentralized tumblers achieve availability, theft prevention and satisfy strong notions of anonymity although they are considerably heavier computationally. In the following we will solely focus on the problem of coin mixing on Ethereum \cite{wood2014ethereum}.

The two major techniques to provide mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}. Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases. Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.

\textbf{Our contributions.} In this paper, we present MixEth, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity already achieved by previous proposals. MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas. Game-theoretical analysis of incentives in MixEth is also enclosed.

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK$ denote the set of public keys belonging to receivers.

We use games in definitions and proofs of security. At the end of each game, the main procedure of game \textsf{G} outputs a single bit. $\Pr(\textsf{G})$ denotes the probability that the output is $1$.
\subsection{Cryptographic keys in Ethereum}
Ethereum uses Elliptic Curve Cryptography (ECC) to secure users' funds. More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin. If a user wants to create an Ethereum address, first she needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite field $\mathbb{F}_{p}$. The corresponding public key will be $sG$. Note that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime. Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.

\subsection{Verifiable shuffle}

Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}. It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers. The output of the shuffle is another $k$ modular integers raised to the same secret exponent only known to the shuffler. The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly.

Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decisional Diffie-Hellman (DDH) problem. Therefore, Neff's verifiable shuffle can also be applied in groups over elliptic curves.

Verifiable shuffle can be used to shuffle a set of public keys, $PK=(s_{1}G,s_{2}G\dots,s_{k}G)$. Note that secret keys are not known to the shuffler.

\begin{enumerate}
	\item Shuffler commits to $C=cG$, publishes $$PK^*=(c(s_{\pi^{-1}(1)}G),c(s_{\pi^{-1}(2)}G),\dots,c({s_{\pi^{-1}(k)}}G))$$ where $\pi$ is a random permutation. Shuffler additionally computes and publishes a zero-knowledge proof about the correctness of the shuffle. This proof can be made non-interactive via the Fiat-Shamir heuristic. Let us call $C$ as the shuffling constant.
	\item Assuming the proof verifies users gain new public keys with respect to another generator element, namely $cG$.
\end{enumerate}

For verifying the proof one needs to compute $8k+5$ exponentiations, however later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.

So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.

\subsection{Chaum-Pedersen protocol}
The language $\mathcal{L}_{DDH}$ is defined to be the set of all tuples $(G,aG,bG,abG)$ where $G\in \mathbb{G}$ is of order prime $q$. The Chaum-Pedersen protocol enables a prover $\mathcal{P}$ to prove to a verifier $\mathcal{V}$ that $(G,A,B,C)\in\mathcal{L}_{DDH}$ in zero-knowledge for groups of prime order \cite{chaum1992wallet}. The protocol is organized as follows:

\begin{enumerate}
	\item $\mathcal{V}$: $s\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $commit(s)$ 
	\item $\mathcal{P}$: $r\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $y_1=rG$, $y_2=rB$.
	\item $\mathcal{V}$ opens commitment by sending $s$
	\item $\mathcal{P}$ sends $z=r+as \Mod{q}$
	\item $\mathcal{V}$ checks $zG=y_{1}sA \Mod{q} \land zB=y_{2}sC \Mod{q}$
\end{enumerate} 
Note that in the following a non-interactive version of this protocol will only be considered that can be achieved by applying the Fiat-Shamir heuristic.

\subsection{Ethereum}

\subsection{Ethereum account abstraction}
Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum. When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they can not do this from a fresh address, since it does not hold any ether. Since as of now only the sender of a transaction can pay for the gas fee, users can not withdraw their funds unless they ask someone to fund their fresh address.

Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}. EIP86 permits receivers of a transaction paying the gas fee. This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses. Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms. This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA). Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.

\section{Threat model}
\subsection{Participants and interactions}
In a decentralized tumbler, we have $3$ distinct entities: the tumbling smart contract, a set of senders and a set of receivers. A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys. Interactions of these entities can be summarized as follows:

$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit some ether to the receiver's public key.

After some period of time no more deposits are allowed to the tumbling contract. Let $PK_{0}$ denote the final set of public keys to be mixed. Every recipient of the mix is allowed to shuffle the public keys at most once:

$PK_{i+1},C_{i+1}^{*}, C_{i},CP_{i+1}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$. The permutation $\pi$ and the secret multiplier $c_{i}$ from the shuffling constant $C_{i}=c_{i}G$ should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled. Let us call $C^{*}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$. The shuffling accumulated constant is needed for receivers to collect their funds at the end of the final shuffling period. $CP_{i+1}$ is a Chaum-Pedersen zero-knowledge proof for the statement $(G,C_{i},C^{*}_{i},C^{*}_{i+1})\in\mathcal{L}_{DDH}$. All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.

$0\lor1\leftarrow 
ChallengeShuffle(PK_{i},C^{*}_{i},C_{i},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle done with $C_{i}=c_{i}G$ by giving a zero-knowledge proof that the following tuple is a DDH-tuple $(G,cG,sG,s(cG))$. If the proof verifies and $s(cG) \notin PK$, then the challenge is accepted, otherwise rejected.

$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds. Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather final shuffling accumulated constant.

\subsection{Security goals} \label{securitygoals}
We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}. We are going to assume that at most $k-2$ recipients are malicious ($k$ is the number of recipients). Otherwise, no meaningful notion of security can be achieved. Furthermore presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle. Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.

In this early version of the MixEth paper we only restrict ourselves to give informal security definitions.
\subsubsection{Anonymity}
\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest miners are sending funds, assuming that honest senders' deposits are indistinguishable.

\textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
\subsubsection{Availability}
It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer.
\subsubsection{Theft prevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. 
\section{MixEth}

\subsection{Overview}
MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
\subsection{Initializing the tumbler}

A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the following parameters:
\begin{itemize}
	\item $amt$: denomination of ether to be mixed;
	\item $senders[]$: list of all the sender addresses;
	\item $initPubKeys[]$: list of all the recipients' public keys;
	\item $shuffles[][]$: list of all the shuffles with corresponding Chaum-Pedersen proofs and values.
	\item $withdrawn[]$: list of all the shuffled public keys who had already withdrawn their coins.	
\end{itemize}

\subsection{Depositing period}
Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value are rejected.  
\subsection{Shuffling period}
After the depositing round, shuffling and challenging roundss are coming after in turns. Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone. If a challenge is accepted, then shuffler's deposit is lost, her shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle. In the course of a shuffle an honest shuffler should raise all the public keys to a secret exponent $c$ and then permute all the transformed public keys. Honest shuffler commits to $c$ by sending back to MixEth $C=cG$ and the shuffled public keys. Moreover, the shuffling accumulated constant is updated as well.

Shuffle is done off-chain, however the result and the Chaum-Pedersen proof is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.

\begin{algorithm}
\caption{Off-chain public key shuffling algorithm}\label{shufflingoffchain}
\begin{algorithmic}[1]
	\State $shuffledKeys \gets []$
	\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
	\State $C^*\leftarrow read\ from\ MixEth\ contract$
	\State $pubKeys\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
	\State $\pi\stackrel{\$}{\leftarrow}S_{|pubKeys|}$ 
	\For{$i=0;i<|pubKeys|;i++$}
	\State $shuffledKeys[\pi(i)]=c*pubKeys[i]$ 
	\EndFor
	\State $C^{*}_{new}=cC^{*}$
	\State $C=cG$
	\State $proof_{DDH}\leftarrow zkChaumPedersen(G,C,C^*,C^{*}_{new})$

\hspace*{\algorithmicindent} \textbf{Output:} $(shuffledKeys,C,C^*_{new},proof_{DDH})$ 
\end{algorithmic}   
\end{algorithm}
\subsection{Challenging period}
Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round. Let us assume that prior the shuffle recipient had public key $sG$ and shuffler committed to $C=cG$. In this case recipient should check that $sC$ is included in the shuffled public keys. Moreover all participants should check that the Chaum-Pedersen proof for the correctness of calculating the shuffling accumulated constant verifies or not.

\begin{algorithm}
	\caption{Off-chain verification algorithm for checking public key shuffling correctness}\label{verifyingshufflingoffchain}
	\hspace*{\algorithmicindent} \textbf{Input}$(shuffledKeys, C, C^{*}, proof_{DDH},s)$ \\
	\begin{algorithmic}[1]
		\State $pk=sC^*$
		\State $b\leftarrow verifyChaumPedersen(G,C,C^{*}_{previous},C^*,proof_{DDH})$  
		\State $b^'\leftarrow0$
		\If {$pk\in shuffledKeys$}
		\State $b^'\gets 1$
		\Else
		\State $b^'\gets 0$
		\EndIf
		\hspace*{\algorithmicindent} \textbf{Output:} $b\land b'$ 
	\end{algorithmic}   
\end{algorithm}
Note that every recipient should perform this check after each shuffling. Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves. This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.

\subsection{Withdrawing}
Let $C^*$be the final shuffling accumulated constant. For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$. The recipient can prove to MixEth that she knows $s$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
\subsection{MixEth pseudocode}

\medskip
\begin{lstlisting}[caption=MixEth contract pseudocode]
contract MixEth {
  uint256 amt;
  address[] senders;
  CurvePoint[] initPubKeys;
  Shuffle[] Shuffles;

  struct CurvePoint {
    uint256 x; //x coordinate
    uint256 y; //y coordinate
  }
  struct Shuffle { 
    //describes a shuffle
    // contains the shuffled pubKeys and Chaum-Pedersen zk proof
  }

  constructor() public {
   //sets amt
  }

  function uploadShuffle(Shuffle newShuffle) public {
    //needs to be ensured that recipient has not shuffled yet
    Shuffles.append(newShuffle);  
  }

  function challengeShuffle(CurvePoint[] challenge, uint256 i) public {
    bool accepted;
    //contract checks the correctness of the i-th shuffle which is stored at Shuffles[i]. If challenge accepted malicious shuffler's deposit is slashed.
    return accepted;
  }

  function withdraw() public {
    //receivers can withdraw funds at most once
  }   
}
\end{lstlisting}

\section{Security}
This section is going to demonstrate security proofs for the notions of security introduced in Section \ref{securitygoals}.

In this early version of the MixEth paper, we only restrict ourselves to give intuition and informal proofs for certain security properties.

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $i$ sends funds to the public key $s_{i}C^{*}$. This public key does not reveal any links to the original $s_{i}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to the Ethereum transaction ledger. 
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they broke discrete logarithm problem on the secp256k1 curve.
\begin{table}[H] 
	\caption{Security properties achieved by each coin mixing protocol.}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}

		\toprule
		\hline
		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
		\hline
		\midrule
		\textbf{Centralized} & & \\
		\midrule
		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
		\midrule
		\textbf{Decentralized}      &    &      \\
		\midrule
		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\cmark        \\
		Miximus \cite{miximus2018}&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

\section{Implementation}
\section{Related work}
As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$. In spite of this seemingly added complexity, we are confident that these 3 (deposit, shuffle, withdraw) transactions consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus. 
\begin{table}[H] 
\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol.}
\centering 
\begin{tabular}{lcc}

	\toprule
	&\#Off-chain messages& \#Transactions \\
	\midrule
	\textbf{Centralized} & & \\
	\midrule
	Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
	Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
	TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
	\midrule
	\textbf{Decentralized}      &    &      \\
	\midrule
	Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
	Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
	XIM \cite{bissias2014sybil} & 0      & 7       \\
	Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
	Miximus \cite{miximus2018} & 1 & 2 \\
	MixEth & 1 & 3 \\
	\bottomrule
\end{tabular}
\label{table:communicationcomplexity}
\end{table}

\section{Extensions and improvements}
MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround. A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant. MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.

\section{Conclusion} \label{conclusion}

\section{Future work}
We are going to implement and deploy MixEth on Ethereum and evaluate its performance. We are also going to give formal security proofs for the claimed security properties.  
An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround and upcoming EIP implementation and is ready to be deployed on present-day Ethereum. 
\bibliographystyle{plain}
\bibliography{sample}

\end{document}

### 2018-10-15 migrations/2_mixeth_migration.js

@@ -1,0 +1,6 @@
+var MixEth = artifacts.require("MixEth");
+
+module.exports = function(deployer) {
+  // deployment steps
+  deployer.deploy(MixEth,1000000000000000000); //1 ether
+};

### 2018-10-15 truffle.js

@@ -1,0 +1,23 @@
+/*
+ * NB: since truffle-hdwallet-provider 0.0.5 you must wrap HDWallet providers in a 
+ * function when declaring them. Failure to do so will cause commands to hang. ex:
+ * ```
+ * mainnet: {
+ *     provider: function() { 
+ *       return new HDWalletProvider(mnemonic, 'https://mainnet.infura.io/<infura-key>') 
+ *     },
+ *     network_id: '1',
+ *     gas: 4500000,
+ *     gasPrice: 10000000000,
+ *   },
+ */
+
+module.exports = {
+  networks: {
+    development: {
+      host: "127.0.0.1",
+      port: 8545,
+      network_id: "*" // Match any network id
+    }
+  }
+};

### 2018-10-15 shuffle/shuffle_generation.js
Minimal shuffle_generator is added

@@ -1,0 +1,50 @@
+const { randomBytes } = require('crypto')
+const sjcl = require('sjcl')
+var EC = require('elliptic').ec;
+var ec = new EC('secp256k1');
+let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8';
+
+
+function shuffleGenerator() {
+
+  let shufflingConstant = randomBytes(32);
+  var cG  = ec.keyFromPublic(G,'hex').getPublic().mul(shufflingConstant);
+
+  var pub1 = '04426a0c83526a2de14ea1641cd542443710ed8e5a64b20b26f3373d479f757e4a62eae6dac0cc98a9d80e24ca2c3cd7d46c461426c60e8176fe5f93fc3371cde0';
+  var pub2 = '04ee156de00515bb8e50a0aef16a5ee147a47a9af27f73160ed02388e88f189e12cb91664cdb3935833d3e43deacb037b9e16509b96007b094e884db2b67c2a316';
+  var pub3 = '04862c73f2b53a823869b1148ef5efa917f57a9e150f165171ef540b256ceb9814bc439622e1fda4596ee162dd66e73648cad1c45096260a7756f34334ce12acdc';
+  var pub4 = '04b01b5b5d0231e24b8ba1bfa829af07c9e2bead9630b672e7b544c25d735c80f2ef2eea998aa0a8109b2cc33bda7219648fec765d99a2e855ea036c25898fd348';
+  let shuffledPubKeys = [];
+  pubKeys=[pub1, pub2, pub3, pub4];
+
+  for(var i=0; i<pubKeys.length; i++) {
+    let pub = ec.keyFromPublic(pubKeys[i],'hex').getPublic();
+    console.log(i+": "+JSON.stringify(pub.mul(shufflingConstant)));
+    shuffledPubKeys.push(pub.mul(shufflingConstant));
+  }
+  shuffledArray = shuffle(shuffledPubKeys);
+
+  return {"shuffledPubkeys": shuffledArray,"cG":cG};
+}
+//Implementation of the Fischer-Yates-Knuth-Shuffle
+function shuffle(array) {
+  var currentIndex = array.length, temporaryValue, randomIndex;
+
+  // While there remain elements to shuffle...
+  while (0 !== currentIndex) {
+
+    // Pick a remaining element...
[…]

### 2018-10-15 article/main.tex
Typos fixed in article

@@
 It requires only $3$ on-chain transactions at most per user and $1$ off-chain.
-It achieves strong notions of anonimity and is able to resist denial-of-service attacks.
+It achieves strong notions of anonymity and is able to resist denial-of-service attacks.
 \end{abstract}
@@
 The cardinality of a finite set $X$ is denoted as $|X|$.
-In the following let $\lambda \in \mathbb{N}$ the security parameter and its unary representation is $1^{\lambda}$.
+In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$.
 If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$.
@@
 $tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds.
-Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather final shuffling accumulated constant.
+Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather the final shuffling accumulated constant.
 
@@
 \subsection{Withdrawing}
-Let $C^*$be the final shuffling accumulated constant.
+Let $C^*$ be the final shuffling accumulated constant.
 For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$.

### 2018-10-16 shuffle/chaum_pedersen_generator.js
Minimal Chaum-Pederson proof generator&verifier

@@ -6,27 +6,25 @@ var ec = new EC('secp256k1');
 let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
 let n = bigInt('FFFFFFFFFFFFFFFFFFFFFFFFFFFFFFFEBAAEDCE6AF48A03BBFD25E8CD0364141',16); //order of the secp256k1 group
 
-function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
+function proofGenerator(_A, _B, _C, shufflingConstant, _s) {
   let A = ec.keyFromPublic(_A,'hex').getPublic();
   let B = ec.keyFromPublic(_B,'hex').getPublic();
   let C = ec.keyFromPublic(_C,'hex').getPublic();
-  let y1 = ec.keyFromPublic(_y1,'hex').getPublic();
-  let y2 = ec.keyFromPublic(_y2,'hex').getPublic();
 
+  let r = randomBytes(32);
+  let rBigInt = bigInt(r.toString('hex'),16).mod(n);
+  let shufflingC = bigInt(shufflingConstant,16);
   let s =  bigInt(_s.toString(16),16);
 
-  let zG = ec.keyFromPublic(G,'hex').getPublic().mul(z);
-  let sAy1 = A.mul(s.toString(16)).add(y1);
-  let ax = zG.getX().eq(sAy1.getX());
-  let ay = zG.getY().eq(sAy1.getY());
+  console.log("s in natur: ", s);
 
-  let zB = B.mul(z);
-  let sCy2 = C.mul(s.toString(16)).add(y2);
-  let bx = zB.getX().eq(sCy2.getX());
-  let by = zB.getY().eq(sCy2.getY());
-  
-  return ax && ay && bx && by;
+  let y1 = ec.keyFromPublic(G,'hex').getPublic().mul(r);
+  let y2 = B.mul(r);
+
+  let z = rBigInt.add(shufflingC.multiply(s));
+
+  return {"y1":y1, "y2":y2, "z":z.mod(n).toString(16)};
 }
 
-module.exports = proofVerifier;
+module.exports = proofGenerator;
 require('make-runnable');

### 2018-10-16 shuffle/shuffle_generation.js

@@ -2,29 +2,30 @@ const { randomBytes } = require('crypto')
 const sjcl = require('sjcl')
 var EC = require('elliptic').ec;
 var ec = new EC('secp256k1');
-let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8';
+let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
 
 
-function shuffleGenerator() {
+function shuffleGenerator(prevCumulatedConstant) {
 
   let shufflingConstant = randomBytes(32);
-  var cG  = ec.keyFromPublic(G,'hex').getPublic().mul(shufflingConstant);
-
-  var pub1 = '04426a0c83526a2de14ea1641cd542443710ed8e5a64b20b26f3373d479f757e4a62eae6dac0cc98a9d80e24ca2c3cd7d46c461426c60e8176fe5f93fc3371cde0';
-  var pub2 = '04ee156de00515bb8e50a0aef16a5ee147a47a9af27f73160ed02388e88f189e12cb91664cdb3935833d3e43deacb037b9e16509b96007b094e884db2b67c2a316';
-  var pub3 = '04862c73f2b53a823869b1148ef5efa917f57a9e150f165171ef540b256ceb9814bc439622e1fda4596ee162dd66e73648cad1c45096260a7756f34334ce12acdc';
-  var pub4 = '04b01b5b5d0231e24b8ba1bfa829af07c9e2bead9630b672e7b544c25d735c80f2ef2eea998aa0a8109b2cc33bda7219648fec765d99a2e855ea036c25898fd348';
+  console.log("Shuffling constant: ", shufflingConstant.toString('hex'));
   let shuffledPubKeys = [];
-  pubKeys=[pub1, pub2, pub3, pub4];
 
+  let prevCumulatedC=ec.keyFromPublic(prevCumulatedConstant,'hex').getPublic();
+  currentCumulatedC=prevCumulatedC.mul(shufflingConstant);
+  let cG  = ec.keyFromPublic(G,'hex').getPublic().mul(shufflingConstant);
+
+  let pubKeys=generatePubKeys(6);
   for(var i=0; i<pubKeys.length; i++) {
[…]

### 2018-10-16 shuffle/chaum_pedersen_verifier.js
Off-chain code No.1. iteration is ready

@@ -6,6 +6,7 @@ var ec = new EC('secp256k1');
 let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
 let n = bigInt('FFFFFFFFFFFFFFFFFFFFFFFFFFFFFFFEBAAEDCE6AF48A03BBFD25E8CD0364141',16); //order of the secp256k1 group
 
+
 function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
   let A = ec.keyFromPublic(_A,'hex').getPublic();
   let B = ec.keyFromPublic(_B,'hex').getPublic();
@@ -24,7 +25,7 @@ function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
   let sCy2 = C.mul(s.toString(16)).add(y2);
   let bx = zB.getX().eq(sCy2.getX());
   let by = zB.getY().eq(sCy2.getY());
-  
+
   return ax && ay && bx && by;
 }
 

### 2018-10-16 shuffle/shuffle_generation.js

@@ -35,7 +35,7 @@ function shuffle(array) {
   while (0 !== currentIndex) {
 
     // Pick a remaining element...
-    randomIndex = Math.floor(Math.random() * currentIndex);
+    randomIndex = Math.floor(Math.random() * currentIndex); //needs to be replaced by cryptographically secure PRNG
     currentIndex -= 1;
 
     // And swap it with the current element.
@@ -50,7 +50,9 @@ function shuffle(array) {
 function generatePubKeys(i) {
   let publicKeys = [];
   for(var j=0;j<i;j++) {
-    let pubPoint = ec.genKeyPair().getPublic();
+    let keyPair = ec.genKeyPair();
+    let pubPoint = keyPair.getPublic();
+    console.log("Privkey: ",keyPair.getPrivate());
     pubKeyX=pubPoint.getX().toString('hex');
     pubKeyY=pubPoint.getY().toString('hex');
     let pub = ec.keyFromPublic('04'+pubKeyX+pubKeyY,'hex');

### 2018-10-16 shuffle/shuffle_verification.js

@@ -1,0 +1,35 @@
+const { randomBytes } = require('crypto')
+let proofVerifier =  require('./chaum_pedersen_verifier.js');
+const sjcl = require('sjcl')
+var EC = require('elliptic').ec;
+var bigInt = require("big-integer");
+var ec = new EC('secp256k1');
+var fs = require('fs');
+let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
+let n = bigInt('FFFFFFFFFFFFFFFFFFFFFFFFFFFFFFFEBAAEDCE6AF48A03BBFD25E8CD0364141',16); //order of the secp256k1 group
+
+function shuffleVerifier() {
+  var obj = JSON.parse(fs.readFileSync('./checkCorrectShuffle.json', 'utf8'));
+  let privKey = obj['privKey'];
+  let shuffledPubKeys = obj['shuffledPubKeys'];
+
+  let localShuffledPoint = ec.keyFromPublic(obj['C'],'hex').getPublic().mul(privKey);
+  let lShuffled = '04'+localShuffledPoint.getX().toString('hex')+localShuffledPoint.getY().toString('hex');
+  console.log("lShuffled: "+lShuffled);
+
+  let localPrivKeyPresent;
+  if(shuffledPubKeys.indexOf(lShuffled) > -1){
+    localPrivKeyPresent = true;
+   console.log('Exists: ' +lShuffled)
+  } else {
+   console.log('Does not exist! Shuffler is a bastard!')
+   localPrivKeyPresent = false;
+  }
+
+  let proofVerifies = proofVerifier(obj['A'], obj['B'], obj['C'], obj['s'], obj['y1'], obj['y2'], obj['z']);
+
+  return proofVerifies && localPrivKeyPresent;
+}
+
+module.exports = shuffleVerifier;
+require('make-runnable');

### 2018-10-18 migrations/2_MixEth_migration.js
Quick and dirty testing of EC library

@@ -1,0 +1,9 @@
+var MixEth = artifacts.require("MixEth");
+var EC = artifacts.require("./EC.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(EC);
+  deployer.link(EC, MixEth);
+
+  deployer.deploy(MixEth,1000000000000000000); //1 ether
+};

### 2018-10-18 migrations/2_mixeth_migration.js

@@ -1,6 +1,0 @@
-var MixEth = artifacts.require("MixEth");
-
-module.exports = function(deployer) {
-  // deployment steps
-  deployer.deploy(MixEth,1000000000000000000); //1 ether
-};

### 2018-10-18 migrations/3_ECLibraryTest_migration.js

@@ -1,0 +1,9 @@
+var ECLibraryTest = artifacts.require("ECLibraryTest");
+var EC = artifacts.require("./EC.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(EC);
+  deployer.link(EC, ECLibraryTest);
+
+  deployer.deploy(ECLibraryTest);
+};

### 2018-10-18 shuffle/chaum_pedersen_verifier.js

@@ -26,6 +26,9 @@ function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
   let bx = zB.getX().eq(sCy2.getX());
   let by = zB.getY().eq(sCy2.getY());
 
+  console.log("zGx", zG.getX());
+  console.log("zGy", zG.getY());
+
   return ax && ay && bx && by;
 }
 

### 2018-10-18 test/TestECLibrary.js

@@ -1,0 +1,136 @@
+let ECLibraryTest = artifacts.require("ECLibraryTest");
+let BigNumber = require('bignumber.js');
+
+
+let Gx = '0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798';
+let Gy = '0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8';
+//test vectors are taken from here: https://crypto.stackexchange.com/questions/784/are-there-any-secp256k1-ecdsa-test-examples-available
+contract('ECLibraryTest', function(accounts) {
+    let ContractInstance;
+    let resultx;
+    let resulty;
+    it("Scalar Multiplication: 1G", function() {
+        return ECLibraryTest.deployed().then(function(instance) {
+            ContractInstance = instance;
+            ContractInstance.mul('0x1');
+            return ContractInstance.hx.call();
+        }).then(function(xcoordinate) {
+            resultx = new BigNumber(xcoordinate).toString(16);
+            console.log("X result",resultx);
+            return ContractInstance.hy.call();
+        }).then(function(ycoordinate){
+          resulty = new BigNumber(ycoordinate).toString(16)
+           console.log("Y result",resulty);
+           assert.equal(('79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798').toLowerCase(),resultx,"X coordinate is incorrect");
+           assert.equal(('483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8').toLowerCase(),resulty,"Y coordinate is incorrect");
+        });
+    });
+
+    it("Scalar Multiplication: 5G", function() {
+        return ECLibraryTest.deployed().then(function(instance) {
+            ContractInstance = instance;
+            ContractInstance.mul('0x5');
+            return ContractInstance.hx.call();
+        }).then(function(xcoordinate) {
+            resultx = new BigNumber(xcoordinate).toString(16);
+            console.log("X result",resultx);
+            return ContractInstance.hy.call();
+        }).then(function(ycoordinate){
+          resulty = new BigNumber(ycoordinate).toString(16)
+           console.log("Y result",resulty);
[…]

### 2018-10-18 test/TestMixEth.js

@@ -1,0 +1,38 @@
+let MixEth = artifacts.require("MixEth");
+let BigNumber = require('bignumber.js');
+
+let Web3latest = require('web3');
+let web3latest = new Web3latest();
+
+
+//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
+//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
+
+         0x109b79ed37eda89312e61ccb2172ce3886b59d9b8d1d6045fff342e21deff9e46f670312d93d147b50c7c30fd9e5025728d95eb994ee1aee32e65222f7fb9da346ab42c7e866383c95e5556b17849640ea0bdc1c99a02220566f118dfaa88f3e835b6b785a3546426ec342c31dce0e7c1c140c3fc00a55d6390cf5abd3757dfb
+
+contract('MixEth', function(accounts) {
+    let ContractInstance;
+    it("Chaum Pedersen Proof Verification", function() {
+        return MixEth.deployed().then(function(instance) {
+            ContractInstance = instance; //ABCsy1y2z
+            ContractInstance.verifyChaumPedersenPart1(
+            '0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8', '0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
+            '0xfc08d6353e48d7e1f8efbf07dd551b531b66b9a167f03058df012930872bd0af', '0xf6b61257dc6b0ecfc4c75a28ba16c75294e8bed048cbc33ae9607e0fef8db0e7',
+            '0x43543543',
+            '0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe'
+          );
+            /*ContractInstance.verifyChaumPedersen(
+             {x:'0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8', y:'0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296'},
[…]

### 2018-10-18 migrations/2_ChaumPedersenVerifier_migration.js
On-chain ChaumPedersen Verifier is added

@@ -1,0 +1,9 @@
+var ChaumPedersenVerifier = artifacts.require("ChaumPedersenVerifier");
+var EC = artifacts.require("./EC.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(EC);
+  deployer.link(EC, ChaumPedersenVerifier);
+
+  deployer.deploy(ChaumPedersenVerifier);
+};

### 2018-10-18 migrations/2_MixEth_migration.js

@@ -1,9 +1,0 @@
-var MixEth = artifacts.require("MixEth");
-var EC = artifacts.require("./EC.sol");
-
-module.exports = function(deployer) {
-  deployer.deploy(EC);
-  deployer.link(EC, MixEth);
-
-  deployer.deploy(MixEth,1000000000000000000); //1 ether
-};

### 2018-10-18 test/TestChaumPedersen.js

@@ -1,0 +1,31 @@
+let ChaumPedersenVerifier = artifacts.require("ChaumPedersenVerifier");
+let BigNumber = require('bignumber.js');
+
+let Web3latest = require('web3');
+let web3latest = new Web3latest();
+
+
+//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
+//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
+
+//0x109b79ed37eda89312e61ccb2172ce3886b59d9b8d1d6045fff342e21deff9e46f670312d93d147b50c7c30fd9e5025728d95eb994ee1aee32e65222f7fb9da346ab42c7e866383c95e5556b17849640ea0bdc1c99a02220566f118dfaa88f3e835b6b785a3546426ec342c31dce0e7c1c140c3fc00a55d6390cf5abd3757dfb
+
+contract('ChaumPedersenVerifier', function(accounts) {
+    let ContractInstance;
+    it("Chaum Pedersen Proof Verification", function() {
+       return ChaumPedersenVerifier.deployed().then(function(instance) {
+        ContractInstance = instance;
+         ContractInstance.verifyChaumPedersen(
+             ['0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
+             '0x612e8ba3c5a6adc4f69c1c8aa304c3f1fdbc053a5feaa949189b80ec439ffa40','0x259ff66f1678eae6b9e23f30f59d1349d027a04eb3a8f4e452709deb40f32b17',
+             '0x1b5839e49e2d6ef32e38aa60cca86e5534cb5bc7978ad3b99dae5197d95512b4','0x583b4d5d798a872bfa7dd9a665b6acf54a250fb47f3aa86053e3c546bf77597f',
+              '0x43543543',
+             '0xfc08d6353e48d7e1f8efbf07dd551b531b66b9a167f03058df012930872bd0af','0xf6b61257dc6b0ecfc4c75a28ba16c75294e8bed048cbc33ae9607e0fef8db0e7',
[…]

### 2018-10-18 test/TestECLibrary.js

@@ -133,4 +133,19 @@ contract('ECLibraryTest', function(accounts) {
            assert.equal(('85E89BC037945D93B343083B5A1C86131A01F60C50269763B570C854E5C09B7A').toLowerCase(),resulty,"Y coordinate is incorrect");
         });
     });
+
+    it("Scalar Multiplication: whatever", function() {
+        return ECLibraryTest.deployed().then(function(instance) {
+            ContractInstance = instance;
+            ContractInstance.mul('0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe');
+            return ContractInstance.hx.call();
+        }).then(function(xcoordinate) {
+            resultx = new BigNumber(xcoordinate).toString(16);
+            console.log("X result",resultx);
+            return ContractInstance.hy.call();
+        }).then(function(ycoordinate){
+          resulty = new BigNumber(ycoordinate).toString(16)
+           console.log("Y result",resulty);
+        });
+    });
 });

### 2018-10-18 test/TestMixEth.js

@@ -1,38 +1,0 @@
-let MixEth = artifacts.require("MixEth");
-let BigNumber = require('bignumber.js');
-
-let Web3latest = require('web3');
-let web3latest = new Web3latest();
-
-
-//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
-//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
-
-         0x109b79ed37eda89312e61ccb2172ce3886b59d9b8d1d6045fff342e21deff9e46f670312d93d147b50c7c30fd9e5025728d95eb994ee1aee32e65222f7fb9da346ab42c7e866383c95e5556b17849640ea0bdc1c99a02220566f118dfaa88f3e835b6b785a3546426ec342c31dce0e7c1c140c3fc00a55d6390cf5abd3757dfb
-
-contract('MixEth', function(accounts) {
-    let ContractInstance;
-    it("Chaum Pedersen Proof Verification", function() {
-        return MixEth.deployed().then(function(instance) {
-            ContractInstance = instance; //ABCsy1y2z
-            ContractInstance.verifyChaumPedersenPart1(
-            '0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8', '0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
-            '0xfc08d6353e48d7e1f8efbf07dd551b531b66b9a167f03058df012930872bd0af', '0xf6b61257dc6b0ecfc4c75a28ba16c75294e8bed048cbc33ae9607e0fef8db0e7',
-            '0x43543543',
-            '0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe'
-          );
-            /*ContractInstance.verifyChaumPedersen(
-             {x:'0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8', y:'0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296'},
[…]

### 2018-10-18 test/TestChaumPedersen.js
Polished contract for Chaum-Pedersen proof verification

@@ -8,8 +8,6 @@ let web3latest = new Web3latest();
 //zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
 //zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
 
-//0x109b79ed37eda89312e61ccb2172ce3886b59d9b8d1d6045fff342e21deff9e46f670312d93d147b50c7c30fd9e5025728d95eb994ee1aee32e65222f7fb9da346ab42c7e866383c95e5556b17849640ea0bdc1c99a02220566f118dfaa88f3e835b6b785a3546426ec342c31dce0e7c1c140c3fc00a55d6390cf5abd3757dfb
-
 contract('ChaumPedersenVerifier', function(accounts) {
     let ContractInstance;
     it("Chaum Pedersen Proof Verification", function() {
@@ -19,12 +17,14 @@ contract('ChaumPedersenVerifier', function(accounts) {
              ['0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
              '0x612e8ba3c5a6adc4f69c1c8aa304c3f1fdbc053a5feaa949189b80ec439ffa40','0x259ff66f1678eae6b9e23f30f59d1349d027a04eb3a8f4e452709deb40f32b17',
              '0x1b5839e49e2d6ef32e38aa60cca86e5534cb5bc7978ad3b99dae5197d95512b4','0x583b4d5d798a872bfa7dd9a665b6acf54a250fb47f3aa86053e3c546bf77597f',
-              '0x43543543',
+              '43543543',
              '0xfc08d6353e48d7e1f8efbf07dd551b531b66b9a167f03058df012930872bd0af','0xf6b61257dc6b0ecfc4c75a28ba16c75294e8bed048cbc33ae9607e0fef8db0e7',
              '0xdb5d6f09b5ee1293a1194e3adf4108ffe841008b963b72f38b8faef83ade9323','0xaa92d8433c8bd6507b4663590fefd34b1c2e0d7a49ca1060ec870157b2b8e97a',
               '0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe']);
             return ContractInstance.testIng.call();
         }).then(function(verified) {
[…]

### 2018-10-19 shuffle/chaum_pedersen_verifier.js
Efficient On-chain Chaum-Pedersen Verifier using Vitalik's trick

@@ -17,17 +17,28 @@ function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
   let s =  bigInt(_s.toString(16),16);
 
   let zG = ec.keyFromPublic(G,'hex').getPublic().mul(z);
+  console.log("zGx", zG.getX());
+  console.log("zGy", zG.getY());
+
   let sAy1 = A.mul(s.toString(16)).add(y1);
+  console.log("sAx",A.mul(s.toString(16)).getX());
+  console.log("sAy",A.mul(s.toString(16)).getY());
+
   let ax = zG.getX().eq(sAy1.getX());
   let ay = zG.getY().eq(sAy1.getY());
 
   let zB = B.mul(z);
+  console.log("zBx", zB.getX());
+  console.log("zBy", zB.getY());
+
   let sCy2 = C.mul(s.toString(16)).add(y2);
+  console.log("sCx",C.mul(s.toString(16)).getX());
+  console.log("sCy",C.mul(s.toString(16)).getY());
+
   let bx = zB.getX().eq(sCy2.getX());
   let by = zB.getY().eq(sCy2.getY());
 
-  console.log("zGx", zG.getX());
-  console.log("zGy", zG.getY());
+
 
   return ax && ay && bx && by;
 }

### 2018-10-19 test/TestChaumPedersen.js

@@ -10,22 +10,26 @@ let web3latest = new Web3latest();
 
 contract('ChaumPedersenVerifier', function(accounts) {
     let ContractInstance;
-    it("Chaum Pedersen Proof Verification", function() {
-       return ChaumPedersenVerifier.deployed().then(function(instance) {
+    it("Chaum Pedersen Proof Verification",  async () => {
+       return ChaumPedersenVerifier.deployed().then( async function(instance) {
         ContractInstance = instance;
-         ContractInstance.verifyChaumPedersen(
+         let txReceipt= await ContractInstance.verifyChaumPedersen(
              ['0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
              '0x612e8ba3c5a6adc4f69c1c8aa304c3f1fdbc053a5feaa949189b80ec439ffa40','0x259ff66f1678eae6b9e23f30f59d1349d027a04eb3a8f4e452709deb40f32b17',
              '0x1b5839e49e2d6ef32e38aa60cca86e5534cb5bc7978ad3b99dae5197d95512b4','0x583b4d5d798a872bfa7dd9a665b6acf54a250fb47f3aa86053e3c546bf77597f',
               '43543543',
              '0xfc08d6353e48d7e1f8efbf07dd551b531b66b9a167f03058df012930872bd0af','0xf6b61257dc6b0ecfc4c75a28ba16c75294e8bed048cbc33ae9607e0fef8db0e7',
              '0xdb5d6f09b5ee1293a1194e3adf4108ffe841008b963b72f38b8faef83ade9323','0xaa92d8433c8bd6507b4663590fefd34b1c2e0d7a49ca1060ec870157b2b8e97a',
-              '0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe']);
+              '0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe',
+              '0x3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0','0x7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5',
[…]

### 2018-10-19 test/TestECLibrary.js

@@ -16,11 +16,9 @@ contract('ECLibraryTest', function(accounts) {
             return ContractInstance.hx.call();
         }).then(function(xcoordinate) {
             resultx = new BigNumber(xcoordinate).toString(16);
-            console.log("X result",resultx);
             return ContractInstance.hy.call();
         }).then(function(ycoordinate){
           resulty = new BigNumber(ycoordinate).toString(16)
-           console.log("Y result",resulty);
            assert.equal(('79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798').toLowerCase(),resultx,"X coordinate is incorrect");
            assert.equal(('483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8').toLowerCase(),resulty,"Y coordinate is incorrect");
         });
@@ -28,16 +26,13 @@ contract('ECLibraryTest', function(accounts) {
 
     it("Scalar Multiplication: 5G", function() {
         return ECLibraryTest.deployed().then(function(instance) {
-            ContractInstance = instance;
             ContractInstance.mul('0x5');
             return ContractInstance.hx.call();
         }).then(function(xcoordinate) {
             resultx = new BigNumber(xcoordinate).toString(16);
-            console.log("X result",resultx);
             return ContractInstance.hy.call();
         }).then(function(ycoordinate){
           resulty = new BigNumber(ycoordinate).toString(16)
-           console.log("Y result",resulty);
            assert.equal(('2F8BDE4D1A07209355B4A7250A5C5128E88B84BDDC619AB7CBA8D569B240EFE4').toLowerCase(),resultx,"X coordinate is incorrect");
            assert.equal(('D8AC222636E5E3D6D4DBA9DDA6C9C426F788271BAB0D6840DCA87D3AA6AC62D6').toLowerCase(),resulty,"Y coordinate is incorrect");
         });
@@ -45,16 +40,13 @@ contract('ECLibraryTest', function(accounts) {
 
     it("Scalar Multiplication: 20G", function() {
         return ECLibraryTest.deployed().then(function(instance) {
-            ContractInstance = instance;
             ContractInstance.mul('0x14');
             return ContractInstance.hx.call();
         }).then(function(xcoordinate) {
             resultx = new BigNumber(xcoordinate).toString(16);
-            console.log("X result",resultx);
[…]

### 2018-10-23 article/main.tex
Minimal Chaum-Pederson proof generator&verifier
Protocol update

@@
 	\item $\mathcal{P}$ sends $z=r+as \Mod{q}$
-	\item $\mathcal{V}$ checks $zG=y_{1}sA \Mod{q} \land zB=y_{2}sC \Mod{q}$
+	\item $\mathcal{V}$ checks $zG=y_{1}+sA \Mod{q} \land zB=y_{2}+sC \Mod{q}$
 \end{enumerate} 
@@
 After some period of time no more deposits are allowed to the tumbling contract.
-Let $PK_{0}$ denote the final set of public keys to be mixed.
+Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
 Every recipient of the mix is allowed to shuffle the public keys at most once:
 
-$PK_{i+1},C_{i+1}^{*}, C_{i},CP_{i+1}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
-The permutation $\pi$ and the secret multiplier $c_{i}$ from the shuffling constant $C_{i}=c_{i}G$ should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
+$PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
 Let us call $C^{*}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
-The shuffling accumulated constant is needed for receivers to collect their funds at the end of the final shuffling period.
-$CP_{i+1}$ is a Chaum-Pedersen zero-knowledge proof for the statement $(G,C_{i},C^{*}_{i},C^{*}_{i+1})\in\mathcal{L}_{DDH}$.
+The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period.
+The permutation $\pi$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
 All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.
@@
 $0\lor1\leftarrow 
-ChallengeShuffle(PK_{i},C^{*}_{i},C_{i},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle done with $C_{i}=c_{i}G$ by giving a zero-knowledge proof that the following tuple is a DDH-tuple $(G,cG,sG,s(cG))$.
-If the proof verifies and $s(cG) \notin PK$, then the challenge is accepted, otherwise rejected.
+ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving two Chaum-Pedersen zero-knowledge proofs that the following two tuples are DDH-tuples: $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i-1})$ and $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i})$.
+If both of the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
+These proofs and checks allow one to check that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
 
 $tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds.
-Note that here the transaction will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather the final shuffling accumulated constant.
+Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather the final shuffling accumulated constant.
 
@@
 	\item $initPubKeys[]$: list of all the recipients' public keys;
-	\item $shuffles[][]$: list of all the shuffles with corresponding Chaum-Pedersen proofs and values.
+	\item $shuffles[][]$: list of all the shuffles with corresponding shuffling accumulated constants.
 	\item $withdrawn[]$: list of all the shuffled public keys who had already withdrawn their coins.	
@@
 \subsection{Shuffling period}
-After the depositing round, shuffling and challenging roundss are coming after in turns.
+After the depositing round, shuffling and challenging rounds are coming after in turns.
 Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
@@
 In the course of a shuffle an honest shuffler should raise all the public keys to a secret exponent $c$ and then permute all the transformed public keys.
-Honest shuffler commits to $c$ by sending back to MixEth $C=cG$ and the shuffled public keys.
-Moreover, the shuffling accumulated constant is updated as well.
+Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
 
-Shuffle is done off-chain, however the result and the Chaum-Pedersen proof is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
 
 \begin{algorithm}
-\caption{Off-chain public key shuffling algorithm}\label{shufflingoffchain}
+\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
 \begin{algorithmic}[1]
-	\State $shuffledKeys \gets []$
+	\State $PK_{i} \gets []$
 	\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
-	\State $C^*\leftarrow read\ from\ MixEth\ contract$
-	\State $pubKeys\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
-	\State $\pi\stackrel{\$}{\leftarrow}S_{|pubKeys|}$ 
-	\For{$i=0;i<|pubKeys|;i++$}
-	\State $shuffledKeys[\pi(i)]=c*pubKeys[i]$ 
+	\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
+	\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
+	\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
+	\For{$j=0;j<|PK_{i-1}|;j++$}
+	\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
 	\EndFor
-	\State $C^{*}_{new}=cC^{*}$
-	\State $C=cG$
-	\State $proof_{DDH}\leftarrow zkChaumPedersen(G,C,C^*,C^{*}_{new})$
+	\State $C^{*}_{i}=cC^{*}_{i-1}$
 
-\hspace*{\algorithmicindent} \textbf{Output:} $(shuffledKeys,C,C^*_{new},proof_{DDH})$ 
+\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i})$ 
 \end{algorithmic}   
@@
 Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round.
-Let us assume that prior the shuffle recipient had public key $sG$ and shuffler committed to $C=cG$.
-In this case recipient should check that $sC$ is included in the shuffled public keys.
-Moreover all participants should check that the Chaum-Pedersen proof for the correctness of calculating the shuffling accumulated constant verifies or not.
+These are the actions Bob as a receiver needs to perform to check the correctness of the shuffle at $i$th round if Bob has secret key $s_{B}$.
+In this case Bob should check whether $s_{B}C^{*}_{i} \in PK_{i}$ or not.
+If not, Bob should prove to MixEth that the $i$th round is indeed the first round, where the shuffled public key corresponding to $s_{B}$ is compromised.
+The first Chaum-Pedersen ensures that the integrity of the shuffled public key in round $i-1$st is intact, while the second proves that it is compromised in round $i$th.
 
 \begin{algorithm}
-	\caption{Off-chain verification algorithm for checking public key shuffling correctness}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(shuffledKeys, C, C^{*}, proof_{DDH},s)$ \\
+	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(G,s_{B}G,C^{*}_{i-1},s_{B}C^{*}_{i-1}), proof_{DDH}(G,s_{B}G,C^{*}_{i},s_{B}C^{*}_{i})$ \\
 	\begin{algorithmic}[1]
-		\State $pk=sC^*$
-		\State $b\leftarrow verifyChaumPedersen(G,C,C^{*}_{previous},C^*,proof_{DDH})$  
-		\State $b^'\leftarrow0$
-		\If {$pk\in shuffledKeys$}
-		\State $b^'\gets 1$
+		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(G,s_{B}G,C^{*}_{i-1},s_{B}C^{*}_{i-1})$ 
+		\State $b^{'}\leftarrow verifyChaumPedersen(proof_{DDH}(G,s_{B}G,C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b^*\leftarrow0$
+		\If {$b \land b^{'} \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
+		\State $b^*\gets 1$
 		\Else
-		\State $b^'\gets 0$
+		\State $b^*\gets 0$
 		\EndIf
-		\hspace*{\algorithmicindent} \textbf{Output:} $b\land b'$ 
+		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
 	\end{algorithmic}   
@@
     //describes a shuffle
-    // contains the shuffled pubKeys and Chaum-Pedersen zk proof
+    // contains the shuffled pubKeys and the shuffling accumulated constant
   }
@@
 \subsection{Recipient anonymity}
-The withdrawing transaction for recipient $i$ sends funds to the public key $s_{i}C^{*}$.
-This public key does not reveal any links to the original $s_{i}G$ in case if at least one honest sender shuffled and the DDH assumption holds.
+The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$.
+This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds.
 Adversary can only distinguish between honest recipients public keys with negligible probability.

### 2018-10-23 article/main.tex
Challenging transaction in article updated

@@
 Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript.
-Let $PK$ denote the set of public keys belonging to receivers.
+Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.
 
@@
 ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving two Chaum-Pedersen zero-knowledge proofs that the following two tuples are DDH-tuples: $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i-1})$ and $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i})$.
-If both of the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
+If both of the proofs are verified and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
 These proofs and checks allow one to check that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
@@
 
+We also highlight the necessity of two Chaum-Pedersen proofs for challenging a shuffle.
+If only one Chaum-Pedersen proof is enclosed in the challenging transaction, MixEth can not be sure that the integrity of the problematic public key indeed in the $i$th shuffling round was compromised.
+This could be abused by a malicious shuffler who deliberately corrupts their own public key in their shuffling round and afterwards they could blame any other shuffler for the compromise.
+This could have been led to losses of honest recipients' deposit.
+
 \subsection{Withdrawing}
 Let $C^*$ be the final shuffling accumulated constant.
-For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$.
-The recipient can prove to MixEth that she knows $s$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
+For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*$.
+The recipient can prove to MixEth that she knows secret key $s_{B}$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
 \subsection{MixEth pseudocode}

### 2018-10-24 migrations/4_MixEth_migration.js
MixEth contract skeleton + deposit function added

@@ -1,0 +1,9 @@
+var MixEth = artifacts.require("MixEth");
+var EC = artifacts.require("./EC.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(EC);
+  deployer.link(EC, MixEth);
+
+  deployer.deploy(MixEth);
+};

### 2018-10-24 test/TestMixEth.js

@@ -1,0 +1,35 @@
+let MixEth = artifacts.require("MixEth");
+let BigNumber = require('bignumber.js');
+let abi = require('ethereumjs-abi');
+
+let Web3latest = require('web3');
+let web3latest = new Web3latest();
+
+
+//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
+//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
+
+contract('MixEth', function(accounts) {
+    let ContractInstance;
+    let shuffler = '0xafdefc1937ae294c3bd55386a8b9775539d81653';
+    let pubKeyX = '0x6cb84859e85b1d9a27e060fdede38bb818c93850fb6e42d9c7e4bd879f8b9153';
+    let pubKeyY = '0xfd94ed48e1f63312dce58f4d778ff45a2e5abb08a39c1bc0241139f5e54de7df';
+    it("Depositting to a public key", function() {
+        return MixEth.deployed().then(async function(instance) {
+            ContractInstance = instance;
+            let txReceipt = await ContractInstance.deposit(
+            pubKeyX,
+            pubKeyY,
+            {value:1000000000000000000});
+            return ContractInstance.initPubKeys.call(0);
+        }).then(function(pubKey) {
+            let xcoordinate = new BigNumber(pubKey[0]).toString(16)
+            let ycoordinate = new BigNumber(pubKey[1]).toString(16)
+            assert.equal(xcoordinate, '6cb84859e85b1d9a27e060fdede38bb818c93850fb6e42d9c7e4bd879f8b9153', "X coordinate is not correct");
+            assert.equal(ycoordinate, 'fd94ed48e1f63312dce58f4d778ff45a2e5abb08a39c1bc0241139f5e54de7df', "Y coordinate is not correct");
+            return ContractInstance.shufflers.call(shuffler);
+        }).then(function(shufflerAddressIsSet) {
+            assert.equal(true, shufflerAddressIsSet, "Shuffler address is not correct");
+        });
+    });
+  });

### 2018-10-25 article/main.tex
Updated challenge tx design thanks to Dmitry Khovratovich

@@
 $0\lor1\leftarrow 
-ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving two Chaum-Pedersen zero-knowledge proofs that the following two tuples are DDH-tuples: $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i-1})$ and $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i})$.
-If both of the proofs are verified and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
-These proofs and checks allow one to check that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
+ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is DDH-tuples: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$.
+If the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
+This proof and checks allow one to be certain that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
 
@@
 If not, Bob should prove to MixEth that the $i$th round is indeed the first round, where the shuffled public key corresponding to $s_{B}$ is compromised.
-The first Chaum-Pedersen ensures that the integrity of the shuffled public key in round $i-1$st is intact, while the second proves that it is compromised in round $i$th.
+The Chaum-Pedersen proof in the challenge transaction ensures that the integrity of the shuffled public key in round $i-1$st is intact, while shuffled public key is compromised in the $i$th round.
 
@@
 	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(G,s_{B}G,C^{*}_{i-1},s_{B}C^{*}_{i-1}), proof_{DDH}(G,s_{B}G,C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
 	\begin{algorithmic}[1]
-		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(G,s_{B}G,C^{*}_{i-1},s_{B}C^{*}_{i-1})$ 
-		\State $b^{'}\leftarrow verifyChaumPedersen(proof_{DDH}(G,s_{B}G,C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
 		\State $b^*\leftarrow0$
-		\If {$b \land b^{'} \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
+		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
 		\State $b^*\gets 1$
@@
 This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
-
-We also highlight the necessity of two Chaum-Pedersen proofs for challenging a shuffle.
-If only one Chaum-Pedersen proof is enclosed in the challenging transaction, MixEth can not be sure that the integrity of the problematic public key indeed in the $i$th shuffling round was compromised.
-This could be abused by a malicious shuffler who deliberately corrupts their own public key in their shuffling round and afterwards they could blame any other shuffler for the compromise.
-This could have been led to losses of honest recipients' deposit.
 
@@
 An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround and upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
+
+\section{Acknowledgements}
+We would like to thank barryWhiteHat and Dmitry Khovratovich for the insightful comments and discussions. 
 \bibliographystyle{plain}

### 2018-10-25 migrations/4_MixEth_migration.js

@@ -1,9 +1,12 @@
-var MixEth = artifacts.require("MixEth");
-var EC = artifacts.require("./EC.sol");
+let MixEth = artifacts.require("MixEth");
+let EC = artifacts.require("./EC.sol");
+let ChaumPedersenVerifier = artifacts.require("./ChaumPedersenVerifier.sol");
 
 module.exports = function(deployer) {
   deployer.deploy(EC);
   deployer.link(EC, MixEth);
+  deployer.deploy(ChaumPedersenVerifier);
+  deployer.link(ChaumPedersenVerifier, MixEth);
 
   deployer.deploy(MixEth);
 };

### 2018-10-25 test/TestChaumPedersen.js

@@ -5,9 +5,6 @@ let Web3latest = require('web3');
 let web3latest = new Web3latest();
 
 
-//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
-//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
-
 contract('ChaumPedersenVerifier', function(accounts) {
     let ContractInstance;
     it("Chaum Pedersen Proof Verification",  async () => {

### 2018-10-25 test/TestMixEth.js

@@ -4,10 +4,8 @@ let abi = require('ethereumjs-abi');
 
 let Web3latest = require('web3');
 let web3latest = new Web3latest();
+web3latest.setProvider(new web3.providers.HttpProvider('http://localhost:8545'));
 
-
-//zGx <BN: 3e23b6642a729ec623b0154685ae6f1de3c72ae3eb3ee7713725bc93c5d281f0>
-//zGy <BN: 7ad3d864b091d260e78139b3fcebc71e0ffbeaf6e0bc3d6c6be3d4920cb6a9f5>
 
 contract('MixEth', function(accounts) {
     let ContractInstance;
@@ -29,7 +27,20 @@ contract('MixEth', function(accounts) {
             assert.equal(ycoordinate, 'fd94ed48e1f63312dce58f4d778ff45a2e5abb08a39c1bc0241139f5e54de7df', "Y coordinate is not correct");
             return ContractInstance.shufflers.call(shuffler);
         }).then(function(shufflerAddressIsSet) {
-            assert.equal(true, shufflerAddressIsSet, "Shuffler address is not correct");
+            assert.equal(true, shufflerAddressIsSet[0], "Shuffler address is not correct");
+        });
+    });
+
+    it("Uploading a shuffle to MixEth", function() {
+        return MixEth.deployed().then(async function(instance) {
+            ContractInstance = instance;
+            let txReceipt = await ContractInstance.uploadShuffle(
+            [pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX, pubKeyX,
+            pubKeyY, pubKeyY],
+            {value:1000000000000000000});
+            return ContractInstance.shufflers.call(accounts[0]);
+        }).then(function(shuffled) {
+            assert.equal(false, shuffled, "Shuffling transaction failed");
         });
     });
   });

### 2018-10-28 article/main.tex
Implementation section of article updated

@@
 \usepackage{amsmath}
+\usepackage{wrapfig}
 \usepackage{amsthm}
+\usepackage{graphicx}
 \usepackage{algorithm}
@@
 \newcommand{\xmark}{\ding{55}}%
-\usepackage{wrapfig}
 \usepackage{eufrak}
@@
 \section{Implementation}
+
+\begin{wrapfigure}{r}{0.7\textwidth}
+	\centering
+	\includegraphics[scale=0.7]{./withdrawalComplexity.jpg}
+\end{wrapfigure}
+
+We envision two approaches for implementing MixEth.
+The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
+This could lead to unwanted gas costs as the number of corrupted shuffles increases.
+One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources as possible.
+Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
+
+On of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
+A Miximus withdrawal transaction burns $1\,903\,305$ gas, regardless of the number of participating parties.
+Since the block gas limit is $8\,000\,266$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
+This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer linearly increases with the numbers of participants.
+
+\subsection{Fully on-chain implementation}
+
+\subsection{State channel implementation}
+
 \section{Related work}

### 2018-10-28 article/withdrawalFigure.m

@@ -1,0 +1,335 @@
+noOfParticipants = 50;
+participants = 1:1:noOfParticipants;
+
+blockGasLimit = 8000266; %https://etherscan.io/chart/gaslimit 2018.10.24.
+
+miximusWithdrawalCost = 1903305;
+noOfMiximusWithdrawal=floor(blockGasLimit/miximusWithdrawalCost);
+plotMiximus = noOfMiximusWithdrawal.* ones(length(participants),1);
+
+mobiusWithdrawalCost = participants.*335714;
+noOfMobiusWithdrawal=floor(1./(mobiusWithdrawalCost./blockGasLimit));
+plotMobius = noOfMobiusWithdrawal;
+
+mixEthWithdrawalCost = 75000;
+noOfMixEthWithdrawal=floor(blockGasLimit/mixEthWithdrawalCost);
+plotMixEth = noOfMixEthWithdrawal.* ones(length(participants),1);
+
+%plot(participants,  plotMiximus, 'Miximus', participants, plotMobius, participants, plotMixEth,'LineWidth',2);
+plot(participants, plotMiximus,'DisplayName','Miximus','LineWidth',2);
+hold on
+plot(participants, plotMobius,'DisplayName', 'Möbius' ,'LineWidth',2);
+plot(participants, plotMixEth, 'DisplayName', 'MixEth','LineWidth',2);
+hold off
+lgd = legend;
+lgd.NumColumns = 1;
+
+xlabel('Number of participants in the mixer')
+ylabel('Number of withdrawal tx fitting in a block')
+
+breakyaxis([30 100]); % Break Axis
+
+pause(0.1);
+legend({'Miximus','Möbius','MixEth'},'Location','southeast');
+
+% breakyaxes splits data in an axes so that data is in a low and high pane.
+%
+%   breakYAxes(splitYLim) splitYLim is a 2 element vector containing a range
+%   of y values from splitYLim(1) to splitYLim(2) to remove from the axes.
+%   They must be within the current yLimis of the axes.
+%
+%   breakYAxes(splitYLim,splitHeight) splitHeight is the distance to 
+%   seperate the low and high side.  Units are the same as 
+%   get(AX,'uints') default is 0.015
+% 
+%   breakYAxes(splitYLim,splitHeight,xOverhang) xOverhang stretches the 
+%   axis split graphic to extend past the top and bottom of the plot by
+%   the distance set by XOverhang.  Units are the same as get(AX,'units')
+%   default value is 0.015
+%
[…]

### 2018-10-29 migrations/5_CHPLibaryTest_migration.js
challengeShuffle func added to MixEth w/ a testcase

@@ -1,0 +1,9 @@
+let CHPLibraryTest = artifacts.require("CHPLibraryTest");
+let ChaumPedersenVerifier = artifacts.require("./ChaumPedersenVerifier.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(ChaumPedersenVerifier);
+  deployer.link(ChaumPedersenVerifier, CHPLibraryTest);
+
+  deployer.deploy(CHPLibraryTest);
+};

### 2018-10-29 shuffle/chaum_pedersen_generator.js

@@ -6,22 +6,20 @@ var ec = new EC('secp256k1');
 let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
 let n = bigInt('FFFFFFFFFFFFFFFFFFFFFFFFFFFFFFFEBAAEDCE6AF48A03BBFD25E8CD0364141',16); //order of the secp256k1 group
 
-function proofGenerator(_A, _B, _C, shufflingConstant, _s) {
+function proofGenerator(_G, _A, _B, _C, _privKey, _s) {
   let A = ec.keyFromPublic(_A,'hex').getPublic();
   let B = ec.keyFromPublic(_B,'hex').getPublic();
   let C = ec.keyFromPublic(_C,'hex').getPublic();
 
   let r = randomBytes(32);
   let rBigInt = bigInt(r.toString('hex'),16).mod(n);
-  let shufflingC = bigInt(shufflingConstant,16);
+  let privKey = bigInt(_privKey,16);
   let s =  bigInt(_s.toString(16),16);
 
-  console.log("s in natur: ", s);
-
-  let y1 = ec.keyFromPublic(G,'hex').getPublic().mul(r);
+  let y1 = ec.keyFromPublic(_G,'hex').getPublic().mul(r);
   let y2 = B.mul(r);
 
-  let z = rBigInt.add(shufflingC.multiply(s));
+  let z = rBigInt.add(privKey.multiply(s));
 
   return {"y1":y1, "y2":y2, "z":z.mod(n).toString(16)};
 }

### 2018-10-29 shuffle/chaum_pedersen_verifier.js

@@ -7,7 +7,7 @@ let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483AD
 let n = bigInt('FFFFFFFFFFFFFFFFFFFFFFFFFFFFFFFEBAAEDCE6AF48A03BBFD25E8CD0364141',16); //order of the secp256k1 group
 
 
-function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
+function proofVerifier(_G, _A, _B, _C, _s, _y1, _y2, z) {
   let A = ec.keyFromPublic(_A,'hex').getPublic();
   let B = ec.keyFromPublic(_B,'hex').getPublic();
   let C = ec.keyFromPublic(_C,'hex').getPublic();
@@ -16,7 +16,7 @@ function proofVerifier(_A, _B, _C, _s, _y1, _y2, z) {
 
   let s =  bigInt(_s.toString(16),16);
 
-  let zG = ec.keyFromPublic(G,'hex').getPublic().mul(z);
+  let zG = ec.keyFromPublic(_G,'hex').getPublic().mul(z);
   console.log("zGx", zG.getX());
   console.log("zGy", zG.getY());
 

### 2018-10-29 test/TestChaumPedersen.js

@@ -1,17 +1,18 @@
-let ChaumPedersenVerifier = artifacts.require("ChaumPedersenVerifier");
+let CHPLibraryTest = artifacts.require("CHPLibraryTest");
 let BigNumber = require('bignumber.js');
 
 let Web3latest = require('web3');
 let web3latest = new Web3latest();
 
 
-contract('ChaumPedersenVerifier', function(accounts) {
+contract('CHPLibraryTest', function(accounts) {
     let ContractInstance;
     it("Chaum Pedersen Proof Verification",  async () => {
-       return ChaumPedersenVerifier.deployed().then( async function(instance) {
+       return CHPLibraryTest.deployed().then( async function(instance) {
         ContractInstance = instance;
          let txReceipt= await ContractInstance.verifyChaumPedersen(
-             ['0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
+             ['0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798','0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8',
+              '0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
              '0x612e8ba3c5a6adc4f69c1c8aa304c3f1fdbc053a5feaa949189b80ec439ffa40','0x259ff66f1678eae6b9e23f30f59d1349d027a04eb3a8f4e452709deb40f32b17',
              '0x1b5839e49e2d6ef32e38aa60cca86e5534cb5bc7978ad3b99dae5197d95512b4','0x583b4d5d798a872bfa7dd9a665b6acf54a250fb47f3aa86053e3c546bf77597f',
               '43543543',
@@ -22,7 +23,7 @@ contract('ChaumPedersenVerifier', function(accounts) {
               '0xd5c6218926cd52ba55e5e519373c0e54678b41c5d4d899719cca5a286746711c','0x83f75b325fe00b405fbdaf151ae82d97b8902fd4e77177d2e0659e777c901f11',
[…]

### 2018-10-29 test/TestECLibrary.js

@@ -1,6 +1,11 @@
 let ECLibraryTest = artifacts.require("ECLibraryTest");
 let BigNumber = require('bignumber.js');
+let abi = require('ethereumjs-abi');
+let bigInt = require("big-integer")
 
+let Web3latest = require('web3');
+let web3latest = new Web3latest();
+web3latest.setProvider(new web3.providers.HttpProvider('http://localhost:8545'));
 
 let Gx = '0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798';
 let Gy = '0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8';
@@ -115,14 +120,18 @@ contract('ECLibraryTest', function(accounts) {
     });
 
     it("Scalar Multiplication: whatever", function() {
+
         return ECLibraryTest.deployed().then(function(instance) {
-            ContractInstance.mul('0xd043398fa1f2791bb88af1f439844bedebb2c20b13e0fa4a72081e5280a9a4fe');
+            ContractInstance.mul('0xcf646c195cc0d8667e62a98c753eb27bc78c1b8193beef81b7dc48b9bc6dfe49');
             return ContractInstance.hx.call();
         }).then(function(xcoordinate) {
             resultx = new BigNumber(xcoordinate).toString(16);
+            console.log("x coordinate of ganache", resultx);
             return ContractInstance.hy.call();
         }).then(function(ycoordinate){
-          resulty = new BigNumber(ycoordinate).toString(16)
+          resulty = new BigNumber(ycoordinate).toString(16);
+          console.log("y coordinate of ganache", resulty);
+          console.log("hash of pubkey", web3latest.utils.sha3(resultx,resulty));
         });
     });
 

### 2018-10-29 test/TestMixEth.js

@@ -9,38 +9,71 @@ web3latest.setProvider(new web3.providers.HttpProvider('http://localhost:8545'))
 
 contract('MixEth', function(accounts) {
     let ContractInstance;
-    let shuffler = '0xafdefc1937ae294c3bd55386a8b9775539d81653';
-    let pubKeyX = '0x6cb84859e85b1d9a27e060fdede38bb818c93850fb6e42d9c7e4bd879f8b9153';
-    let pubKeyY = '0xfd94ed48e1f63312dce58f4d778ff45a2e5abb08a39c1bc0241139f5e54de7df';
+    let shuffler = accounts[0];
+    let pubKeyX = '0x1ec64fdd678f8528c981fbdd742e8c79fa91c6f7bfdfbebf2f99f74df6f09589';
+    let pubKeyY = '0x118caf99d37bd0f75cd9efa455261f8806c14bae4ddee43690aff3bc1b6eef48';
     it("Depositting to a public key", function() {
         return MixEth.deployed().then(async function(instance) {
             ContractInstance = instance;
             let txReceipt = await ContractInstance.deposit(
             pubKeyX,
             pubKeyY,
+            shuffler,
             {value:1000000000000000000});
+            console.log("Deposit tx gas cost:", txReceipt.receipt.gasUsed);
             return ContractInstance.initPubKeys.call(0);
         }).then(function(pubKey) {
             let xcoordinate = new BigNumber(pubKey[0]).toString(16)
             let ycoordinate = new BigNumber(pubKey[1]).toString(16)
-            assert.equal(xcoordinate, '6cb84859e85b1d9a27e060fdede38bb818c93850fb6e42d9c7e4bd879f8b9153', "X coordinate is not correct");
-            assert.equal(ycoordinate, 'fd94ed48e1f63312dce58f4d778ff45a2e5abb08a39c1bc0241139f5e54de7df', "Y coordinate is not correct");
+            assert.equal(xcoordinate, '1ec64fdd678f8528c981fbdd742e8c79fa91c6f7bfdfbebf2f99f74df6f09589', "X coordinate is not correct");
+            assert.equal(ycoordinate, '118caf99d37bd0f75cd9efa455261f8806c14bae4ddee43690aff3bc1b6eef48', "Y coordinate is not correct");
[…]

### 2018-10-30 ecdsa/sign.js
ECDSA with arbitrary generator off-chain code

@@ -1,0 +1,64 @@
+let EC = require('elliptic').ec;
+let ec = new EC('secp256k1');
+let BN = require('bn.js');
+let secureRandom = require('secure-random')
+
+let n = 'fffffffffffffffffffffffffffffffebaaedce6af48a03bbfd25e8cd0364141';
+let power256 = new BN('10000000000000000000000000000000000000000000000000000000000000000',16);
+
+//FIXME: checks has to be added for sign and verify as well
+
+//this is a modified ECDSA, where user can specifiy their own generator element
+function sign(generator, privKey, msgHash) {
+  let mHash = new BN(msgHash, 16);
+  let pKey = new BN(privKey, 16);
+
+  /*
+    we assume to use keccak-256, so there is no need to take the 256 leftmost bits,
+    since messages are already truncated to 256-bits via keccak-256
+  */
+
+  /*
+    Select a cryptographically secure random integer k from [1,n-1]
+  */
+  let k = new BN(secureRandom.randomBuffer(32).toString('hex'),16).mod(ec.curve.n)
+
+  //Calculate the curve point (x_{1},y_{1})=kG.
+
+  let G = ec.keyFromPublic(generator,'hex').getPublic();
+  let kG = G.mul(k);
+
+  console.log("Public key: ", G.mul(pKey));
+
+  //get the x coordinate of kG mod n
+  let r = kG.getX().mod(ec.curve.n);
+
+  // Calculate  s=k^{-1}(mHash+r*pKey)\,mod n.
+  let kinv = k.invm(ec.curve.n);
+  let term = (mHash.add(r.mul(pKey))).mod(ec.curve.n);
+  let s = kinv.mul(term).mod(ec.curve.n);
+
+  return {"r": r, "s": s};
+}
+
+function verify(generator, _pubKey, msgHash, _r, _s) {
+  let G = ec.keyFromPublic(generator,'hex').getPublic();
+  let pubKey = ec.keyFromPublic(_pubKey,'hex').getPublic();
+  let mHash = new BN(msgHash, 16);
+  let r = new BN(_r, 16);
+  let s = new BN(_s, 16);
+  //Calculate w=s^{-1} mod n.
+  let w = s.invm(ec.curve.n);
+  //Calculate u1=zw mod n and u2=rw mod n
+  let u1 = (mHash.mul(w)).mod(ec.curve.n);
+  let u2 = (r.mul(w)).mod(ec.curve.n);
+
[…]

### 2018-10-30 ecdsa/sign.js
Withdraw functionality added to MixEth

@@ -4,7 +4,6 @@ let BN = require('bn.js');
 let secureRandom = require('secure-random')
 
 let n = 'fffffffffffffffffffffffffffffffebaaedce6af48a03bbfd25e8cd0364141';
-let power256 = new BN('10000000000000000000000000000000000000000000000000000000000000000',16);
 
 //FIXME: checks has to be added for sign and verify as well
 
@@ -53,8 +52,15 @@ function verify(generator, _pubKey, msgHash, _r, _s) {
   let u1 = (mHash.mul(w)).mod(ec.curve.n);
   let u2 = (r.mul(w)).mod(ec.curve.n);
 
+  console.log("w", w);
+  console.log("u1", u1);
+  console.log("u2", u2);
   //Calculate the curve point (x,y)=u1*G+u2*pubKey.
   let Q = (G.mul(u1)).add(pubKey.mul(u2));
+  console.log("u1Gx",(G.mul(u1)).getX());
+  console.log("u1Gy",(G.mul(u1)).getY());
+  console.log("u2pKx",(pubKey.mul(u2)).getX());
+  console.log("u2pKy",(pubKey.mul(u2)).getY());
   //The signature is valid if r=x mod n, invalid otherwisee
   return((Q.getX().mod(ec.curve.n)).eq(r));
 }

### 2018-10-30 migrations/4_MixEth_migration.js

@@ -1,12 +1,18 @@
 let MixEth = artifacts.require("MixEth");
 let EC = artifacts.require("./EC.sol");
 let ChaumPedersenVerifier = artifacts.require("./ChaumPedersenVerifier.sol");
+let ECDSAGeneralized = artifacts.require("./ECDSAGeneralized.sol");
 
 module.exports = function(deployer) {
   deployer.deploy(EC);
   deployer.link(EC, MixEth);
   deployer.deploy(ChaumPedersenVerifier);
   deployer.link(ChaumPedersenVerifier, MixEth);
+  deployer.deploy(EC);
+  deployer.link(EC, ECDSAGeneralized);
+  deployer.deploy(ECDSAGeneralized);
+  deployer.link(ECDSAGeneralized, MixEth);
+
 
   deployer.deploy(MixEth);
 };

### 2018-10-30 migrations/6_ECDSATest_migration.js

@@ -1,0 +1,12 @@
+let ECDSALibraryTest = artifacts.require("ECDSALibraryTest");
+let ECDSAGeneralized = artifacts.require("./ECDSAGeneralized.sol");
+let EC = artifacts.require("./EC.sol");
+
+module.exports = function(deployer) {
+  deployer.deploy(EC);
+  deployer.link(EC, ECDSAGeneralized);
+  deployer.deploy(ECDSAGeneralized);
+  deployer.link(ECDSAGeneralized, ECDSALibraryTest);
+
+  deployer.deploy(ECDSALibraryTest);
+};

### 2018-10-30 test/TestECDSALibrary.js

@@ -1,0 +1,34 @@
+let ECDSALibraryTest = artifacts.require("ECDSALibraryTest");
+let BigNumber = require('bignumber.js');
+
+let Web3latest = require('web3');
+let web3latest = new Web3latest();
+
+
+
+/*
+  uint256 Gx, uint256 Gy, uint256 pKx, uint256 pKy,
+  uint256 msgHash, uint256 r, uint256 s,
+  uint256 u1Gx, uint256 u1Gy, uint256 u2pKx, uint256 u2pKy
+*/
+contract('ECDSALibraryTest', function(accounts) {
+    let ContractInstance;
+    it("Generalized ECDSA Signature Verification",  async () => {
+       return ECDSALibraryTest.deployed().then( async function(instance) {
+        ContractInstance = instance;
+         let txReceipt= await ContractInstance.verifySig([
+           '0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
+           '0xd0cc696065a9bd1f4fc83259d13ebd05a19ef97ac3440b78012405627623d672','0xf5b9894c4032a9b607c4f10ce706cf73803416d14e8c14f222d7ad0c62e544d4',
+           '0xf5654645fcdea',
+           '0xeae131d615529859cb9973db036d004e7c6e0d5de48fdc7d5659c037ecc75a47','0x825c437c9b48f46e44ffbb2093ac54b9d66db4a32a0d0d36565616cc2a7cf780',
+           '0x6554c05280fe320f3e9b598e9b3260d7ec7f2a203a0df98e58773031913f9f34','0x30782f93940ebadba87a336466722774970f3f7352edf50211054c1c18e810a1',
+           '0x605f27fa8fac4c2b77de3352179a6f1dc019cab29483e14dd8c36ea985fb1960','0xb268882cc5856c6dbf4443c0b0b60876076a95d46f50789e1fa0ee63ca1a6ea',
+           '0x8cc70839ed233fafe105c7ac9d00870b99b35d227ae6b53a5be6c597ffd0a5']);
+           console.log("The gas cost of verifying a generalized ECDSA signature on-chain:", txReceipt.receipt.gasUsed);
+          return ContractInstance.testIng.call();
+      }).then(function(verified) {
+          console.log(verified);
+          assert.equal(true, verified, "Signature is not verified");
+        });
+   });
+});

### 2018-10-30 test/TestMixEth.js

@@ -72,8 +72,33 @@ contract('MixEth', function(accounts) {
              );
              console.log("challengeShuffle gas usage", txReceipt.receipt.gasUsed);
              return ContractInstance.shufflers.call(accounts[1]);
-           }).then(function(shuffled) {      
+           }).then(function(shuffled) {
              assert.equal(true, shuffled[1], "Shuffler is not slashed!");
            });
       });
+      it("Withdrawing from the mixer", function() {
+          return MixEth.deployed().then(async function(instance) {
+              ContractInstance = instance;
+              let a = await ContractInstance.deposit(pubKeyX, pubKeyY, accounts[0],
+              {value:1000000000000000000, from:accounts[0]});
+              let tx = await ContractInstance.uploadShuffle(['0xd3b0b6d59fdd841d28821171aa912d625169d58fac04592b239bcab9b84082ee','0x99f88955859c34dc7c2cbe0ce423ded7e1d2302fc279be3f805f71dde7eca582',
+              '0xf924738fbaebf80ca5a0d1d6cc33856be448c0e60670c64f73aeac0000925808','0xe392c39c052599470fea0142bea6add7cceb5a2f99423bb45320d35f083d4f60',
+              '0x6c709bf8f273b07791824b08e1b99ece69c0fb5fbdcfe7c1150b0ccd7a816c54','0x21753728d8b3028f041a71eee89c7424a870c2ff8da41350cc15ef397df0d373',
+              '0x23c239f04c5ac9c411379b1a3570b68526dd5d47888cdcb7caf874ff3aeab499','0x3dd81fbd6a7907275b0ce68b9261ec8a5520b6587bb7cbd33d26d72a0d917f47',
+              '0xd0cc696065a9bd1f4fc83259d13ebd05a19ef97ac3440b78012405627623d672','0xf5b9894c4032a9b607c4f10ce706cf73803416d14e8c14f222d7ad0c62e544d4',
+              '0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296'],
+              {value:1000000000000000000, from:accounts[0]});
[…]

### 2018-10-31 article/main.tex
Preliminary implementation gas cost results

@@
 \usepackage{listings}
+\usepackage[toc,page]{appendix}
 \usepackage{color}
@@
 
-\subsection{Chaum-Pedersen protocol}
+\subsection{Decision Diffie-Hellman Problem and Chaum-Pedersen Protocol}
+
+The Decision Diffie-Hellman assumption (DDH) is a standard cryptographic hardness assumption which underlies the security of many cryptographic protocols.
+Roughly speaking DDH states that no efficient algorithm can distinguish between the two distributions $(aG, bG, abG)$ and $(aG, bG, cG)$, where $a,b,c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|}$.
+It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve, which is used to generate accounts and sign transactions in Bitcoin and Ethereum among other cryptocurrencies.
+
+ Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers
+
 The language $\mathcal{L}_{DDH}$ is defined to be the set of all tuples $(G,aG,bG,abG)$ where $G\in \mathbb{G}$ is of order prime $q$.
@@
 Note that in the following a non-interactive version of this protocol will only be considered that can be achieved by applying the Fiat-Shamir heuristic.
+
+\subsection{ECDSA with arbitrary generator element}
+Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth.
+ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}.
+Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.
+
+However, in MixEth, we deploy a somewhat loosened version of ECDSA, where we allow arbitrary generator elements to be used.
+Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
+Therefore the usial $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.
+
+In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e.
+no efficient adversary could forge a signature on any given message with non-negligible probability.
 
@@
 
+\newpage
 \section{Implementation}
@@
 On of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
-A Miximus withdrawal transaction burns $1\,903\,305$ gas, regardless of the number of participating parties.
-Since the block gas limit is $8\,000\,266$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
+A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
+Since the block gas limit is $\num[group-separator={,}]{8000266}$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
 This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer linearly increases with the numbers of participants.
@@
 \subsection{State channel implementation}
+
+\begin{table}[H] 
+	\caption{Preliminary implementation gas cost results. Expect further improvements. MixEth++ refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\centering 
+	\begin{tabular}{@{\extracolsep{6pt}}lcccc@{}}
+
+		\toprule
+		\hline
+		&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
+		\cline{3-4}&&Shuffle upload&Challenge\\
+		\hline
+		\midrule
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&\num[group-separator={,}]{99254}&\num[group-separator={,}]{253268}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{143268}  \\
+		MixEth++&TBD&0&0&TBD\\
+		\bottomrule
+	\end{tabular}
+	\label{table:securityproperties}
+\end{table}
 
@@
 We would like to thank barryWhiteHat and Dmitry Khovratovich for the insightful comments and discussions.
+
 \bibliographystyle{plain}
@@
 
+\begin{appendices}
+	\section{Proof of Anonymity}
+	Reduction to DDH has to be added here
+\end{appendices}
+
 \end{document}

### 2018-11-02 article/main.tex
Require error messages in contract and security definitions in article

@@
 \usepackage{amsthm}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
 \usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
 \usepackage{breqn}
@@
 
-\textbf{Note: this is an early-stage work-in-progress! Security proofs, implementation and many more are yet to come!} 
+\textbf{Note: this is an early-stage work-in-progress! Security proofs, (state channel) implementation and many more are yet to come!} 
 \begin{abstract}
@@
 A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys.
+In all the following interactions and algorithms we assume that the public state of the tumbler is implicitly given as input.
 Interactions of these entities can be summarized as follows:
 
-$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit some ether to the receiver's public key.
+$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.
+
+$0/1\leftarrow VerifyDeposit(tx)$: The tumbler contract checks the validity of senders' deposits.
+
+$ProcessDeposit(tx)$: upon receiving a valid deposit transaction, the mixing contract updates its internal state accordingly.
 
@@
 
-$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B)$: after the end of the shuffling period users are allowed to withdraw their funds.
-Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather the final shuffling accumulated constant.
+$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*})$: after the end of the shuffling period users are allowed to withdraw their funds.
+Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}$, the final shuffling accumulated constant.
+
+$0/1\leftarrow VerifyWithdraw(tx)$: tumbler checks the validity of a recipient's withdrawal transaction.
+
+$ProcessWithdraw(tx)$: upon receiving a valid withdrawal transaction, mixing contract updates its internal state accordingly.
 
 \subsection{Security goals} \label{securitygoals}
-We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}.
+We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
 We are going to assume that at most $k-2$ recipients are malicious ($k$ is the number of recipients).
 Otherwise, no meaningful notion of security can be achieved.
-Furthermore presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
+Furthermore we presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
 Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
 
-In this early version of the MixEth paper we only restrict ourselves to give informal security definitions.
+In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles.
+CORR enables $\adv$ to corrupt a sencer or receiver by learning the secret key of any party $l$ of their choice.
+Oracle access to AD or AW allow $\adv$ to deposit or withdraw respectively from tumbler session $j$.
+Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW.
+In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
+
+These oracles are formally defined as follows:
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cccc}    
+		\begin{minipage}{6cm}
+			\procedure{AD(tx,$j$)}{%
+				b \leftarrow VerifyDeposit(tumblers[j],tx) \\
+				if\ (b) \ ProcessDeposit(tumblers[j],tx) \\
+				\pcreturn b  }
+		\end{minipage}
+		&
+		\begin{minipage}{6cm}
+			\procedure{AW(tx,$j$)}{%
+				b \leftarrow VerifyWithdraw(tumblers[j],tx) \\
+				if\ (b) \  ProcessWithdraw(tumblers[j],tx) \\
+				\pcreturn b  }
+		\end{minipage}
+		&
+		\begin{minipage}{4cm}
+			\procedure{CORR($l$)}{%
+				C=C.push(pk_{B_{l}}) \\
+				\pcreturn sk_{B_l}}
+		\end{minipage}
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cc}   
+\begin{minipage}{5cm}
+	\procedure{HD($i$,$j$,$l$)}{%
+		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}})\\
+		H_{d}=H_{d}.push(tx) \\
+		ProcessDeposit(tumblers[j],tx)\\
+		\pcreturn tx }
+\end{minipage}
+&
+\begin{minipage}{5cm}
+	\procedure{HW($j$,$l$)}{%
+		if\ (pk_{B_{l}} \notin tumblers[j].keys_{B})\ return \ \bot \\
+		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}}) \\
+		H_{w}=H_{w}.push(j,l,tx) \\
+		ProcessWithdraw(tumblers[j],tx)\\
+		\pcreturn tx }
+\end{minipage}
+\end{tabular}
+\end{table}
+
+From now on, we will denote the number of senders and receivers in the mixer as $n$, while a specific key in a given session is denoted as $tumbler.keys_{B}$.
+
 \subsubsection{Anonymity}
-\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest miners are sending funds, assuming that honest senders' deposits are indistinguishable.
+\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
 
 \textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
+These notions of anonymity were introduced in \cite{meiklejohn2018mobius}, which are included here for sake of self-containedness.
+
+\begin{definition}
+	Define $\textbf{Adv}^{d-anon}_{mix,\adv}(\lambda) = 2\Pr[\textsf{G}^{d-anon}_{mix,\adv}(\lambda)]-1\ for\ d \in \{dep, with\}$, where these games are defined as follows:
+
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{cc}    
+			\begin{minipage}{7cm}
+					\procedure{MAIN $\textsf{G}^{dep-anon}_{mix,\adv}(\lambda)$}{%
+						(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+						\textsf{PK}_A\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
+						b \stackrel{\$}{\leftarrow} \bin \\
+						(state,j,pk, i_{0},i_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{A}) \\
+						tx \stackrel{\$}{\leftarrow} Deposit(tumblers[j], sk_{A_{{l}_{b}}}, pk) \\
+						b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
+						\pcreturn b = b^{’} }
+			\end{minipage}
+			&
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
+					b \stackrel{\$}{\leftarrow} \bin \\
+					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
+					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
+					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
+					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
+					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
+					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
+					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
+					\pcreturn b = b^{’} }		
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+Then the tumbler satisfies sender or recipient anonymity if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.
+\end{definition}
+
 \subsubsection{Availability}
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&\num[group-separator={,}]{99254}&\num[group-separator={,}]{253268}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{143268}  \\
+		MixEth&\num[group-separator={,}]{99254}&\num[group-separator={,}]{153268}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
 		MixEth++&TBD&0&0&TBD\\
@@
 \begin{appendices}
+
 \section{Proof of Anonymity}
 Reduction to DDH has to be added here
+
+\begin{bbrenv}{A}
+ \begin{bbrbox} [name=BoxName]
+ \pseudocode {
+	 \text{ s t e p 1} \\
+	 \text{ s t e p 2} \\
+	 \pcfor\text{some c o n d i t i o n } \pcdo \\
+	 \pcind\text{step3}
+	 }
+
+ \begin{bbrenv}{B}
+ \begin{bbrbox}[name=InnerBox]
+ \pseudocode{
+	 \text{ i n n e r s t e p 1} \\
+	 \text{ i n n e r s t e p 2} \\
+	 }
+ \end{bbrbox}
+ \end{bbrenv}
+
+ \pseudocode{
+	 \text{ s t e p 4} \\
+	 \text{ s t e p 5} \\
+	 }
+ \end{bbrbox}
+ \bbrinput{input}
+ \bbroutput{output}
+ \end{bbrenv}
+
 \end{appendices}

### 2018-11-02 test/TestMixEth.js

@@ -28,8 +28,8 @@ contract('MixEth', function(accounts) {
             assert.equal(xcoordinate, '1ec64fdd678f8528c981fbdd742e8c79fa91c6f7bfdfbebf2f99f74df6f09589', "X coordinate is not correct");
             assert.equal(ycoordinate, '118caf99d37bd0f75cd9efa455261f8806c14bae4ddee43690aff3bc1b6eef48', "Y coordinate is not correct");
             return ContractInstance.shufflers.call(shuffler);
-        }).then(function(shufflerAddressIsSet) {
-            assert.equal(false, shufflerAddressIsSet[0], "Shuffler address is not correct");
+        }).then(function(shufflerStateIsSet) {
+            assert.equal(true, shufflerStateIsSet[2], "Shuffler's address and/or state is not correct");
         });
     });
 
@@ -79,7 +79,7 @@ contract('MixEth', function(accounts) {
       it("Withdrawing from the mixer", function() {
           return MixEth.deployed().then(async function(instance) {
               ContractInstance = instance;
-              let a = await ContractInstance.deposit(pubKeyX, pubKeyY, accounts[0],
+              let a = await ContractInstance.deposit(pubKeyX, pubKeyY, accounts[2],
               {value:1000000000000000000, from:accounts[0]});
               let tx = await ContractInstance.uploadShuffle(['0xd3b0b6d59fdd841d28821171aa912d625169d58fac04592b239bcab9b84082ee','0x99f88955859c34dc7c2cbe0ce423ded7e1d2302fc279be3f805f71dde7eca582',
               '0xf924738fbaebf80ca5a0d1d6cc33856be448c0e60670c64f73aeac0000925808','0xe392c39c052599470fea0142bea6add7cceb5a2f99423bb45320d35f083d4f60',
@@ -87,14 +87,14 @@ contract('MixEth', function(accounts) {
               '0x23c239f04c5ac9c411379b1a3570b68526dd5d47888cdcb7caf874ff3aeab499','0x3dd81fbd6a7907275b0ce68b9261ec8a5520b6587bb7cbd33d26d72a0d917f47',
               '0xd0cc696065a9bd1f4fc83259d13ebd05a19ef97ac3440b78012405627623d672','0xf5b9894c4032a9b607c4f10ce706cf73803416d14e8c14f222d7ad0c62e544d4',
[…]

### 2018-11-03 article/main.tex
Proof of recipient anonymity added

@@
 
-\subsubsection{Anonymity}
+\subsubsection{Anonymity} \label{sec:defanonymity}
 \textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
@@
 It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer.
+
 \subsubsection{Theft prevention}
@@
 	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lcccc@{}}
+	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}}
 
@@
 		\hline
-		&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
-		\cline{3-4}&&Shuffle upload&Challenge\\
+		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
+		\cline{4-5}&&&Shuffle upload&Challenge\\
 		\hline
 		\midrule
-		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
-		Miximus \cite{miximus2018}&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&\num[group-separator={,}]{99254}&\num[group-separator={,}]{153268}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
-		MixEth++&TBD&0&0&TBD\\
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
+		MixEth++&TBD&TBD&0&0&TBD\\
 		\bottomrule
@@
 \section{Proof of Anonymity}
-Reduction to DDH has to be added here
+Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
 
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\centering
 \begin{bbrenv}{A}
- \begin{bbrbox} [name=BoxName]
+ \begin{bbrbox} [name=\bdv]
  \pseudocode {
-	 \text{ s t e p 1} \\
-	 \text{ s t e p 2} \\
-	 \pcfor\text{some c o n d i t i o n } \pcdo \\
-	 \pcind\text{step3}
+	 \text{$\textsf{PK}_{B} = (s_{0}C^{*}, s_{1}C^{*})$} \\
+	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{l_{b}}})$}
 	 }
@@
  \begin{bbrenv}{B}
- \begin{bbrbox}[name=InnerBox]
+ \begin{bbrbox}[name=\adv]
  \pseudocode{
-	 \text{ i n n e r s t e p 1} \\
-	 \text{ i n n e r s t e p 2} \\
+ 	 \text{Input: $PK_{B}, tx$} \\
+	 \text{Output: $b^'$} \\
 	 }
  \end{bbrbox}
+
  \end{bbrenv}
 
- \pseudocode{
-	 \text{ s t e p 4} \\
-	 \text{ s t e p 5} \\
-	 }
  \end{bbrbox}
- \bbrinput{input}
- \bbroutput{output}
+
+ \bbrinput{$(s_{0}G,C^{*},s_{b}C^{*})$}
+ \bbroutput{$b^'$}
 \end{bbrenv}
+
+\captionof{figure}{An illustration for the reduction of withdrawal anonymity to the DDH assumption}
+\end{wrapfigure}
+
+Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(s_{0}G,C^{*},s_{b}C^{*})$.
+If original keys are $(s_{0}G, s_{1}G)$ and shuffled keys are $\textsf{PK}_{B}=(s_{0}C^{*}, s_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
+Then a withdrawal transaction occurs from $s_{b}C^{*}$.
+After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will outpu the very same bit.
+It is straightforward to see that $\bdv$ wins the DDH-game if and only if $\adv$ wins the $\textsf{G}^{with, anon}_{mix, \adv}$ security game.
+Therefore, by the assumption that recipient anonymity does not hold we have that $$\textsf{non-negl}(\lambda)=\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\Pr[\textsf{DDH}_{\bdv}],$$ which contradicts to the DDH assumption.
 

### 2018-11-03 migrations/4_MixEth_migration.js

@@ -3,7 +3,7 @@ let EC = artifacts.require("./EC.sol");
 let ChaumPedersenVerifier = artifacts.require("./ChaumPedersenVerifier.sol");
 let ECDSAGeneralized = artifacts.require("./ECDSAGeneralized.sol");
 
-module.exports = function(deployer) {
+module.exports = async function(deployer) {
   deployer.deploy(EC);
   deployer.link(EC, MixEth);
   deployer.deploy(ChaumPedersenVerifier);

### 2018-11-03 test/TestMixEth.js

@@ -12,6 +12,7 @@ contract('MixEth', function(accounts) {
     let shuffler = accounts[0];
     let pubKeyX = '0x1ec64fdd678f8528c981fbdd742e8c79fa91c6f7bfdfbebf2f99f74df6f09589';
     let pubKeyY = '0x118caf99d37bd0f75cd9efa455261f8806c14bae4ddee43690aff3bc1b6eef48';
+
     it("Depositting to a public key", function() {
         return MixEth.deployed().then(async function(instance) {
             ContractInstance = instance;
@@ -32,6 +33,12 @@ contract('MixEth', function(accounts) {
             assert.equal(true, shufflerStateIsSet[2], "Shuffler's address and/or state is not correct");
         });
     });
+
+    /*it("Should deploy with less than 4.7 mil gas", async () => {
+      let someInstance = await MixEth.new();
+      let receipt = await web3.eth.getTransactionReceipt(someInstance.transactionHash);
+      assert.isBelow(receipt.gasUsed, 4700000);
+    });*/
 
      it("Challenging a shuffle", function() {
          return MixEth.deployed().then(async function(instance) {

### 2018-11-05 article/main.tex
MixEth formal specification added

@@
 \subsection{Depositing period}
-Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value are rejected.  
+Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value or invalid public key are rejected.  
 \subsection{Shuffling period}
@@
 The recipient can prove to MixEth that she knows secret key $s_{B}$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
-\subsection{MixEth pseudocode}
 
-\medskip
-\begin{lstlisting}[caption=MixEth contract pseudocode]
-contract MixEth {
-  uint256 amt;
-  address[] senders;
-  CurvePoint[] initPubKeys;
-  Shuffle[] Shuffles;
+\subsection{MixEth formal specification}
 
-  struct CurvePoint {
-    uint256 x; //x coordinate
-    uint256 y; //y coordinate
-  }
-  struct Shuffle { 
-    //describes a shuffle
-    // contains the shuffled pubKeys and the shuffling accumulated constant
-  }
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cccc}    
+		\begin{minipage}{5.5cm}
+			\procedure{\textsf{Deposit}($sk_A, pk_{B}$)}{%
+				\pcreturn \textsf{FormTx}(sk_A,id_{\textsf{contract}}, amt, pk_{B}) }
+		\end{minipage}
+		&
+		\begin{minipage}{5.4cm}
+			\procedure{\textsf{VerifyDeposit}(tx)}{%
+				if\ (tx[amt] \neq id_{\textsf{contract}}[amt]) \ return\ 0 \\
+				if\ (pk_{B} \notin \mathbb{G}) \ return\ 0 \\
+				\pcreturn \textsf{VerifyTx(tx)}  }
+		\end{minipage}
+		&
+		\begin{minipage}{4cm}
+			\procedure{\textsf{ProcessDeposit(tx)}}{%
+				add\ \textsf{addr(tx[pk]) to initPubKeys[]}}
+		\end{minipage}
+	\end{tabular}
+\end{table}
 
-  constructor() public {
-   //sets amt
-  }
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cccc}    
+		\begin{minipage}{5.5cm}
+			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
+				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
+				C^{'*} \leftarrow cC^{*} \\
+				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
+				\pcreturn (PK^{'},C^{'*}) }
+		\end{minipage}
+		&
+		\begin{minipage}{6.3cm}
+			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, C^{*}$)}{%
+				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
+				if\ (sC^{*} \notin PK) \ return\ 0 \\
+				\pcreturn 1  }
+		\end{minipage}
+	\end{tabular}
+\end{table}
 
-  function uploadShuffle(Shuffle newShuffle) public {
-    //needs to be ensured that recipient has not shuffled yet
-    Shuffles.append(newShuffle);  
-  }
-
-  function challengeShuffle(CurvePoint[] challenge, uint256 i) public {
-    bool accepted;
-    //contract checks the correctness of the i-th shuffle which is stored at Shuffles[i]. If challenge accepted malicious shuffler's deposit is slashed.
-    return accepted;
-  }
-
-  function withdraw() public {
-    //receivers can withdraw funds at most once
-  }   
-}
-\end{lstlisting}
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cccc}    
+		\begin{minipage}{4.5cm}
+			\procedure{\textsf{Withdraw($C^{*},sC^{*}$)}}{%
+				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
+				\pcreturn \textsf{FormTx($sC^{*}, id_{\textsf{contract}, 0}, \sigma,$)} }
+		\end{minipage}
+		&
+		\begin{minipage}{6.3cm}
+			\procedure{\textsf{VerifyWithdraw(tx)}}{%
+				if\ (sC^{*} \notin id_{\textsf{contract}}[lastShuffle] ) \ return\ 0 \\
+				if\ (\lnot\verify(C^{*}, sC^{*},\sigma, sC^{*}||tx.sender)) \ return\ 0 \\
+				\pcreturn \textsf{VerifyTx(tx)}  }
+		\end{minipage}
+		&
+		\begin{minipage}{4cm}
+			\procedure{\textsf{ProcessWithdraw(tx)})}{%
+				delete\ sC^{*} from\ id_{\textsf{contract}}[lastShuffle]   \\
+				tx^{'}\stackrel{\$}{\leftarrow} \textsf{FormTx}(id_{contract}, tx.sender, amt) }
+		\end{minipage}
+	\end{tabular}
+\end{table}
 

### 2018-11-05 test/TestMixEth.js

@@ -34,12 +34,6 @@ contract('MixEth', function(accounts) {
         });
     });
 
-    /*it("Should deploy with less than 4.7 mil gas", async () => {
-      let someInstance = await MixEth.new();
-      let receipt = await web3.eth.getTransactionReceipt(someInstance.transactionHash);
-      assert.isBelow(receipt.gasUsed, 4700000);
-    });*/
-
      it("Challenging a shuffle", function() {
          return MixEth.deployed().then(async function(instance) {
              ContractInstance = instance;

### 2018-11-05 article/main.tex
Testcases for invalid deposit

@@
  \pseudocode {
-	 \text{$\textsf{PK}_{B} = (s_{0}C^{*}, s_{1}C^{*})$} \\
-	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{l_{b}}})$}
+ 	 \text{$c_{1}\stackrel{\$}{\leftarrow}\mathbb{Z}_p$} \\
+	 \text{$\textsf{PK}_{B} = (c_{0}G, c_{1}G)$} \\
+	 \text{$b \stackrel{\$}{\leftarrow} \bin $} \\
+	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{c_{b}}})$}
 	 }
@@
  	 \text{Input: $PK_{B}, tx$} \\
-	 \text{Output: $b^'$} \\
+	 \text{Output: $b^'$}
 	 }
@@
 
- \bbrinput{$(s_{0}G,C^{*},s_{b}C^{*})$}
- \bbroutput{$b^'$}
+ \bbrinput{$(sG,cG,c_{0}G)$}
+ \bbroutput{$\lnot b\lnot{b^'}+b$}
 \end{bbrenv}
@@
 
-Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(s_{0}G,C^{*},s_{b}C^{*})$.
-If original keys are $(s_{0}G, s_{1}G)$ and shuffled keys are $\textsf{PK}_{B}=(s_{0}C^{*}, s_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
-Then a withdrawal transaction occurs from $s_{b}C^{*}$.
-After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will outpu the very same bit.
-It is straightforward to see that $\bdv$ wins the DDH-game if and only if $\adv$ wins the $\textsf{G}^{with, anon}_{mix, \adv}$ security game.
-Therefore, by the assumption that recipient anonymity does not hold we have that $$\textsf{non-negl}(\lambda)=\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\Pr[\textsf{DDH}_{\bdv}],$$ which contradicts to the DDH assumption.
+Towards contradiction let us assume that the recipient anonymity does not hold.
+Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(sG,cG,c_{0}G)$.
+Adversary $\bdv$ generates uniformly random public key $c_{1}G$ and invokes $\adv$ with the set $\textsf{PK}_{B}=(c_{0}C^{*}, c_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
+Then a withdrawal transaction occurs from $c_{b}G$.
+After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will output $\lnot b^{'}$.
+If $\adv$ outputs $0$ and $b=b^{'}$, this signals to $\bdv$ that $c_{0}G$ might potentially be of the form $scG=c_{0}G$  i.e.
+it is a DDH tuple, therefore $\bdv$ outputs $1$.
+In all the other cases $\bdv$ outputs a random bit.
+Therefore we have that $\bdv$ has an adventage in their DDH-game if and only if $\adv$ wins their $\textsf{G}^{with, anon}_{mix, \adv}$ security game.
+Since we assumed that recipient anonymity does not hold we have that $$\Pr[\textsf{DDH}_{\bdv}]=\frac{1}{2}+\frac{1}{2}*\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\frac{1}{2}+\frac{1}{2}*\textsf{non-negl}(\lambda),$$ which contradicts to the DDH assumption.
+
+\section{Proof of Availability}
+\section{Proof of Theft Prevention}
 

### 2018-11-05 test/TestMixEth.js

@@ -1,6 +1,7 @@
 let MixEth = artifacts.require("MixEth");
 let BigNumber = require('bignumber.js');
 let abi = require('ethereumjs-abi');
+let catchRevert = require("./exceptions.js").catchRevert;
 
 let Web3latest = require('web3');
 let web3latest = new Web3latest();
@@ -31,6 +32,28 @@ contract('MixEth', function(accounts) {
             return ContractInstance.shufflers.call(shuffler);
         }).then(function(shufflerStateIsSet) {
             assert.equal(true, shufflerStateIsSet[2], "Shuffler's address and/or state is not correct");
+        });
+    });
+
+    it("Depositting to a public key with invalid amount", function() {
+        return MixEth.deployed().then(async function(instance) {
+            ContractInstance = instance;
+            await catchRevert(ContractInstance.deposit(
+              pubKeyX,
+              pubKeyY,
+              shuffler,
+              {value:100}));
+        });
+    });
+
+    it("Depositting to an invalid public key", function() {
+        return MixEth.deployed().then(async function(instance) {
+            ContractInstance = instance;
+            await catchRevert(ContractInstance.deposit(
+              '111',
+              pubKeyY,
+              shuffler,
+              {value:1000000000000000000}));
         });
     });
 

### 2018-11-05 test/exceptions.js

@@ -1,0 +1,22 @@
+const PREFIX = "VM Exception while processing transaction: ";
+
+async function tryCatch(promise, message) {
+    try {
+        await promise;
+        throw null;
+    }
+    catch (error) {
+        assert(error, "Expected an error but did not get one");
+        assert(error.message.startsWith(PREFIX + message), "Expected an error starting with '" + PREFIX + message + "' but got '" + error.message + "' instead");
+    }
+};
+
+module.exports = {
+    catchRevert            : async function(promise) {await tryCatch(promise, "revert"             );},
+    catchOutOfGas          : async function(promise) {await tryCatch(promise, "out of gas"         );},
+    catchInvalidJump       : async function(promise) {await tryCatch(promise, "invalid JUMP"       );},
+    catchInvalidOpcode     : async function(promise) {await tryCatch(promise, "invalid opcode"     );},
+    catchStackOverflow     : async function(promise) {await tryCatch(promise, "stack overflow"     );},
+    catchStackUnderflow    : async function(promise) {await tryCatch(promise, "stack underflow"    );},
+    catchStaticStateChange : async function(promise) {await tryCatch(promise, "static state change");},
+};

### 2018-11-06 article/main.tex
Security definitions are added

@@
 We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
-We are going to assume that at most $k-2$ recipients are malicious ($k$ is the number of recipients).
+These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
+
+We are going to assume that at most $n-2$ recipients are malicious ($n$ is the number of recipients).
 Otherwise, no meaningful notion of security can be achieved.
@@
 In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles.
-CORR enables $\adv$ to corrupt a sencer or receiver by learning the secret key of any party $l$ of their choice.
+CORR enables $\adv$ to corrupt a sender or receiver by learning the secret key of any party $l$ of their choice.
 Oracle access to AD or AW allow $\adv$ to deposit or withdraw respectively from tumbler session $j$.
@@
 
-From now on, we will denote the number of senders and receivers in the mixer as $n$, while a specific key in a given session is denoted as $tumbler.keys_{B}$.
+From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.
 
@@
 \textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
-These notions of anonymity were introduced in \cite{meiklejohn2018mobius}, which are included here for sake of self-containedness.
 
@@
 \subsubsection{Availability}
-It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer.
+It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and one but all recipients are compromised.
+
+Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient can not withdraw their funds.
+
+\begin{definition}
+	Define $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{avail}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
+
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{c}    
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{avail}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w} \leftarrow \emptyset\\
+					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
+					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l}) \\
+					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
+					\pcreturn (b=0)\land(pk_{l}\in tumblers[j].keys_{B})}
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+	Then the tumbler satisfies availability if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+\end{definition}
 
 \subsubsection{Theft prevention}
-We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. 
+We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:
+
+\begin{definition}
+	Define $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{theft}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
+
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{c}    
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{theft}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w}, \textsf{contract} \leftarrow \emptyset\\
+					(\textsf{tx},j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,AW,HW}(1^{\lambda},\textsf{PK}_{B}) \\
+					if(\textsf{tumblers}[j].\textsf{keys}_{B}\not\subset \textsf{PK}_{B}\setminus C)\ return \ 0 \\
+					\pcreturn \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{tx})}
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+	Then the tumbler satisfies theft prevention if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+\end{definition}
+
 \section{MixEth}

### 2018-11-08 article/main.tex
Miximus added to related work

@@
 		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\cmark        \\
-		Miximus \cite{miximus2018}&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
+		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
 		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
@@
 \section{Related work}
+Miximus is a trustless zkSNARK-based mixer for Ethereum.
+It uses zkSNAKRKs to conceal the mapping between depositors and recipients.
+A depositor creates a leaf in a Merkle-tree.
+A depositor needs to exchange the preimage of the leaf with the recipient.
+Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf.
+So called nullifiers enable recipients to withdraw funds once and only once.
+The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
+However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
+Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
+Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
+
 As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
@@
 	Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
-	Miximus \cite{miximus2018} & 1 & 2 \\
+	Miximus \cite{miximus2018} & 1+MPC & 2 \\
 	MixEth & 1 & 3 \\

### 2018-11-09 test/TestMixEth.js
Fixed Withdrawal tx, fixed frontrunning vulnerability

@@ -100,6 +100,13 @@ contract('MixEth', function(accounts) {
              assert.equal(true, shuffled[1], "Shuffler is not slashed!");
            });
       });
+
+      /*
+        uint256 Gx, uint256 Gy, uint256 pKx, uint256 pKy,
+        uint256 msgHash, uint256 r, uint256 s,
+        uint256 u1Gx, uint256 u1Gy, uint256 u2pKx, uint256 u2pKy,
+        uint256 w
+      */
       it("Withdrawing from the mixer", function() {
           return MixEth.deployed().then(async function(instance) {
               ContractInstance = instance;
@@ -114,11 +121,11 @@ contract('MixEth', function(accounts) {
               {value:1000000000000000000, from:accounts[2]});
               let tx2 = await ContractInstance.withdrawAmt(['0xa25126710efb86866b63ffab6539e791c76e08f332618bd3fff7d0b1fcd68fd8','0xac55f34cd8a4e188f9629d8546ed7025036a61c5407b129cc8376e3570c7d296',
               '0xd0cc696065a9bd1f4fc83259d13ebd05a19ef97ac3440b78012405627623d672','0xf5b9894c4032a9b607c4f10ce706cf73803416d14e8c14f222d7ad0c62e544d4',
-              '0xf5654645fcdea',
-              '0xeae131d615529859cb9973db036d004e7c6e0d5de48fdc7d5659c037ecc75a47','0x825c437c9b48f46e44ffbb2093ac54b9d66db4a32a0d0d36565616cc2a7cf780',
-              '0x6554c05280fe320f3e9b598e9b3260d7ec7f2a203a0df98e58773031913f9f34','0x30782f93940ebadba87a336466722774970f3f7352edf50211054c1c18e810a1',
-              '0x605f27fa8fac4c2b77de3352179a6f1dc019cab29483e14dd8c36ea985fb1960','0xb268882cc5856c6dbf4443c0b0b60876076a95d46f50789e1fa0ee63ca1a6ea',
-              '0x8cc70839ed233fafe105c7ac9d00870b99b35d227ae6b53a5be6c597ffd0a5'],8, {from:accounts[2]});
+              '0x0f055734df9b01fc88c282decddb06fd25e3c3faf2ec8b0eb682221c2bdd69e6',
[…]

### 2018-11-10 article/main.tex
Möbius added to related work

@@
 		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
-		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\cmark        \\
+		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
 		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
@@
 \section{Related work}
-Miximus is a trustless zkSNARK-based mixer for Ethereum.
-It uses zkSNAKRKs to conceal the mapping between depositors and recipients.
+Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
+Authors of Möbius provided formal definitions of various notions of securty such as anonymity, theft prevention and mixer availability.
+These properties could be used to evaluate and compare existing and future proposals from a security perspective.
+Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
+However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
+No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
+If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
+Another, maybe even more severe problem with Möbius is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
+When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
+Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius is not guaranteed.
+
+Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}.
+It uses zkSNARKs to conceal the mapping between depositors and recipients.
 A depositor creates a leaf in a Merkle-tree.
@@
 \begin{table}[H] 
-\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol.}
+\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol.
+Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
 \centering 

### 2018-11-13 article/main.tex
Ethereum section added to background

@@
 
-\title{MixEth: efficient trustless coin mixing service for Ethereum}
+\title{MixEth: efficient, trustless coin mixing service for Ethereum}
 \author[1]{István András Seres}
@@
 These transactions are recorded in an immutable, publicly verifiable ledger.
-Due to this transparent nature of the ledger, privacy is notably reduced.
-If the link between users' public key and their physical identity is exposed  their pseudonymity is lost.
+Due to the ledger's transparent nature, privacy is notably reduced.
+If the link between users' public key and their physical identity is exposed, their pseudonymity is lost.
 One way to increase users' privacy is to deploy coin mixing services.
@@
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
-Game-theoretical analysis of incentives in MixEth is also enclosed.
 
@@
 More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin.
-If a user wants to create an Ethereum address, first she needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite field $\mathbb{F}_{p}$.
+If a user wants to create an Ethereum address, first they needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite prime field $\mathbb{F}_{p}$.
 The corresponding public key will be $sG$.
@@
 So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.
+The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.
 
@@
 
- Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers
+ Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers.
 
@@
 \subsection{Ethereum}
+
+Ethereum is a cryptocurrency built on top of a blockchain.
+Similarly to Bitcoin, network participants broadcast transactions in a peer-to-peer network, where transactions are bundled together into blocks that are appended to a public ledger called blockchain.
+Only those specific nodes can append new blocks to the blockchain who previously solved a difficult cryptographic puzzle.
+The state of the system consists of the state of different accounts populating it.
+
+In Ethereum currently there are two types of accounts.
+The first account type is called \textit{externally owned account}.
+It owns an ECDSA keypair controlled by its user.
+Private keys are used to sign transactions.
+On the other hand there are \textit{contract accounts}, often smart contracts, that additionally have persistent storage and contract's code.
+Both of the account types have Ether balances, which is the native currency of the Ethereum network.
+Ether is denominated in wei, where $1\ ETH = 10^ {18}\ wei$.
+
+Transactions can alter the system's state by either creating a contract account or by calling to an existing account.
+Transactions to externally owned accounts can only transfere Ether, while transactions to contract accounts can additionally execute the code associated with them.
+Codes are executed in a quasi-Turing complete execution environment, called Ethereum Virtual Machine (EVM).
+
+EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}.
+In every gas the sender needs to pay upfront for the execution of the contract's code.
+The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price.
+Therefore the transaction fee is the gas cost multiplied by the gas price.
+One needs to specify a gas limit, meaning that they do not allow their transaction to burn more gas than the limit.
+If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner.
+If there are gas left after successful execution, transaction originator is reimbursed.
+Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block.
+Currently the block gas limit is cca.
+$\num[group-separator={,}]{8000000}$ gas.
+Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees.
+Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.
 

### 2018-11-13 article/main.tex
Error spotted by Sina Mahmoodi

@@
 Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
-Every recipient of the mix is allowed to shuffle the public keys at most once:
+Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve.
+be Every recipient of the mix is allowed to shuffle the public keys at most once:
 
 $PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
-Let us call $C^{*}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
+Let us call $C^{*}_{i}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
 The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period.
@@
 $tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*})$: after the end of the shuffling period users are allowed to withdraw their funds.
-Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}$, the final shuffling accumulated constant.
+Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}_{final}$, the final shuffling accumulated constant.
 
@@
 
-A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the following parameters:
-\begin{itemize}
-	\item $amt$: denomination of ether to be mixed;
-	\item $senders[]$: list of all the sender addresses;
-	\item $initPubKeys[]$: list of all the recipients' public keys;
-	\item $shuffles[][]$: list of all the shuffles with corresponding shuffling accumulated constants.
-	\item $withdrawn[]$: list of all the shuffled public keys who had already withdrawn their coins.	
-\end{itemize}
+A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
 
 \subsection{Depositing period}
-Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value or invalid public key are rejected.  
+Every sender must deposit exactly $amt$ ether to a specific public key.
+Deposits with incorrect ether value or invalid public key are rejected.
+Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.
+
 \subsection{Shuffling period}
@@
 Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
-If a challenge is accepted, then shuffler's deposit is lost, her shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should raise all the public keys to a secret exponent $c$ and then permute all the transformed public keys.
+If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret exponent $c$ and then permute all the transformed public keys.
 Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
@@
 \subsection{Withdrawing}
-Let $C^*$ be the final shuffling accumulated constant.
-For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*$.
-The recipient can prove to MixEth that she knows secret key $s_{B}$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
+Let $C^*_{final}$ be the final shuffling accumulated constant.
+For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*_{final}$.
+The recipient can prove to MixEth that she knows secret key $s_{B}$ by signing their public key using a modified ECDSA, which uses $C^*_{final}$ as the generator element instead of the standardized $G$.
 
@@
 This section is going to demonstrate security proofs for the notions of security introduced in Section \ref{securitygoals}.
-
-In this early version of the MixEth paper, we only restrict ourselves to give intuition and informal proofs for certain security properties.
 
@@
 \section{Acknowledgements}
-We would like to thank barryWhiteHat and Dmitry Khovratovich for the insightful comments and discussions.
+We would like to thank barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 

### 2018-11-13 article/main.tex
Error spotted by Sina Mahmoodi part 2

@@
 					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
-					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l}) \\
+					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l})) \\
 					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
@@
 \section{Security}
-This section is going to demonstrate security proofs for the notions of security introduced in Section \ref{securitygoals}.
+This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.
 
@@
 \subsection{Availability}
-If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to the Ethereum transaction ledger.
+If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
 \subsection{Theft prevention} 

### 2018-11-14 article/main.tex
Proof for theft prevention added

@@
 
-\subsubsection{Theft prevention}
+\subsubsection{Theft prevention} \label{sec:theftprevention}
 We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:
@@
 Adversary can only distinguish between honest recipients public keys with negligible probability.
+See reduction proof in Appendix \ref*{appendanon}.
 \subsection{Availability}
-If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
+If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
 \subsection{Theft prevention} 
-If an adversary is able to steal funds from other users than it would imply that they broke discrete logarithm problem on the secp256k1 curve.
+If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient.
+This contradicts to the assumption that ECDSA is existentially unforgeable.
+Reduction proof is enclosed in Appendix \ref*{appendtheft}.
 \begin{table}[H] 
@@
 
-\section{Proof of Anonymity}
+\section{Proof of Anonymity} \label{appendanon}
 Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
@@
 
-\section{Proof of Availability}
-\section{Proof of Theft Prevention}
+\section{Proof of Availability}  \label{appendavail}
+\section{Proof of Theft Prevention} \label{appendtheft}
+
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\centering
+	\begin{bbrenv}{A}
+		\begin{bbrbox} [name=\bdv]
+			\pseudocode {
+				\text{$(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]$} \\
+				\text{$\textsf{PK}_{B}\leftarrow\{pk_{i}\}_{i=1}^{n}$;$C, H_{\omega}, contract \leftarrow \emptyset$}
+			}
+
+			\begin{bbrenv}{B}
+				\begin{bbrbox}[name=\adv]
+					\pseudocode{
+						\text{Input: $(1^{\lambda},PK_{B})$} \\
+						\text{$(tx,j) \stackrel{\$}{\leftarrow}\adv^{CORR,AD,AW,HW}(1^{\lambda},PK_{B})$} \\
+						\text{Output: $(tx,j)$}
+					}
+				\end{bbrbox}
+
+			\end{bbrenv}
+
+		\end{bbrbox}
+		\bbrinput{$1^\lambda$}
+		\bbroutput{$(tx,\sigma_{tx})$}
+	\end{bbrenv}
+
+	\captionof{figure}{An illustration for the reduction of theft prevention to the existentially unforgeability of ECDSA.}
+\end{wrapfigure}
+
+Towards contradiction we assume that there exists an adversary $\adv$, who is able to break the theft prevention property introduced in Section \ref{sec:theftprevention} with non-negligible probability.
+Using such an adversary as a subroutine we could create another efficient adversary $\bdv$ who is able to break the existential unforgeability of ECDSA.
+The input of the forgeability game is the security parameter which is forwarded to $\adv$ along with $n$ randomly generated public keys.
+By assumption $\adv$ outputs with non-negligible probability valid withdraw transaction belonging to one of the public keys in the mixer.
+$\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
+$\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
+$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$. This contradicts to the assumption that ECDSA is existentially unforgeable.
 

### 2018-11-22 test/TestMixEth.js
Separating shuffle and the shuffling accumulated constant

@@ -67,8 +67,8 @@ contract('MixEth Challenge', function(accounts) {
              '0xf924738fbaebf80ca5a0d1d6cc33856be448c0e60670c64f73aeac0000925808','0xe392c39c052599470fea0142bea6add7cceb5a2f99423bb45320d35f083d4f60',
              '0x6c709bf8f273b07791824b08e1b99ece69c0fb5fbdcfe7c1150b0ccd7a816c54','0x21753728d8b3028f041a71eee89c7424a870c2ff8da41350cc15ef397df0d373',
              '0x23c239f04c5ac9c411379b1a3570b68526dd5d47888cdcb7caf874ff3aeab499','0x3dd81fbd6a7907275b0ce68b9261ec8a5520b6587bb7cbd33d26d72a0d917f47',
-             '0x82078c021bf51fd1b3066ac43662d0c3ca63718e0ee424790ddb81f060ee7a43','0xb2954aeac3580c5ce6cfc4ca84186b5433c06a81983bb474b4aee97fef5bb031',
-             '0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798','0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'],
+             '0x82078c021bf51fd1b3066ac43662d0c3ca63718e0ee424790ddb81f060ee7a43','0xb2954aeac3580c5ce6cfc4ca84186b5433c06a81983bb474b4aee97fef5bb031'],
+             ['0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798','0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'],
              {value:1000000000000000000, from:accounts[0]});
              console.log("Gas cost of uploading a shuffle", tx.receipt.gasUsed);
              let abd = await ContractInstance.uploadShuffle('0x0000000000000000000000000000000000000000',
@@ -77,8 +77,8 @@ contract('MixEth Challenge', function(accounts) {
              '0x8c46882be46a4e65cfd5515f8809253654e61a7fa4135d269a1694d32f374602', '0xe8675d17c8ed23bd205fa65ab505792cd16d3cffc1f2f347ae52040d77ce0848',
[…]

### 2018-11-22 test/TestMixEth.js
Distinguishing shuffle/challenge periods using block.numbers

@@ -10,6 +10,28 @@ web3latest.setProvider(new web3.providers.HttpProvider('http://localhost:8545'))
 let pubKeyX = '0x1ec64fdd678f8528c981fbdd742e8c79fa91c6f7bfdfbebf2f99f74df6f09589';
 let pubKeyY = '0x118caf99d37bd0f75cd9efa455261f8806c14bae4ddee43690aff3bc1b6eef48';
 
+let networkID;
+
+web3latest.eth.net.getId().then(netId => {
+  switch (netId) {
+    case 1:
+      console.log('This is mainnet')
+      networkID = 1;
+      break
+    case 2:
+      console.log('This is the deprecated Morden test network.')
+      networkID = 2;
+      break
+    case 3:
+      console.log('This is the ropsten test network.')
+      networkID = 3;
+      break
+    default:
+      console.log('This is an unknown network.')
+      networkID = netId;
+  }
+})
+
 contract('MixEth Deposits', function(accounts) {
     let ContractInstance;
     let shuffler = accounts[0];
@@ -57,10 +79,6 @@ contract('MixEth Challenge', function(accounts) {
      it("Challenging a shuffle", function() {
          return MixEth.deployed().then(async function(instance) {
              ContractInstance = instance;
-             /*let a = await ContractInstance.depositEther(pubKeyX, pubKeyY,
-             {value:1000000000000000000, from:accounts[0]});
-             let b = await ContractInstance.depositEther(pubKeyX, pubKeyY,
-             {value:1000000000000000000, from:accounts[1]});*/
              let tx = await ContractInstance.uploadShuffle('0x0000000000000000000000000000000000000000',
              [],
              ['0xd3b0b6d59fdd841d28821171aa912d625169d58fac04592b239bcab9b84082ee','0x99f88955859c34dc7c2cbe0ce423ded7e1d2302fc279be3f805f71dde7eca582',
@@ -69,8 +87,9 @@ contract('MixEth Challenge', function(accounts) {
              '0x23c239f04c5ac9c411379b1a3570b68526dd5d47888cdcb7caf874ff3aeab499','0x3dd81fbd6a7907275b0ce68b9261ec8a5520b6587bb7cbd33d26d72a0d917f47',
[…]

### 2018-11-23 article/withdrawalFigure.m
Initial measurements of shuffle tx gas costs

@@ -1,4 +1,4 @@
-noOfParticipants = 50;
+noOfParticipants = 40;
 participants = 1:1:noOfParticipants;
 
 blockGasLimit = 8000266; %https://etherscan.io/chart/gaslimit 2018.10.24.
@@ -11,7 +11,7 @@ mobiusWithdrawalCost = participants.*335714;
 noOfMobiusWithdrawal=floor(1./(mobiusWithdrawalCost./blockGasLimit));
 plotMobius = noOfMobiusWithdrawal;
 
-mixEthWithdrawalCost = 75000;
+mixEthWithdrawalCost = 113958;
 noOfMixEthWithdrawal=floor(blockGasLimit/mixEthWithdrawalCost);
 plotMixEth = noOfMixEthWithdrawal.* ones(length(participants),1);
 
@@ -26,8 +26,9 @@ lgd.NumColumns = 1;
 
 xlabel('Number of participants in the mixer')
 ylabel('Number of withdrawal tx fitting in a block')
+ylim([0 80])
 
-breakyaxis([30 100]); % Break Axis
+breakyaxis([25 65]); % Break Axis
 
 pause(0.1);
 legend({'Miximus','Möbius','MixEth'},'Location','southeast');

### 2018-11-23 test/TestMixEth.js

@@ -79,26 +79,75 @@ contract('MixEth Challenge', function(accounts) {
      it("Challenging a shuffle", function() {
          return MixEth.deployed().then(async function(instance) {
              ContractInstance = instance;
-             let tx = await ContractInstance.uploadShuffle('0x0000000000000000000000000000000000000000',
+             let tx0 = await ContractInstance.uploadShuffle('0x0000000000000000000000000000000000000000',
              [],
+             ['0xd3b0b6d59fdd841d28821171aa912d625169d58fac04592b239bcab9b84082ee','0x99f88955859c34dc7c2cbe0ce423ded7e1d2302fc279be3f805f71dde7eca582',
+             ],
+             ['0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798','0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'],
+             {value:2000000000000000000, from:accounts[0]});
+             console.log("Gas cost of uploading a shuffle01:", tx0.receipt.gasUsed);
+             await mineBlock(20);
+             let tx1 = await ContractInstance.uploadShuffle('0x0000000000000000000000000000000000000000',
+             [],
+             ['0xd3b0b6d59fdd841d28821171aa912d625169d58fac04592b239bcab9b84082ee','0x99f88955859c34dc7c2cbe0ce423ded7e1d2302fc279be3f805f71dde7eca582',
+             '0xf924738fbaebf80ca5a0d1d6cc33856be448c0e60670c64f73aeac0000925808','0xe392c39c052599470fea0142bea6add7cceb5a2f99423bb45320d35f083d4f60'
+             ],
+             ['0x79BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798','0x483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'],
+             {value:2000000000000000000, from:accounts[1]});
+             console.log("Gas cost of uploading a shuffle02", tx1.receipt.gasUsed);
+             await mineBlock(20);
[…]

### 2018-11-25 test/TestMixEth.js
Fixed bug spotted by Chris

@@ -201,7 +201,7 @@ contract('MixEth Challenge', function(accounts) {
               '0xac402dfc8929141090a320508de763d020fedbe00286cde14673e173d691fc8f','0x8d8684b3edd169d9eefcc2732bceb5baca902476fd8e1a4dd14010a6845d3f68',
               '0xe4237819aef1db170ffe8a9e768d623f95c7b2a5f0ad717be86fbfbdf9bd679e','0xe8b71a0ee31ec3cd54af6c926943dc5986c510392f8b6b9cfce2113f9e108045',
               '0xc718652f3c3814ef324d636312e4558a21232cb806f15cccf60125ecbf91c35c'],
-              '0x0000000000000000000000000000000000000000', {from:accounts[2]});
+              {from:accounts[2]});
               console.log("Gas cost of witdhrawing from the mixer", tx2.receipt.gasUsed);
               return ContractInstance.Shuffles('0x0000000000000000000000000000000000000000', true);
             }).then(function(a){

### 2018-11-26 article/main.tex
Added Chris to authors' list
State channel subsection to background is added

@@
 \usepackage{amsthm}
+\usetikzlibrary{arrows,automata}
 \usepackage{algpseudocode}
@@
 
+\newcommand{\smallsim}{\smallsym{\mathrel}{\sim}}
+
+\makeatletter
+\newcommand{\smallsym}[2]{#1{\mathpalette\make@small@sym{#2}}}
+\newcommand{\make@small@sym}[2]{%
+	\vcenter{\hbox{$\m@th\downgrade@style#1#2$}}%
+}
+\newcommand{\downgrade@style}[1]{%
+	\ifx#1\displaystyle\scriptstyle\else
+	\ifx#1\textstyle\scriptstyle\else
+	\scriptscriptstyle
+	\fi\fi
+}
+\makeatother
+
 \title{MixEth: efficient, trustless coin mixing service for Ethereum}
@@
 \author[1]{Dániel A. Nagy}
+\author[2]{Chris Buckland}
 \author[1]{Péter Burcsi}
 \affil[1]{Department of Computer Algebra, Eötvös Loránd University}
+\affil[2]{King's College London}
 \begin{document}
@@
 
-\textbf{Note: this is an early-stage work-in-progress! Security proofs, (state channel) implementation and many more are yet to come!} 
 \begin{abstract}
@@
 
-\subsection{Ethereum account abstraction}
+\subsubsection{State channels} 
+Public blockchain's decentralization comes at an inherent cost in regard to scalability, since currently each full node verifies the full state of the public ledger.
+Often times Bitcoin's ($\smallsim7$ transactions per second (tps)) or Ethereum's ($\smallsim15$ tps) throughput is compared to that of Visa's ($\smallsim\num[group-separator={,}]{45000}$ tps).
+Blockchains' scalability issues became an increasingly growing problem as more and more users adopted the technology.
+One remarkable example was the launch of the Cryptokitties game in 2017, when the Ethereum network was congested for a few hours due to the enormous popularity of the game.
+Therefore several solutions were proposed to alleviate aforementioned scalability issues.
+
+One of the major class of these techniques is called off-chain solutions.
+The insight of these proposals is that it is not needed to conduct all transactions on the blockchain, since participants could lock funds on-chain and afterwards securely issue transactions off-chain, for instance micropayments, with high degree of security and finality.
+They only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
+The first implementation of this idea was a payment channel network for Bitcoin called Lightning network \cite{poon2016bitcoin}.
+The advantage of the Lightning network is that participants can issue several payments without sending transactions to the blockchain and paying the sometimes costly transaction fees.
+Furthermore users are guaranteed to have instant finality instead of waiting several blocks to confirm their payments.
+
+State channels are the more general form of payment channels, they can be used not only for payments, but for any arbitrary state updates on a blockchain, like changes inside a smart contract.
+State channels were first described in detail by Jeff Coleman et al.\cite{coleman2018counterfactual}.
+Since then several other frameworks for generalised state channels were elaborated (\cite{dziembowski2017perun},\cite{mccorryyou}).
+Recently a case study of the Battleship game was published Patrick McCorry, Chris Buckland et al.
+to evaluate how state channels could contribute in scaling blockchain-based applications \cite{mccorryyou}.
+
+Later in this paper, in Section \ref{statechannelimpl} we argue that MixEth can be made more scalable by implementing shuffling in a state channel.
+
+\subsubsection{Ethereum account abstraction}
 Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
@@
 
-\newpage
 \section{Implementation}
@@
 	\includegraphics[scale=0.7]{./withdrawalComplexity.jpg}
+	\captionsetup{justification=centering}
+	\caption{Gas complexity of withdraw transactions for various trustless Ethereum coin mixers}
 \end{wrapfigure}
 
-We envision two approaches for implementing MixEth.
+We implemented MixEth with two different approaches.
 The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
 This could lead to unwanted gas costs as the number of corrupted shuffles increases.
-One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources as possible.
+One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible.
 Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
+Both of the implementations allow users to mix Ether or other ERC20-compatible, a popular Ethereum token standard, tokens.
 
-On of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
+One of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
 A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
 Since the block gas limit is $\num[group-separator={,}]{8000266}$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
-This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer linearly increases with the numbers of participants.
+This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
 
-\subsection{Fully on-chain implementation}
-
-\subsection{State channel implementation}
+All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts.
+MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions.
+Note that these implementations are only proof-of-concept implementations, expect further improvements.
+All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
 
 \begin{table}[H] 
-	\caption{Preliminary implementation gas cost results. Expect further improvements. MixEth++ refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\caption{Proof-of-concept implementation gas cost results.
+Expect further improvements.
+MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
 	\centering 
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{210220}&\num[group-separator={,}]{113265}  \\
-		MixEth++&TBD&TBD&0&0&TBD\\
+		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{227563}&\num[group-separator={,}]{113265}  \\
+		MixEthChannel&TBD&TBD&0&0&TBD\\
 		\bottomrule
@@
 \end{table}
+
+\subsection{Fully on-chain implementation} \label{fullyonchainimpl}
+
+\begin{wrapfigure}{r}{0.3\textwidth}
+	\centering
+\begin{tikzpicture}[shorten >=1pt,node distance=3cm,on grid,auto] 
+\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
+\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
+\node[state] (q_challenge) [below=of q_shuffle ] {$q_{challenge}$};
+\node[state, accepting below, below=of q_challenge] (q_withdraw) {$q_{withdraw_{k}}$};
+\path[->]
+(q_deposit) edge [loop right] node {$i+1$} ()
+(q_deposit) edge node {$i=N$} (q_shuffle)		
+(q_shuffle) edge node {} (q_challenge)
+(q_challenge) edge [bend right, swap] node {$noFraud, j+1$} (q_shuffle)
+(q_challenge) edge [bend left] node {$fraud, j-1$} (q_shuffle)
+(q_challenge) edge node {$j=N$} (q_withdraw)
+(q_withdraw) edge [loop right] node {$k+1$} ();
+\end{tikzpicture}
+\captionsetup{justification=centering}
+\caption{Shuffle-and-challenge paradigm implemented for the fully on-chain version of MixEth}
+\end{wrapfigure}
+
+In our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
+Since on-chain storage is extremely expensive, we decided to store only the last two sets of shuffled public keys.
+Note that storing only the latest shuffle would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first shuffled key is also available for the contract.
+Such a storage structure implies that after uploading the new shuffled keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle.
+Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $2$ on-chain transactions are sufficient to complete the protocol.
+However shufflers need to withdraw their shuffling deposits with an additional on-chain transaction.
+We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.
+
+A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets.
+One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time.
+As soon as the anonymity set is large enough a receiver could withdraw their assets.
+This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
+However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
+$300$.
+
+Also note that the on-chain cost of a shuffle transaction could be amortized among participants.
+Specifically if there is a group of senders and/or receivers who trust each other they could collectively charge any of them to shuffle once.
+Since they trust their peer, all the rest of the group does not need to shuffle anymore.
+Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.
+
+\subsection{State channel implementation} \label{statechannelimpl}
+
+\begin{wrapfigure}{r}{0.4\textwidth}
+	\centering
+\begin{tikzpicture}[shorten >=1pt,node distance=4cm,on grid,auto] 
+\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
+\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
+\node[state, below=of q_shuffle] (q_no_fraud) {$q_{noFraud_j}$};	\node[state, accepting, right=of q_no_fraud] (q_fraud) {$q_{fraud}$};
+\node[state, accepting below, below=of q_no_fraud] (q_withdraw) {$q_{withdraw_{k}}$};
+\path[->]
+(q_deposit) edge [loop left] node {$i+1$} ()
+(q_deposit) edge node {$i=N$} (q_shuffle)		
+(q_shuffle) edge [loop left] node {$j+1$} ()
+(q_shuffle) edge node {$j=N$} (q_no_fraud)
+(q_no_fraud) edge node {$j=N$} (q_withdraw)
+(q_no_fraud) edge [loop left] node {$j+1$} ()
+(q_no_fraud) edge node {} (q_fraud)
+(q_withdraw) edge [loop left] node {$k+1$} ();
+\end{tikzpicture}
+\captionsetup{justification=centering}
+\caption{Shuffle-then-challenge paradigm implemented for the channelised version of MixEth}
+\end{wrapfigure}
+
+MixEth is also implemented in a way where shuffling and challenging periods are taking place in a state channel.
+We accomodated our implementation to the Counterfactual state channel framework  \cite{coleman2018counterfactual}.
 
@@
 	Miximus \cite{miximus2018} & 1+MPC & 2 \\
-	MixEth & 1 & 3 \\
+	MixEth & 1 & 2 \\
+	MixEthChannel  & $\mathcal{O}(n)$ &2 \\
 	\bottomrule

### 2018-11-26 article/main.tex
Integrating Chris sections to the article

@@
 
-\begin{table}[H] 
-	\caption{Proof-of-concept implementation gas cost results.
-Expect further improvements.
-MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
-	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}}
-
-		\toprule
-		\hline
-		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
-		\cline{4-5}&&&Shuffle upload&Challenge\\
-		\hline
-		\midrule
-		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
-		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{227563}&\num[group-separator={,}]{113265}  \\
-		MixEthChannel&TBD&TBD&0&0&TBD\\
-		\bottomrule
-	\end{tabular}
-	\label{table:securityproperties}
-\end{table}
-
 \subsection{Fully on-chain implementation} \label{fullyonchainimpl}
@@
 (q_challenge) edge [bend left] node {$fraud, j-1$} (q_shuffle)
-(q_challenge) edge node {$j=N$} (q_withdraw)
+(q_challenge) edge node {$j=N^{'}$} (q_withdraw)
 (q_withdraw) edge [loop right] node {$k+1$} ();
@@
 \caption{Shuffle-and-challenge paradigm implemented for the fully on-chain version of MixEth}
+\label{fig:shuffleandchallenge}
 \end{wrapfigure}
@@
 Such a storage structure implies that after uploading the new shuffled keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle.
-Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $2$ on-chain transactions are sufficient to complete the protocol.
+Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions are sufficient to complete the protocol.
 However shufflers need to withdraw their shuffling deposits with an additional on-chain transaction.
@@
 As soon as the anonymity set is large enough a receiver could withdraw their assets.
+The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}.
+A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
 This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
@@
 Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.
-
-\subsection{State channel implementation} \label{statechannelimpl}
 
@@
 \caption{Shuffle-then-challenge paradigm implemented for the channelised version of MixEth}
+\label{fig:shufflethenchallenge}
 \end{wrapfigure}
+\newpage
+\subsection{State channel implementation} \label{statechannelimpl}
 
-MixEth is also implemented in a way where shuffling and challenging periods are taking place in a state channel.
-We accomodated our implementation to the Counterfactual state channel framework  \cite{coleman2018counterfactual}.
+We have also adapted MixEth to operate within a state channel.
+We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}.
+This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic.
+Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront.
+In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$.
+To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state.
+The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round.
+In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass.
+In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
+To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.
+
+Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic.
+Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic.
+This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle.
+After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round.
+Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.
+If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur.
+In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain.
+A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.
+Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
+The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}.
+Note that all three $N$s are the same.
+In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.
+
+\begin{table}[H] 
+	\caption{Proof-of-concept implementation gas cost results.
+Expect further improvements.
+MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\centering 
+	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
+		\toprule
+		\hline
+		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
+		\cline{4-5}&&&Shuffle upload&Challenge\\
+		\hline
+		\midrule
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{227563}&\num[group-separator={,}]{113265}  \\
+		MixEthChannel&TBD&TBD&0&0&TBD\\
+		\bottomrule
+	\end{tabular}
+	\label{table:securityproperties}
+\end{table}
 
@@
 \begin{table}[H] 
-\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol.
+\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
 Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
@@
 	Miximus \cite{miximus2018} & 1+MPC & 2 \\
-	MixEth & 1 & 2 \\
+	MixEth & 1 & 3 \\
 	MixEthChannel  & $\mathcal{O}(n)$ &2 \\
@@
 \section{Acknowledgements}
-We would like to thank barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+We would like to thank Liam Horne, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 

### 2018-11-26 article/main.tex
Updated acknowledgements

@@
 \section{Future work}
-We are going to implement and deploy MixEth on Ethereum and evaluate its performance. We are also going to give formal security proofs for the claimed security properties.  
-An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround and upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
+We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
+An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
 
 \section{Acknowledgements}
-We would like to thank Liam Horne, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+Chris Buckland is supported by an Ethereum Foundation
+scaling grant and an Ethereum Community Fund grant.
+We would like to thank Liam Horne, Patrick McCorry, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 

### 2018-11-28 article/main.tex
Proof of availability added

@@
 \end{abstract}
-\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer}
+\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer, State Channel}
 
@@
 Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.
-
-\textbf{Our contributions.} In this paper, we present MixEth, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity already achieved by previous proposals.
+As the Ethereum network is congested, ie.
+blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
+
+\textbf{Our contributions.} In this paper, we present MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals.
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
+
+We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
+Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back to on-chain.
 
@@
 \subsection{Availability}
-If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the soundness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
+If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
 \subsection{Theft prevention} 
@@
 \end{wrapfigure}
-\newpage
+
 \subsection{State channel implementation} \label{statechannelimpl}
@@
 
-\section{Conclusion} \label{conclusion}
-
-\section{Future work}
+\section{Conclusion and Future Work} \label{conclusion}
 We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
@@
 \section{Proof of Availability}  \label{appendavail}
+
+The only possibility for an adversary to threaten the availability of funds for an honest receiver if they create an incorrect shuffle, where honest receiver's shuffled public key is compromised.
+Since the Chaum-Pedersen zero-knowledge protocol is complete, an honest receiver is alway able to create a Chaum-Pedersen proof, which demonstrates to the contract that their shuffled public key is compromised.
+Therefore we have for any PPT $\adv$ and $\forall \lambda \in \mathbb{N}$ that, $$\Pr[\textsf{G}^{avail}_{mix, \adv}]=0<negl(\lambda).$$
+
 \section{Proof of Theft Prevention} \label{appendtheft}

### 2018-12-05 article/main.tex
Added Aztec protocol to related work and updated our contribution

@@
 
-The two major techniques to provide mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
+There is no doubt that there exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
+This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.
+
+The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
 Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases.
@@
 
-\textbf{Our contributions.} In this paper, we present MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals.
+Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
+
+\textbf{Our contributions.} In this paper, we present an efficient mixing protocol for Turing-complete blockchains.
+This protocol can be used to shuffle cyphertexts, ballots or public keys.
+The protocol have many usecases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
+
+To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
@@
 In our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
-Since on-chain storage is extremely expensive, we decided to store only the last two sets of shuffled public keys.
-Note that storing only the latest shuffle would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first shuffled key is also available for the contract.
-Such a storage structure implies that after uploading the new shuffled keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle.
+Since on-chain storage is extremely expensive ($\num[group-separator={,}]{20000}$ gas to store a $256$-bit number), we decided to store only the last two cryptographic accumulators of shuffled public keys.
+Note that storing only the latest shuffle's accumulator would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first shuffled key is also available for the contract to check its set-membership.
+Such a storage structure implies that after logging the new shuffled keys and uploading the updated accumulator, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is contained in the accumulator.
 Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions are sufficient to complete the protocol.
@@
 We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.
+
+We chose to implement a pairing-based cryptographic accumulator \cite{catalano2013vector}, since it allows constant-size updates and deletes to the accumulator, while also the set-membership proof is constant-size.
 
@@
 However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
-$300$.
+$\num[group-separator={,}]{15000}$.
 
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&\num[group-separator={,}]{99254}&\num[group-separator={,}]{138653}+\num[group-separator={,}]{40000}n&\num[group-separator={,}]{227563}&\num[group-separator={,}]{113265}  \\
+		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{512}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
 		MixEthChannel&TBD&TBD&0&0&TBD\\
@@
 
+\subsection{Additional related work}
+Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}.
+Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes.
+Later on Aztec notes can be traded in a join-split style confidential transaction, namely the value of the traded Aztec notes are encrypted and not visible to outsiders.
+A join-split style transaction can have multiple inputs and outputs.
+Aztec applies zero-knowledge proofs and range proofs in order to achieve that the sum of inputs traded in a confidential transaction is greater or equal than the sum of outputs.
+The gas cost of a confidential Aztec transaction is $\num[group-separator={,}]{219000}$+$\num[group-separator={,}]{121000}n$+$\num[group-separator={,}]{41000}m$, where $n$ and $m$ are the numbers of inputs and outputs respectively.
+Although Aztec is not a coin mixer, it can be used not only to provide confidential transaction, but also to increase anonymity.
+On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes.
+Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions.
+For instance on top Aztec one could use MixEth to shuffle Aztec notes.
+
 \section{Extensions and improvements}

### 2018-12-07 article/main.tex
Updated paper

@@
 \begin{abstract}
-Cryptocurrencies enable users to transact with each other without relying on trusted parties or intermediaries.
+Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries.
 These transactions are recorded in an immutable, publicly verifiable ledger.
@@
 MixEth is more efficient than any proposed trustless coin tumbler.
-It requires only $3$ on-chain transactions at most per user and $1$ off-chain.
+It requires only $3$ on-chain transactions at most per user and $1$ off-chain message.
 It achieves strong notions of anonymity and is able to resist denial-of-service attacks.
+Furthermore the underlying protocol can also be used to efficiently shuffle ballots, cyphertexts in a trustless and decentralized manner.
 \end{abstract}
@@
 
-\textbf{Our contributions.} In this paper, we present an efficient mixing protocol for Turing-complete blockchains.
+\textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains.
 This protocol can be used to shuffle cyphertexts, ballots or public keys.
-The protocol have many usecases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
+The protocol have many use cases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
 
@@
 \section{Background}
+In this section we introduce the building bocks required to create our mixing protocol and MixEth, the trustless coin tumbler.
 \subsection{Notations}
@@
 
-Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decisional Diffie-Hellman (DDH) problem.
+Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decision Diffie-Hellman (DDH) problem.
 Therefore, Neff's verifiable shuffle can also be applied in groups over elliptic curves.
@@
 EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}.
-In every gas the sender needs to pay upfront for the execution of the contract's code.
+In every transaction the sender needs to pay upfront for the execution of the contract's code.
 The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price.
@@
 The insight of these proposals is that it is not needed to conduct all transactions on the blockchain, since participants could lock funds on-chain and afterwards securely issue transactions off-chain, for instance micropayments, with high degree of security and finality.
-They only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
+Participants only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
 The first implementation of this idea was a payment channel network for Bitcoin called Lightning network \cite{poon2016bitcoin}.
@@
 Since then several other frameworks for generalised state channels were elaborated (\cite{dziembowski2017perun},\cite{mccorryyou}).
-Recently a case study of the Battleship game was published Patrick McCorry, Chris Buckland et al.
+Recently a case study of the Battleship game was published by Patrick McCorry, Chris Buckland et al.
 to evaluate how state channels could contribute in scaling blockchain-based applications \cite{mccorryyou}.
@@
 
-After some period of time no more deposits are allowed to the tumbling contract.
 Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
 Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve.
-be Every recipient of the mix is allowed to shuffle the public keys at most once:
+Anyone is allowed to shuffle the public keys at most once by paying some deposit to the tumbler contract:
 
@@
 
-$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*})$: after the end of the shuffling period users are allowed to withdraw their funds.
+$tx\stackrel{\$}{\leftarrow}WithdrawShufflingDeposit(sk_B)$: after a challenging period a shuffler can withdraw their shuffling deposit from the tumbler contract.
+
+$0\lor1\leftarrow VerifyWitdhrawShufflingDeposit(pk_B)$: if there was no successful challenges against the shuffler, i.e. their deposit is not slashed, they can withdraw their shuffling deposit.
+
+$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*}_{final})$: after the end of the shuffling period users are allowed to withdraw their funds.
 Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}_{final}$, the final shuffling accumulated constant.
@@
 	\begin{tabular}{cccc}    
-		\begin{minipage}{5.5cm}
+		\begin{minipage}{5cm}
 			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
@@
 		&
+		\begin{minipage}{5.7cm}
+			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
+				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
+		\end{minipage}
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{ccc}
 		\begin{minipage}{6.3cm}
-			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, C^{*}$)}{%
+			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, PK^{'}$)}{%
 				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
 				if\ (sC^{*} \notin PK) \ return\ 0 \\
+				delete (C^{'},PK^{'})\\
+				slashDeposit(shuffler(C^{'},PK^{'}))\\
 				\pcreturn 1  }
 		\end{minipage}
+		&
+		\begin{minipage}{4.6cm}
+			\procedure{\textsf{WithdrawShufflingDeposit($sk_{A}$)}}{%
+				\pcreturn \textsf{FormTx($sk_{A}, id_{contract},0$)} }
+		\end{minipage}
+		&
+		\begin{minipage}{4.6cm}
+			\procedure{\textsf{VerifyWithdrawShufflingDeposit($pk_{A}$)}}{%
+				\pcreturn shufflingDepositSlashed(pk_{A}) }
+		\end{minipage}
 	\end{tabular}
@@
 	\begin{tabular}{cccc}    
-		\begin{minipage}{4.5cm}
-			\procedure{\textsf{Withdraw($C^{*},sC^{*}$)}}{%
+		\begin{minipage}{4.7cm}
+			\procedure{\textsf{Withdraw($s,C^{*}$)}}{%
 				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
-				\pcreturn \textsf{FormTx($sC^{*}, id_{\textsf{contract}, 0}, \sigma,$)} }
+				\pcreturn \textsf{FormTx($s,C^{*}, id_{\textsf{contract}, 0}, \sigma$)} }
 		\end{minipage}
@@
 All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
-
+\newpage
 \subsection{Fully on-chain implementation} \label{fullyonchainimpl}
@@
 
-In our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
-Since on-chain storage is extremely expensive ($\num[group-separator={,}]{20000}$ gas to store a $256$-bit number), we decided to store only the last two cryptographic accumulators of shuffled public keys.
-Note that storing only the latest shuffle's accumulator would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first shuffled key is also available for the contract to check its set-membership.
-Such a storage structure implies that after logging the new shuffled keys and uploading the updated accumulator, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is contained in the accumulator.
-Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions are sufficient to complete the protocol.
-However shufflers need to withdraw their shuffling deposits with an additional on-chain transaction.
+Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
+There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender.
+The rest of the protocol happens entirely on-chain.
+
+On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas.
+To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
+Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
+Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}.
+Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.
 We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.
-
-We chose to implement a pairing-based cryptographic accumulator \cite{catalano2013vector}, since it allows constant-size updates and deletes to the accumulator, while also the set-membership proof is constant-size.
 
@@
 This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
+A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
 However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
-$\num[group-separator={,}]{15000}$.
+$\num[group-separator={,}]{800}$.
 
@@
 
+\newpage
 \subsection{State channel implementation} \label{statechannelimpl}
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{512}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
 		MixEthChannel&TBD&TBD&0&0&TBD\\
@@
 	\end{tabular}
-	\label{table:securityproperties}
+	\label{table:gasproperties}
 \end{table}
@@
 Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
-Authors of Möbius provided formal definitions of various notions of securty such as anonymity, theft prevention and mixer availability.
+Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability.
 These properties could be used to evaluate and compare existing and future proposals from a security perspective.
@@
 If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
-Another, maybe even more severe problem with Möbius is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
+Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
 When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
-Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius is not guaranteed.
+Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.
 
@@
 As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
-In spite of this seemingly added complexity, we are confident that these 3 (deposit, shuffle, withdraw) transactions consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus.
+In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
 \begin{table}[H] 
@@
 
+In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
+This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
+
 \section{Conclusion and Future Work} \label{conclusion}
@@
 scaling grant and an Ethereum Community Fund grant.
-We would like to thank Liam Horne, Patrick McCorry, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 

### 2018-12-13 article/shortpaper/main.tex
Added short paper version of the paper

--- 2018-12-07 article/main.tex
@@
 
-There is no doubt that there exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
-This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.
-
 The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
@@
 blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
-
-Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
 
@@
 \section{Background}
-In this section we introduce the building bocks required to create our mixing protocol and MixEth, the trustless coin tumbler.
 \subsection{Notations}
@@
 Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.
-
-\subsection{Verifiable shuffle}
-
-Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}.
-It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers.
-The output of the shuffle is another $k$ modular integers raised to the same secret exponent only known to the shuffler.
-The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly.
-
-Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decision Diffie-Hellman (DDH) problem.
-Therefore, Neff's verifiable shuffle can also be applied in groups over elliptic curves.
-
-Verifiable shuffle can be used to shuffle a set of public keys, $PK=(s_{1}G,s_{2}G\dots,s_{k}G)$. Note that secret keys are not known to the shuffler.
-
-\begin{enumerate}
-	\item Shuffler commits to $C=cG$, publishes $$PK^*=(c(s_{\pi^{-1}(1)}G),c(s_{\pi^{-1}(2)}G),\dots,c({s_{\pi^{-1}(k)}}G))$$ where $\pi$ is a random permutation.
-Shuffler additionally computes and publishes a zero-knowledge proof about the correctness of the shuffle.
-This proof can be made non-interactive via the Fiat-Shamir heuristic.
-Let us call $C$ as the shuffling constant.
-	\item Assuming the proof verifies users gain new public keys with respect to another generator element, namely $cG$.
-\end{enumerate}
-
-For verifying the proof one needs to compute $8k+5$ exponentiations, however later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.
-
-So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.
-The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.
 
@@
 
-In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e.
-no efficient adversary could forge a signature on any given message with non-negligible probability.
-
 \subsection{Ethereum}
@@
 Codes are executed in a quasi-Turing complete execution environment, called Ethereum Virtual Machine (EVM).
-
-EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}.
-In every transaction the sender needs to pay upfront for the execution of the contract's code.
-The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price.
-Therefore the transaction fee is the gas cost multiplied by the gas price.
-One needs to specify a gas limit, meaning that they do not allow their transaction to burn more gas than the limit.
-If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner.
-If there are gas left after successful execution, transaction originator is reimbursed.
-Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block.
-Currently the block gas limit is cca.
-$\num[group-separator={,}]{8000000}$ gas.
-Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees.
-Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.
 
@@
 
-\subsubsection{Ethereum account abstraction}
-Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
-When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they can not do this from a fresh address, since it does not hold any ether.
-Since as of now only the sender of a transaction can pay for the gas fee, users can not withdraw their funds unless they ask someone to fund their fresh address.
-
-Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}.
-EIP86 permits receivers of a transaction paying the gas fee.
-This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses.
-Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
-This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA).
-Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
-
-\section{Threat model}
-\subsection{Participants and interactions}
-In a decentralized tumbler, we have $3$ distinct entities: the tumbling smart contract, a set of senders and a set of receivers.
-A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys.
-In all the following interactions and algorithms we assume that the public state of the tumbler is implicitly given as input.
-Interactions of these entities can be summarized as follows:
-
-$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.
-
-$0/1\leftarrow VerifyDeposit(tx)$: The tumbler contract checks the validity of senders' deposits.
-
-$ProcessDeposit(tx)$: upon receiving a valid deposit transaction, the mixing contract updates its internal state accordingly.
-
-Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
-Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve.
-Anyone is allowed to shuffle the public keys at most once by paying some deposit to the tumbler contract:
-
-$PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
-Let us call $C^{*}_{i}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
-The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period.
-The permutation $\pi$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
-All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.
-
-$0\lor1\leftarrow 
-ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is DDH-tuples: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$.
-If the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
-This proof and checks allow one to be certain that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
-
-$tx\stackrel{\$}{\leftarrow}WithdrawShufflingDeposit(sk_B)$: after a challenging period a shuffler can withdraw their shuffling deposit from the tumbler contract.
-
-$0\lor1\leftarrow VerifyWitdhrawShufflingDeposit(pk_B)$: if there was no successful challenges against the shuffler, i.e. their deposit is not slashed, they can withdraw their shuffling deposit.
-
-$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*}_{final})$: after the end of the shuffling period users are allowed to withdraw their funds.
-Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}_{final}$, the final shuffling accumulated constant.
-
-$0/1\leftarrow VerifyWithdraw(tx)$: tumbler checks the validity of a recipient's withdrawal transaction.
-
-$ProcessWithdraw(tx)$: upon receiving a valid withdrawal transaction, mixing contract updates its internal state accordingly.
-
-\subsection{Security goals} \label{securitygoals}
+\section{Security goals} \label{securitygoals}
 We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
-These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
+These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}.
 
@@
 
-In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles.
-CORR enables $\adv$ to corrupt a sender or receiver by learning the secret key of any party $l$ of their choice.
-Oracle access to AD or AW allow $\adv$ to deposit or withdraw respectively from tumbler session $j$.
-Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW.
-In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
-
-These oracles are formally defined as follows:
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{6cm}
-			\procedure{AD(tx,$j$)}{%
-				b \leftarrow VerifyDeposit(tumblers[j],tx) \\
-				if\ (b) \ ProcessDeposit(tumblers[j],tx) \\
-				\pcreturn b  }
-		\end{minipage}
-		&
-		\begin{minipage}{6cm}
-			\procedure{AW(tx,$j$)}{%
-				b \leftarrow VerifyWithdraw(tumblers[j],tx) \\
-				if\ (b) \  ProcessWithdraw(tumblers[j],tx) \\
-				\pcreturn b  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{CORR($l$)}{%
-				C=C.push(pk_{B_{l}}) \\
-				\pcreturn sk_{B_l}}
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cc}   
-\begin{minipage}{5cm}
-	\procedure{HD($i$,$j$,$l$)}{%
-		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}})\\
-		H_{d}=H_{d}.push(tx) \\
-		ProcessDeposit(tumblers[j],tx)\\
-		\pcreturn tx }
-\end{minipage}
-&
-\begin{minipage}{5cm}
-	\procedure{HW($j$,$l$)}{%
-		if\ (pk_{B_{l}} \notin tumblers[j].keys_{B})\ return \ \bot \\
-		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}}) \\
-		H_{w}=H_{w}.push(j,l,tx) \\
-		ProcessWithdraw(tumblers[j],tx)\\
-		\pcreturn tx }
-\end{minipage}
-\end{tabular}
-\end{table}
-
-From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.
-
 \subsubsection{Anonymity} \label{sec:defanonymity}
@@
 \textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
-
-\begin{definition}
-	Define $\textbf{Adv}^{d-anon}_{mix,\adv}(\lambda) = 2\Pr[\textsf{G}^{d-anon}_{mix,\adv}(\lambda)]-1\ for\ d \in \{dep, with\}$, where these games are defined as follows:
-
-	\begin{table}[H]
-		\centering
-		\begin{tabular}{cc}    
-			\begin{minipage}{7cm}
-					\procedure{MAIN $\textsf{G}^{dep-anon}_{mix,\adv}(\lambda)$}{%
-						(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
-						\textsf{PK}_A\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
-						b \stackrel{\$}{\leftarrow} \bin \\
-						(state,j,pk, i_{0},i_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{A}) \\
-						tx \stackrel{\$}{\leftarrow} Deposit(tumblers[j], sk_{A_{{l}_{b}}}, pk) \\
-						b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
-						\pcreturn b = b^{’} }
-			\end{minipage}
-			&
-			\begin{minipage}{7cm}
-				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
-					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
-					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
-					b \stackrel{\$}{\leftarrow} \bin \\
-					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
-					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
-					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
-					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
-					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
-					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
-					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
-					\pcreturn b = b^{’} }		
-			\end{minipage}
-		\end{tabular}
-	\end{table}	
-Then the tumbler satisfies sender or recipient anonymity if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.
-\end{definition}
 
@@
 
-\begin{definition}
-	Define $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{avail}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
-
-	\begin{table}[H]
-		\centering
-		\begin{tabular}{c}    
-			\begin{minipage}{7cm}
-				\procedure{MAIN $\textsf{G}^{avail}_{mix,\adv}(\lambda)$}{%
-					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
-					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w} \leftarrow \emptyset\\
-					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
-					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l})) \\
-					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
-					\pcreturn (b=0)\land(pk_{l}\in tumblers[j].keys_{B})}
-			\end{minipage}
-		\end{tabular}
-	\end{table}	
-	Then the tumbler satisfies availability if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
-\end{definition}
-
 \subsubsection{Theft prevention} \label{sec:theftprevention}
-We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:
-
-\begin{definition}
-	Define $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{theft}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
-
-	\begin{table}[H]
-		\centering
-		\begin{tabular}{c}    
-			\begin{minipage}{7cm}
-				\procedure{MAIN $\textsf{G}^{theft}_{mix,\adv}(\lambda)$}{%
-					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
-					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w}, \textsf{contract} \leftarrow \emptyset\\
-					(\textsf{tx},j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,AW,HW}(1^{\lambda},\textsf{PK}_{B}) \\
-					if(\textsf{tumblers}[j].\textsf{keys}_{B}\not\subset \textsf{PK}_{B}\setminus C)\ return \ 0 \\
-					\pcreturn \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{tx})}
-			\end{minipage}
-		\end{tabular}
-	\end{table}	
-	Then the tumbler satisfies theft prevention if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
-\end{definition}
+We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.
 
@@
 
-\subsection{MixEth formal specification}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{5.5cm}
-			\procedure{\textsf{Deposit}($sk_A, pk_{B}$)}{%
-				\pcreturn \textsf{FormTx}(sk_A,id_{\textsf{contract}}, amt, pk_{B}) }
-		\end{minipage}
-		&
-		\begin{minipage}{5.4cm}
-			\procedure{\textsf{VerifyDeposit}(tx)}{%
-				if\ (tx[amt] \neq id_{\textsf{contract}}[amt]) \ return\ 0 \\
-				if\ (pk_{B} \notin \mathbb{G}) \ return\ 0 \\
-				\pcreturn \textsf{VerifyTx(tx)}  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{\textsf{ProcessDeposit(tx)}}{%
-				add\ \textsf{addr(tx[pk]) to initPubKeys[]}}
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{5cm}
-			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
-				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
-				C^{'*} \leftarrow cC^{*} \\
-				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
-				\pcreturn (PK^{'},C^{'*}) }
-		\end{minipage}
-		&
-		\begin{minipage}{5.7cm}
-			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
-				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{ccc}
-		\begin{minipage}{6.3cm}
-			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, PK^{'}$)}{%
-				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
-				if\ (sC^{*} \notin PK) \ return\ 0 \\
-				delete (C^{'},PK^{'})\\
-				slashDeposit(shuffler(C^{'},PK^{'}))\\
-				\pcreturn 1  }
-		\end{minipage}
-		&
-		\begin{minipage}{4.6cm}
-			\procedure{\textsf{WithdrawShufflingDeposit($sk_{A}$)}}{%
-				\pcreturn \textsf{FormTx($sk_{A}, id_{contract},0$)} }
-		\end{minipage}
-		&
-		\begin{minipage}{4.6cm}
-			\procedure{\textsf{VerifyWithdrawShufflingDeposit($pk_{A}$)}}{%
-				\pcreturn shufflingDepositSlashed(pk_{A}) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{4.7cm}
-			\procedure{\textsf{Withdraw($s,C^{*}$)}}{%
-				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
-				\pcreturn \textsf{FormTx($s,C^{*}, id_{\textsf{contract}, 0}, \sigma$)} }
-		\end{minipage}
-		&
-		\begin{minipage}{6.3cm}
-			\procedure{\textsf{VerifyWithdraw(tx)}}{%
-				if\ (sC^{*} \notin id_{\textsf{contract}}[lastShuffle] ) \ return\ 0 \\
-				if\ (\lnot\verify(C^{*}, sC^{*},\sigma, sC^{*}||tx.sender)) \ return\ 0 \\
-				\pcreturn \textsf{VerifyTx(tx)}  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{\textsf{ProcessWithdraw(tx)})}{%
-				delete\ sC^{*} from\ id_{\textsf{contract}}[lastShuffle]   \\
-				tx^{'}\stackrel{\$}{\leftarrow} \textsf{FormTx}(id_{contract}, tx.sender, amt) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\section{Security}
-This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.
+\section{Informal reasoning about security properties}
 
@@
 Reduction proof is enclosed in Appendix \ref*{appendtheft}.
-\begin{table}[H] 
-	\caption{Security properties achieved by each coin mixing protocol.}
-	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}
-
-		\toprule
-		\hline
-		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
-		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
-		\hline
-		\midrule
-		\textbf{Centralized} & & \\
-		\midrule
-		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
-		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
-		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
-		\midrule
-		\textbf{Decentralized}      &    &      \\
-		\midrule
-		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
-		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
-		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
-		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
-		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
-		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
-		\bottomrule
-	\end{tabular}
-	\label{table:securityproperties}
-\end{table}
 
@@
 All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
-\newpage
+
 \subsection{Fully on-chain implementation} \label{fullyonchainimpl}
@@
 
-\newpage
 \subsection{State channel implementation} \label{statechannelimpl}
@@
 
-\section{Related work}
-Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
-Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability.
-These properties could be used to evaluate and compare existing and future proposals from a security perspective.
-Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
-However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
-No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
-If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
-Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
-When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
-Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.
-
-Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}.
-It uses zkSNARKs to conceal the mapping between depositors and recipients.
-A depositor creates a leaf in a Merkle-tree.
-A depositor needs to exchange the preimage of the leaf with the recipient.
-Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf.
-So called nullifiers enable recipients to withdraw funds once and only once.
-The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
-However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
-Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
-If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
-Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
-
-As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
-In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
-\begin{table}[H] 
-\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
-Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
-\centering 
-\begin{tabular}{lcc}
-
-	\toprule
-	&\#Off-chain messages& \#Transactions \\
-	\midrule
-	\textbf{Centralized} & & \\
-	\midrule
-	Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
-	Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
-	TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
-	\midrule
-	\textbf{Decentralized}      &    &      \\
-	\midrule
-	Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
-	Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
-	XIM \cite{bissias2014sybil} & 0      & 7       \\
-	Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
-	Miximus \cite{miximus2018} & 1+MPC & 2 \\
-	MixEth & 1 & 3 \\
-	MixEthChannel  & $\mathcal{O}(n)$ &2 \\
-	\bottomrule
-\end{tabular}
-\label{table:communicationcomplexity}
-\end{table}
-
-\subsection{Additional related work}
-Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}.
-Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes.
-Later on Aztec notes can be traded in a join-split style confidential transaction, namely the value of the traded Aztec notes are encrypted and not visible to outsiders.
-A join-split style transaction can have multiple inputs and outputs.
-Aztec applies zero-knowledge proofs and range proofs in order to achieve that the sum of inputs traded in a confidential transaction is greater or equal than the sum of outputs.
-The gas cost of a confidential Aztec transaction is $\num[group-separator={,}]{219000}$+$\num[group-separator={,}]{121000}n$+$\num[group-separator={,}]{41000}m$, where $n$ and $m$ are the numbers of inputs and outputs respectively.
-Although Aztec is not a coin mixer, it can be used not only to provide confidential transaction, but also to increase anonymity.
-On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes.
-Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions.
-For instance on top Aztec one could use MixEth to shuffle Aztec notes.
-
-\section{Extensions and improvements}
-MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround.
-A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant.
-MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.
-
-In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
-This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
-
-\section{Conclusion and Future Work} \label{conclusion}
-We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
-An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
-
 \section{Acknowledgements}
@@
 
-\begin{appendices}
-
-\section{Proof of Anonymity} \label{appendanon}
-Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
-
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\centering
-\begin{bbrenv}{A}
- \begin{bbrbox} [name=\bdv]
- \pseudocode {
- 	 \text{$c_{1}\stackrel{\$}{\leftarrow}\mathbb{Z}_p$} \\
-	 \text{$\textsf{PK}_{B} = (c_{0}G, c_{1}G)$} \\
-	 \text{$b \stackrel{\$}{\leftarrow} \bin $} \\
-	 \text{$tx \stackrel{\$}{\leftarrow}Withdraw(tumblers[j],sk_{B_{c_{b}}})$}
-	 }
-
- \begin{bbrenv}{B}
- \begin{bbrbox}[name=\adv]
- \pseudocode{
- 	 \text{Input: $PK_{B}, tx$} \\
-	 \text{Output: $b^'$}
-	 }
- \end{bbrbox}
-
- \end{bbrenv}
-
- \end{bbrbox}
-
- \bbrinput{$(sG,cG,c_{0}G)$}
- \bbroutput{$\lnot b\lnot{b^'}+b$}
-\end{bbrenv}
-
-\captionof{figure}{An illustration for the reduction of withdrawal anonymity to the DDH assumption}
-\end{wrapfigure}
-
-Towards contradiction let us assume that the recipient anonymity does not hold.
-Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(sG,cG,c_{0}G)$.
-Adversary $\bdv$ generates uniformly random public key $c_{1}G$ and invokes $\adv$ with the set $\textsf{PK}_{B}=(c_{0}C^{*}, c_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
-Then a withdrawal transaction occurs from $c_{b}G$.
-After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will output $\lnot b^{'}$.
-If $\adv$ outputs $0$ and $b=b^{'}$, this signals to $\bdv$ that $c_{0}G$ might potentially be of the form $scG=c_{0}G$  i.e.
-it is a DDH tuple, therefore $\bdv$ outputs $1$.
-In all the other cases $\bdv$ outputs a random bit.
-Therefore we have that $\bdv$ has an adventage in their DDH-game if and only if $\adv$ wins their $\textsf{G}^{with, anon}_{mix, \adv}$ security game.
-Since we assumed that recipient anonymity does not hold we have that $$\Pr[\textsf{DDH}_{\bdv}]=\frac{1}{2}+\frac{1}{2}*\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\frac{1}{2}+\frac{1}{2}*\textsf{non-negl}(\lambda),$$ which contradicts to the DDH assumption.
-
-\section{Proof of Availability}  \label{appendavail}
-
-The only possibility for an adversary to threaten the availability of funds for an honest receiver if they create an incorrect shuffle, where honest receiver's shuffled public key is compromised.
-Since the Chaum-Pedersen zero-knowledge protocol is complete, an honest receiver is alway able to create a Chaum-Pedersen proof, which demonstrates to the contract that their shuffled public key is compromised.
-Therefore we have for any PPT $\adv$ and $\forall \lambda \in \mathbb{N}$ that, $$\Pr[\textsf{G}^{avail}_{mix, \adv}]=0<negl(\lambda).$$
-
-\section{Proof of Theft Prevention} \label{appendtheft}
-
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\centering
-	\begin{bbrenv}{A}
-		\begin{bbrbox} [name=\bdv]
-			\pseudocode {
-				\text{$(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]$} \\
-				\text{$\textsf{PK}_{B}\leftarrow\{pk_{i}\}_{i=1}^{n}$;$C, H_{\omega}, contract \leftarrow \emptyset$}
-			}
-
-			\begin{bbrenv}{B}
-				\begin{bbrbox}[name=\adv]
-					\pseudocode{
-						\text{Input: $(1^{\lambda},PK_{B})$} \\
-						\text{$(tx,j) \stackrel{\$}{\leftarrow}\adv^{CORR,AD,AW,HW}(1^{\lambda},PK_{B})$} \\
-						\text{Output: $(tx,j)$}
-					}
-				\end{bbrbox}
-
-			\end{bbrenv}
-
-		\end{bbrbox}
-		\bbrinput{$1^\lambda$}
-		\bbroutput{$(tx,\sigma_{tx})$}
-	\end{bbrenv}
-
-	\captionof{figure}{An illustration for the reduction of theft prevention to the existentially unforgeability of ECDSA.}
-\end{wrapfigure}
-
-Towards contradiction we assume that there exists an adversary $\adv$, who is able to break the theft prevention property introduced in Section \ref{sec:theftprevention} with non-negligible probability.
-Using such an adversary as a subroutine we could create another efficient adversary $\bdv$ who is able to break the existential unforgeability of ECDSA.
-The input of the forgeability game is the security parameter which is forwarded to $\adv$ along with $n$ randomly generated public keys.
-By assumption $\adv$ outputs with non-negligible probability valid withdraw transaction belonging to one of the public keys in the mixer.
-$\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
-$\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
-$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$. This contradicts to the assumption that ECDSA is existentially unforgeable.
-
-\end{appendices}
-
 \end{document}

### 2018-12-18 article/shortpaper/main.tex
Short paper updated

@@
 
-We use games in definitions and proofs of security.
-At the end of each game, the main procedure of game \textsf{G} outputs a single bit.
-$\Pr(\textsf{G})$ denotes the probability that the output is $1$.
 \subsection{Cryptographic keys in Ethereum}
@@
 
-\subsection{Ethereum}
-
-Ethereum is a cryptocurrency built on top of a blockchain.
-Similarly to Bitcoin, network participants broadcast transactions in a peer-to-peer network, where transactions are bundled together into blocks that are appended to a public ledger called blockchain.
-Only those specific nodes can append new blocks to the blockchain who previously solved a difficult cryptographic puzzle.
-The state of the system consists of the state of different accounts populating it.
-
-In Ethereum currently there are two types of accounts.
-The first account type is called \textit{externally owned account}.
-It owns an ECDSA keypair controlled by its user.
-Private keys are used to sign transactions.
-On the other hand there are \textit{contract accounts}, often smart contracts, that additionally have persistent storage and contract's code.
-Both of the account types have Ether balances, which is the native currency of the Ethereum network.
-Ether is denominated in wei, where $1\ ETH = 10^ {18}\ wei$.
-
-Transactions can alter the system's state by either creating a contract account or by calling to an existing account.
-Transactions to externally owned accounts can only transfere Ether, while transactions to contract accounts can additionally execute the code associated with them.
-Codes are executed in a quasi-Turing complete execution environment, called Ethereum Virtual Machine (EVM).
-
-\subsubsection{State channels} 
+\subsection{State channels} 
 Public blockchain's decentralization comes at an inherent cost in regard to scalability, since currently each full node verifies the full state of the public ledger.
@@
 
-\subsubsection{Anonymity} \label{sec:defanonymity}
-\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
-
+\begin{itemize}
+	\item \textbf{Anonymity}: \textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
 \textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
-
-\subsubsection{Availability}
-It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and one but all recipients are compromised.
-
+	\item \textbf{Availability}: means that honest recipients can always withdraw their assets from the mixer, even if all participants are compromised.
 Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient can not withdraw their funds.
-
-\subsubsection{Theft prevention} \label{sec:theftprevention}
-We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.
+	\item \textbf{Theft prevention}: We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.
+\end{itemize}
 
 \section{MixEth}
-
-\subsection{Overview}
-MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
-\subsection{Initializing the tumbler}
+\subsection{Initializing the tumbler and depositing period}
 
 A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
-
-\subsection{Depositing period}
 Every sender must deposit exactly $amt$ ether to a specific public key.
@@
 \begin{algorithmic}[1]
-	\State $PK_{i} \gets []$
-	\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
+	\State $PK_{i} \gets []
+ ,c\stackrel{\$}{\leftarrow}\mathbb{Z}_n,\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$
 	\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
 	\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
-	\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
 	\For{$j=0;j<|PK_{i-1}|;j++$}
@@
 
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\centering
+	\includegraphics[scale=0.5]{./withdrawalComplexity.jpg}
+	\captionsetup{justification=centering}
+	\caption{Gas complexity of withdraw txs for various trustless Ethereum coin mixers}
+\end{wrapfigure}
+
 \subsection{Withdrawing}
@@
 
-\subsection{Recipient anonymity}
+\begin{itemize}
+\item \textbf{Recipient anonymity}
 The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$.
-This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds.
+This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest participant shuffled and the DDH assumption holds.
 Adversary can only distinguish between honest recipients public keys with negligible probability.
-See reduction proof in Appendix \ref*{appendanon}.
-\subsection{Availability}
+\item \textbf{Availability}
 If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
-\subsection{Theft prevention} 
+\item \textbf{Theft prevention} 
 If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient.
 This contradicts to the assumption that ECDSA is existentially unforgeable.
-Reduction proof is enclosed in Appendix \ref*{appendtheft}.
-
+\end{itemize}
 \section{Implementation}
 
-\begin{wrapfigure}{r}{0.7\textwidth}
-	\centering
-	\includegraphics[scale=0.7]{./withdrawalComplexity.jpg}
-	\captionsetup{justification=centering}
-	\caption{Gas complexity of withdraw transactions for various trustless Ethereum coin mixers}
-\end{wrapfigure}
-
-We implemented MixEth with two different approaches.
-The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
+We implemented MixEth in Solidity with two different approaches.
+The first one does not apply state channels, all the transactions are made on-chain.
 This could lead to unwanted gas costs as the number of corrupted shuffles increases.
@@
 Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
-Both of the implementations allow users to mix Ether or other ERC20-compatible, a popular Ethereum token standard, tokens.
+Both of the implementations allow users to mix Ether or other ERC20-compatible tokens.
 
@@
 This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
-
-All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts.
-MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions.
-Note that these implementations are only proof-of-concept implementations, expect further improvements.
-All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
 

### 2018-12-18 article/shortpaper/main.tex
Short paper updated vol2

@@
 
-One of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
+The bottleneck of coin mixing protocols is the withdrawal transactions' gas costs.
 A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
@@
 Also note that the on-chain cost of a shuffle transaction could be amortized among participants.
-Specifically if there is a group of senders and/or receivers who trust each other they could collectively charge any of them to shuffle once.
+Specifically if there is a group of senders or receivers who trust each other they could collectively charge any of them to shuffle once.
 Since they trust their peer, all the rest of the group does not need to shuffle anymore.

### 2018-12-19 migrations/4_MixEth_migration.js
Rinkeby deployment

@@ -6,6 +6,7 @@ let ECDSAGeneralized = artifacts.require("./ECDSAGeneralized.sol");
 module.exports = async function(deployer) {
   deployer.deploy(EC);
   deployer.link(EC, MixEth);
+  deployer.link(EC, ChaumPedersenVerifier);
   deployer.deploy(ChaumPedersenVerifier);
   deployer.link(ChaumPedersenVerifier, MixEth);
   deployer.deploy(EC);

### 2018-12-19 truffle.js

@@ -1,16 +1,19 @@
 /*
- * NB: since truffle-hdwallet-provider 0.0.5 you must wrap HDWallet providers in a 
+ * NB: since truffle-hdwallet-provider 0.0.5 you must wrap HDWallet providers in a
  * function when declaring them. Failure to do so will cause commands to hang. ex:
  * ```
  * mainnet: {
- *     provider: function() { 
- *       return new HDWalletProvider(mnemonic, 'https://mainnet.infura.io/<infura-key>') 
+ *     provider: function() {
+ *       return new HDWalletProvider(mnemonic, 'https://mainnet.infura.io/<infura-key>')
  *     },
  *     network_id: '1',
  *     gas: 4500000,
  *     gasPrice: 10000000000,
  *   },
  */
+ let HDWalletProvider = require('truffle-hdwallet-provider');
+let mnemonic = 'dream pilot judge begin office silent improve scatter grant dream hollow arrive';
+
 
 module.exports = {
   networks: {
@@ -18,6 +21,12 @@ module.exports = {
       host: "127.0.0.1",
       port: 8545,
       network_id: "*" // Match any network id
+    },
+    rinkeby: {
+      provider: function() {
+        return new HDWalletProvider(mnemonic,'https://rinkeby.infura.io/v3/023ec2b3a073411a9f11ee0a431d58d3');
+      },
+      network_id: 1
     }
   }
 };

### 2018-12-19 article/shortpaper/main.tex
Short paper update

@@
 \section{Introduction}
-Bitcoin \cite{nakamoto2008bitcoin} and other cryptocurrencies are pseudonymous.
-Users' public keys are used as pseudonyms in these systems.
-Transactions essentially record a flow of cryptocurrency from one (or more) public keys to another public key (or more).
-Flow of cryptocurrency can be easily tracked due to the open and transparent nature of cryptocurrencies' transaction ledger.
-Moreover, coherent public keys, which are used by the same user, can be clustered merely by analyzing the ledger.
-Recently several tools and algorithms were proposed to diminish users' privacy (\cite{meiklejohn2013fistful},\cite{moser2013inquiry}, \cite{moreno2016listening}).
-Such deanomyzation attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.
-
-One of the methods to increase users' privacy is coin mixing or tumbling.
+One of the methods to increase cryptocurrency users' privacy is coin mixing or tumbling.
 This technique provides \textit{k-anonymity} or \textit{plausible deniability}.
@@
 On the other hand decentralized tumblers achieve availability, theft prevention and satisfy strong notions of anonymity although they are considerably heavier computationally.
-In the following we will solely focus on the problem of coin mixing on Ethereum \cite{wood2014ethereum}.
 
@@
 Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.
-As the Ethereum network is congested, ie.
-blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
 
 \textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains.
-This protocol can be used to shuffle cyphertexts, ballots or public keys.
-The protocol have many use cases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
-
 To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
@@
 
- Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers.
-
 The language $\mathcal{L}_{DDH}$ is defined to be the set of all tuples $(G,aG,bG,abG)$ where $G\in \mathbb{G}$ is of order prime $q$.
@@
 
-\subsection{State channels} 
-Public blockchain's decentralization comes at an inherent cost in regard to scalability, since currently each full node verifies the full state of the public ledger.
-Often times Bitcoin's ($\smallsim7$ transactions per second (tps)) or Ethereum's ($\smallsim15$ tps) throughput is compared to that of Visa's ($\smallsim\num[group-separator={,}]{45000}$ tps).
-Blockchains' scalability issues became an increasingly growing problem as more and more users adopted the technology.
-One remarkable example was the launch of the Cryptokitties game in 2017, when the Ethereum network was congested for a few hours due to the enormous popularity of the game.
-Therefore several solutions were proposed to alleviate aforementioned scalability issues.
-
-One of the major class of these techniques is called off-chain solutions.
-The insight of these proposals is that it is not needed to conduct all transactions on the blockchain, since participants could lock funds on-chain and afterwards securely issue transactions off-chain, for instance micropayments, with high degree of security and finality.
-Participants only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
-The first implementation of this idea was a payment channel network for Bitcoin called Lightning network \cite{poon2016bitcoin}.
-The advantage of the Lightning network is that participants can issue several payments without sending transactions to the blockchain and paying the sometimes costly transaction fees.
-Furthermore users are guaranteed to have instant finality instead of waiting several blocks to confirm their payments.
-
-State channels are the more general form of payment channels, they can be used not only for payments, but for any arbitrary state updates on a blockchain, like changes inside a smart contract.
-State channels were first described in detail by Jeff Coleman et al.\cite{coleman2018counterfactual}.
-Since then several other frameworks for generalised state channels were elaborated (\cite{dziembowski2017perun},\cite{mccorryyou}).
-Recently a case study of the Battleship game was published by Patrick McCorry, Chris Buckland et al.
-to evaluate how state channels could contribute in scaling blockchain-based applications \cite{mccorryyou}.
-
-Later in this paper, in Section \ref{statechannelimpl} we argue that MixEth can be made more scalable by implementing shuffling in a state channel.
-
 \section{Security goals} \label{securitygoals}
@@
 \end{itemize}
-
 \section{MixEth}
@@
 \end{algorithm}
-Note that every recipient should perform this check after each shuffling.
-Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
-This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
 
-\begin{wrapfigure}{r}{0.5\textwidth}
+\begin{wrapfigure}{r}{0.35\textwidth}
 	\centering
-	\includegraphics[scale=0.5]{./withdrawalComplexity.jpg}
+	\includegraphics[scale=0.35]{./withdrawalComplexity.jpg}
 	\captionsetup{justification=centering}
@@
 
-\section{Acknowledgements}
-Chris Buckland is supported by an Ethereum Foundation
-scaling grant and an Ethereum Community Fund grant.
-We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
-
 \bibliographystyle{plain}

### 2018-12-20 article/shortpaper/main.tex
Short paper update

@@
 \end{abstract}
-\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer, State Channel}
+\keywords{Cryptography, Verifiable shuffle, Ethereum, Privacy, Coin mixer, State Channel}
 
@@
 We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
-Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back to on-chain.
+Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back on-chain.
 
@@
 \subsection{Notations}
-In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
 Let $[]$ denote the empty tuple.
@@
 More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin.
-If a user wants to create an Ethereum address, first they needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite prime field $\mathbb{F}_{p}$.
+If a user wants to create an Ethereum address, first they need to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite prime field $\mathbb{F}_{p}$.
 The corresponding public key will be $sG$.
-Note that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime.
+Note, that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime.
 Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.
@@
 Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
-Therefore the usial $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages get an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
 Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.
@@
 Otherwise, no meaningful notion of security can be achieved.
-Furthermore we presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
-Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
+Furthermore we presume that recipients are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
+Finally we assume that honest participants will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
 
@@
 If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should multiply all the public keys with a secret exponent $c$ and then permute all the transformed public keys.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
 Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
-
-Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
 
@@
 \end{algorithm}
+
+Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+
 \subsection{Challenging period}
@@
 
-\begin{wrapfigure}{r}{0.3\textwidth}
-	\centering
-\begin{tikzpicture}[shorten >=1pt,node distance=3cm,on grid,auto] 
-\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
-\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
-\node[state] (q_challenge) [below=of q_shuffle ] {$q_{challenge}$};
-\node[state, accepting below, below=of q_challenge] (q_withdraw) {$q_{withdraw_{k}}$};
-\path[->]
-(q_deposit) edge [loop right] node {$i+1$} ()
-(q_deposit) edge node {$i=N$} (q_shuffle)		
-(q_shuffle) edge node {} (q_challenge)
-(q_challenge) edge [bend right, swap] node {$noFraud, j+1$} (q_shuffle)
-(q_challenge) edge [bend left] node {$fraud, j-1$} (q_shuffle)
-(q_challenge) edge node {$j=N^{'}$} (q_withdraw)
-(q_withdraw) edge [loop right] node {$k+1$} ();
-\end{tikzpicture}
-\captionsetup{justification=centering}
-\caption{Shuffle-and-challenge paradigm implemented for the fully on-chain version of MixEth}
-\label{fig:shuffleandchallenge}
-\end{wrapfigure}
-
 Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
@@
 Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.
-
-\begin{wrapfigure}{r}{0.4\textwidth}
-	\centering
-	\begin{tikzpicture}[shorten >=1pt,node distance=4cm,on grid,auto] 
-	\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
-	\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
-	\node[state, below=of q_shuffle] (q_no_fraud) {$q_{noFraud_j}$};	\node[state, accepting, right=of q_no_fraud] (q_fraud) {$q_{fraud}$};
-	\node[state, accepting below, below=of q_no_fraud] (q_withdraw) {$q_{withdraw_{k}}$};
-	\path[->]
-	(q_deposit) edge [loop left] node {$i+1$} ()
-	(q_deposit) edge node {$i=N$} (q_shuffle)		
-	(q_shuffle) edge [loop left] node {$j+1$} ()
-	(q_shuffle) edge node {$j=N$} (q_no_fraud)
-	(q_no_fraud) edge node {$j=N$} (q_withdraw)
-	(q_no_fraud) edge [loop left] node {$j+1$} ()
-	(q_no_fraud) edge node {} (q_fraud)
-	(q_withdraw) edge [loop left] node {$k+1$} ();
-	\end{tikzpicture}
-	\captionsetup{justification=centering}
-	\caption{Shuffle-then-challenge paradigm implemented for the channelised version of MixEth}
-	\label{fig:shufflethenchallenge}
-\end{wrapfigure}
 

### 2018-12-20 truffle.js

@@ -1,17 +1,4 @@
-/*
- * NB: since truffle-hdwallet-provider 0.0.5 you must wrap HDWallet providers in a
- * function when declaring them. Failure to do so will cause commands to hang. ex:
- * ```
- * mainnet: {
- *     provider: function() {
- *       return new HDWalletProvider(mnemonic, 'https://mainnet.infura.io/<infura-key>')
- *     },
- *     network_id: '1',
- *     gas: 4500000,
- *     gasPrice: 10000000000,
- *   },
- */
- let HDWalletProvider = require('truffle-hdwallet-provider');
+let HDWalletProvider = require('truffle-hdwallet-provider');
 let mnemonic = 'dream pilot judge begin office silent improve scatter grant dream hollow arrive';
 
 

### 2018-12-20 article/shortpaper/main.tex
Fixing short paper

@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
-	\begin{algorithmic}[1]
+	\begin{algorithmic}[H]
 		\State $PK_{i} \gets []
@@
 	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
 	\begin{algorithmic}[1]
-		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b\leftarrow verifyChaumPedersen(proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
 		\State $b^*\leftarrow0$
@@
 Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
-Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}.
+Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract.
 Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.
@@
 As soon as the anonymity set is large enough a receiver could withdraw their assets.
-The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}.
 A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
@@
 Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
-The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}.
-Note that all three $N$s are the same.
-In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.
 
@@
 \end{table} 
-
+\newpage
 \bibliographystyle{plain}

### 2018-12-20 article/shortpaper/main.tex
Added ae package to for clearer fonts
Small edits to the short paper

@@
 \usepackage{booktabs}
+\usepackage{ae,aecompl}
 %% Sets page size and margins
@@
 In this paper, we present MixEth, which is a trustless coin mixing service.
-MixEth is more efficient than any proposed trustless coin tumbler.
-It requires only $3$ on-chain transactions at most per user and $1$ off-chain message.
+MixEth is more efficient than any current proposed trustless coin tumbler.
+It requires at most only $3$ on-chain transactions per user and $1$ off-chain message.
 It achieves strong notions of anonymity and is able to resist denial-of-service attacks.
-Furthermore the underlying protocol can also be used to efficiently shuffle ballots, cyphertexts in a trustless and decentralized manner.
+Furthermore the underlying protocol can also be used to efficiently shuffle ballots and cyphertexts in a trustless and decentralized manner.
 \end{abstract}
@@
 The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys.
-This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.
+This powerful technique gives users superior privacy and anonymity since their newly received coins can not be linked to them.
 
@@
 The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
-Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases.
+Both of them require usage of a large amount of gas to withdraw funds, which could be prohibitive for many use cases.
 Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.
@@
 \textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains.
-To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
+To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum.
+MixEth overcomes the above mentioned efficiency issues of an Ethereum-based coin-mixer while retaining the strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
@@
 We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
-Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back on-chain.
 
@@
 Let $[]$ denote the empty tuple.
-For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$.
+For a tuple $t=(x_1,\dots,x_n)$ we denote $t[x_i]$ as the value stored at $x_{i}$.
 The cardinality of a finite set $X$ is denoted as $|X|$.
@@
 Roughly speaking DDH states that no efficient algorithm can distinguish between the two distributions $(aG, bG, abG)$ and $(aG, bG, cG)$, where $a,b,c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|}$.
-It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve, which is used to generate accounts and sign transactions in Bitcoin and Ethereum among other cryptocurrencies.
+It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve used in Ethereum.
 
@@
 \end{enumerate} 
-Note that in the following a non-interactive version of this protocol will only be considered that can be achieved by applying the Fiat-Shamir heuristic.
+Note that in the following a non-interactive version of this protocol will only be considered. This can be achieved by applying the Fiat-Shamir heuristic.
 
@@
 ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}.
-Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.
+Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assist usability.
 
-However, in MixEth, we deploy a somewhat loosened version of ECDSA, where we allow arbitrary generator elements to be used.
-Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
-Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages get an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+However, in MixEth, we require the use of arbitrary generator elements.
+Such an extension is needed for withdrawing funds from the mixer as the shuffled public keys remain public keys with respect to non-standardized generator elements.
+Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages require an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
 Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.
@@
 
-A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
+A MixEth contract is deployed on the Ethereum blockchain at $id_{contract}$ address and is initialized with the $amt$ parameter which denotes the denomination of ether to be mixed.
 Every sender must deposit exactly $amt$ ether to a specific public key.
@@
 \subsection{Shuffling period}
-After the depositing round, shuffling and challenging rounds are coming after in turns.
-Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
+After the depositing round the shuffling and challenging rounds alternate in turn.
+Each shuffling round is followed by a challenging round where the correctness of the preceding shuffle can be challenged by anyone.
 If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
-Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
+In the course of a shuffle an honest shuffler multiplies all the public keys with a secret multiplier $c$ and then permutes the transformed public keys.
+This shuffling is done off-chain, then the shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
+This allows anyone to verify the shuffle and, if required, submit a challenge during the succeeding challenge round.
 
@@
 \end{algorithm}
-
-Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
 
@@
 To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
-Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
+Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last-but-one list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
 Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract.
@@
 In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass.
-In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
+In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat of lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
 To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.
@@
 Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.
+
 If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur.
@@
 A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.
+
 Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
@@
 \begin{table}[H] 
-	\caption{Proof-of-concept implementation gas cost results.
-Expect further improvements.
-MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\caption{Proof-of-concept implementation gas cost results. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
 	\centering 

### 2018-12-20 article/shortpaper/main.tex
Added gas costs for deploy and deposit

@@
 		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&TBD&TBD&0&0&TBD\\
+		MixEthChannel&672276&21000&0&0&TBD\\
 		\bottomrule

### 2018-12-21 article/shortpaper/main.tex
Short paper ready

--- 2018-12-20 article/shortpaper/main.tex
@@
 
-We implemented MixEth in Solidity with two different approaches.
+We implemented MixEth in Solidity with two different approaches \footnote{https://github.com/seresistvanandras/MixEth}.
 The first one does not apply state channels, all the transactions are made on-chain.
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&TBD&TBD&0&0&TBD\\
+		MixEth&5395945&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&672276&21000&0&0&TBD\\
 		\bottomrule

### 2018-12-26 shuffle/shuffle_generation.js
Shuffle generation with pre-defined pubKeys

@@ -4,8 +4,31 @@ var EC = require('elliptic').ec;
 var ec = new EC('secp256k1');
 let G = '0479BE667EF9DCBBAC55A06295CE870B07029BFCDB2DCE28D959F2815B16F81798483ADA7726A3C4655DA4FBFC0E1108A8FD17B448A68554199C47D08FFB10D4B8'; //Generator point
 
+function shuffleGenerator(pubKeys, prevCumulatedConstant) {
+  let pubKeyArray = pubKeys.split(',');
 
-function shuffleGenerator(prevCumulatedConstant) {
+  let shufflingConstant = randomBytes(32);
+  console.log("Shuffling constant: ", shufflingConstant.toString('hex'));
+  let shuffledPubKeys = [];
+
+  let prevCumulatedC=ec.keyFromPublic(prevCumulatedConstant,'hex').getPublic();
+  currentCumulatedC=prevCumulatedC.mul(shufflingConstant);
+  let cG  = ec.keyFromPublic(G,'hex').getPublic().mul(shufflingConstant);
+  console.log("cG",cG);
+
+  for(var i=0; i < pubKeyArray.length; i++) {
+    console.log("figyuka",pubKeyArray[i].toString('hex'));
+    let pub = ec.keyFromPublic('04'+pubKeyArray[i].toString('hex'),'hex').getPublic();
+    console.log("pub",pub);
+    shuffledPubKeys.push(pub.mul(shufflingConstant));
+  }
+  shuffledArray = shuffle(shuffledPubKeys);
+
+  return {"shuffledPubkeys": shuffledArray,"cG":cG,"currentCumulatedConstant":currentCumulatedC};
+}
+
+
+function shuffleGeneratorWithRandKeys(prevCumulatedConstant) {
 
   let shufflingConstant = randomBytes(32);
   console.log("Shuffling constant: ", shufflingConstant.toString('hex'));
@@ -16,7 +39,7 @@ function shuffleGenerator(prevCumulatedConstant) {
   let cG  = ec.keyFromPublic(G,'hex').getPublic().mul(shufflingConstant);
 
   let pubKeys=generatePubKeys(6);
-  for(var i=0; i<pubKeys.length; i++) {
+  for(var i=0; i < pubKeys.length; i++) {
     let pub = pubKeys[i].getPublic();
     console.log(i+": "+JSON.stringify(pub.mul(shufflingConstant)));
[…]

### 2018-12-29 article/main.tex
Fixed PDF rendering artifacts

@@
 Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
-Therefore the usial $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
 Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.

### 2018-12-29 article/main.tex
Closes #1

@@
 It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers.
-The output of the shuffle is another $k$ modular integers raised to the same secret exponent only known to the shuffler.
-The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly.
+The output of the shuffle is another $k$ modular integers multiplied by the same secret multiplier only known to the shuffler.
+The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly without disclosing the secret multiplier.
 

### 2019-01-09 article/main.tex
FC19 Reviews added

@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&TBD&TBD&0&0&TBD\\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&TBD\\
 		\bottomrule

### 2019-02-08 article/IEEE/MixEthIEEESP.tex
Started IEEE version of paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{MixEth: efficient, trustless coin mixing service for Ethereum}

\author{\IEEEauthorblockN{István András Seres\IEEEauthorrefmark{1},
		Dániel A. Nagy\IEEEauthorrefmark{2}, Péter Burcsi\IEEEauthorrefmark{3}}
	\IEEEauthorblockA{Department of Computer Algebra,
		Eötvös Loránd University\\
		Budapest, Hungary\\
		Email: \IEEEauthorrefmark{1}istvanseres@caesar.elte.hu,
		\IEEEauthorrefmark{2}daniel@ethereum.org,
		\IEEEauthorrefmark{3}bupe@inf.elte.hu}
\and
\IEEEauthorblockN{Chris Buckland}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
	\textit{King's College London}\\
	London, United Kingdom \\
	cpbuckland88@gmail.com }
}

\maketitle

\begin{abstract}
Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to the ledger's transparent nature, privacy is notably reduced. If the link between users' public key and their physical identity is exposed, their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only 3 on-chain transactions at most per user and 1 off-chain message. It achieves strong notions of anonymity and is able to resist denial-of-service attacks. Furthermore the underlying protocol can also be used to efficiently shuffle ballots, cyphertexts in a trustless and decentralized manner.
\end{abstract}

\begin{IEEEkeywords}
Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer, State Channel
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-02-09 article/IEEE/MixEthIEEESP.tex
Started Formatting IEEE version

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
+\usepackage[noadjust]{cite}
 \usepackage[english]{babel}
@@
 \usepackage[T1]{fontenc}
+\usepackage{booktabs}
+\usepackage{ae,aecompl}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
+\usepackage[numbers]{natbib}
 \usepackage{xcolor}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+%% Useful packages
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.12}
+\usepackage[group-separator={,}]{siunitx}
+\usepackage{amsmath}
+\usepackage{wrapfig}
+\usepackage{amsthm}
+\usetikzlibrary{arrows,automata}
+\usepackage{algpseudocode}
+\usepackage{graphicx}
+\usepackage{algorithm}
+\usepackage{breqn}
+\usepackage{algpseudocode}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+\usepackage{eufrak}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{listings}
+\usepackage[toc,page]{appendix}
+\usepackage{color}
+\definecolor{lightgray}{rgb}{.9,.9,.9}
+\definecolor{darkgray}{rgb}{.4,.4,.4}
+\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
+\floatname{algorithm}{Procedure}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
+\lstdefinelanguage{JavaScript}{
+	keywords={typeof, contract, struct, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+	keywordstyle=\color{blue}\bfseries,
+	ndkeywords={class, export, boolean, throw, implements, import, this},
+	ndkeywordstyle=\color{darkgray}\bfseries,
+	identifierstyle=\color{black},
+	sensitive=false,
+	comment=[l]{//},
+	morecomment=[s]{/*}{*/},
+	commentstyle=\color{purple}\ttfamily,
+	stringstyle=\color{red}\ttfamily,
+	morestring=[b]',
+	morestring=[b]"
+}
+
+\lstset{
+	language=JavaScript,
+	backgroundcolor=\color{lightgray},
+	extendedchars=true,
+	basicstyle=\footnotesize\ttfamily,
+	showstringspaces=false,
+	showspaces=false,
+	numbers=left,
+	numberstyle=\footnotesize,
+	numbersep=9pt,
+	tabsize=2,
+	breaklines=true,
+	showtabs=false,
+	captionpos=b
+}
+
+\usepackage{graphicx}
+\usepackage[
+n,
+operators,
+advantage,
+sets,
+adversary,
+landau,
+probability,
+notions,	
+logic,
+ff,
+mm,
+primitives,
+events,
+complexity,
+asymptotics,
+keys]{cryptocode}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+
+\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
+
+\def\bitcoinA{%
+	\leavevmode
+	\vtop{\offinterlineskip %\bfseries
+		\setbox0=\hbox{B}%
+		\setbox2=\hbox to\wd0{\hfil\hskip-.03em
+			\vrule height .3ex width .15ex\hskip .08em
+			\vrule height .3ex width .15ex\hfil}
+		\vbox{\copy2\box0}\box2}}
+
+\DeclareMathOperator{\EX}{\mathbb{E}}% expected value
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
+
+\renewcommand{\lstlistingname}{Figure}% Listing -> Algorithm
+\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms
+
+\newcommand{\smallsim}{\smallsym{\mathrel}{\sim}}
+
+\makeatletter
+\newcommand{\smallsym}[2]{#1{\mathpalette\make@small@sym{#2}}}
+\newcommand{\make@small@sym}[2]{%
+	\vcenter{\hbox{$\m@th\downgrade@style#1#2$}}%
+}
+\newcommand{\downgrade@style}[1]{%
+	\ifx#1\displaystyle\scriptstyle\else
+	\ifx#1\textstyle\scriptstyle\else
+	\scriptscriptstyle
+	\fi\fi
+}
+\makeatother
+
 \begin{document}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Bitcoin ~\cite{nakamoto2008bitcoin} and other cryptocurrencies are pseudonymous.
+Users' public keys are used as pseudonyms in these systems.
+Transactions essentially record a flow of cryptocurrency from one (or more) public keys to another public key (or more).
+Flow of cryptocurrency can be easily tracked due to the open and transparent nature of cryptocurrencies' transaction ledger.
+Moreover, coherent public keys, which are used by the same user, can be clustered merely by analyzing the ledger.
+Recently several tools and algorithms were proposed to diminish users' privacy (\cite{meiklejohn2013fistful},\cite{moser2013inquiry},\cite{moreno2016listening}).
+Such deanomyzation attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.
 
-\section{Ease of Use}
+One of the methods to increase users' privacy is coin mixing or tumbling.
+This technique provides \textit{k-anonymity} or \textit{plausible deniability}.
+The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys.
+This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.
 
-\subsection{Maintaining the Integrity of the Specifications}
+Several coin mixing protocols were proposed in the literature both centralized (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}, \cite{heilman2017tumblebit}) and decentralized (\cite{maxwell2013coinjoin}, \cite{ruffing2014coinshuffle}, \cite{miximus2018}, \cite{meiklejohn2018mobius}, \cite{bissias2014sybil}).
+A major drawback of centralized coin mixing is that the availability of the tumbler is entirely dependent on the trusted party and in most cases theft prevention can not be guaranteed (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}).
+On the other hand decentralized tumblers achieve availability, theft prevention and satisfy strong notions of anonymity although they are considerably heavier computationally.
+In the following we will solely focus on the problem of coin mixing on Ethereum \cite{wood2014ethereum}.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+There is no doubt that there exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
+This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
+Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases.
+Möbius requires $335714n$ gas ($n$ is the ring size) while Miximus consumes $1903305$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.
+As the Ethereum network is congested, ie.
+blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains.
+This protocol can be used to shuffle cyphertexts, ballots or public keys.
+The protocol have many use cases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
+MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
+Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back to on-chain.
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+\section{Background}
+In this section we introduce the building bocks required to create our mixing protocol and MixEth, the trustless coin tumbler.
+\subsection{Notations}
+In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
+Let $[]$ denote the empty tuple.
+For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$.
+The cardinality of a finite set $X$ is denoted as $|X|$.
+In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$.
+If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$.
+The symmetric group of degree $n$ is written as ${S}_n$.
+In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation.
+Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript.
+Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.
 
-\subsection{\LaTeX-Specific Advice}
+We use games in definitions and proofs of security.
+At the end of each game, the main procedure of game \textsf{G} outputs a single bit.
+$\Pr(\textsf{G})$ denotes the probability that the output is $1$.
+\subsection{Cryptographic keys in Ethereum}
+Ethereum uses Elliptic Curve Cryptography (ECC) to secure users' funds.
+More specifically, it uses the secp256k1 curve, the same one as used in Bitcoin.
+If a user wants to create an Ethereum address, first they needs to generate a secret key  $s\stackrel{\$}{\leftarrow}\mathbb{Z}_n$, where $n$ is the order of secp256k1 over a finite prime field $\mathbb{F}_{p}$.
+The corresponding public key will be $sG$.
+Note that any multiples of $G$ is also a generator of curve points since $n$, the order of the group is also a prime.
+Accounts in Ethereum are identified by their addresses which can be obtained by taking the right most 20 bytes of the Keccak hashed public key \cite{wood2014ethereum}.
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+\subsection{Verifiable shuffle}
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
+Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}.
+It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers.
+The output of the shuffle is another $k$ modular integers multiplied by the same secret multiplier only known to the shuffler.
+The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly without disclosing the secret multiplier.
 
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
+Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decision Diffie-Hellman (DDH) problem.
+Therefore, Neff's verifiable shuffle can also be applied in groups over elliptic curves.
 
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
+Verifiable shuffle can be used to shuffle a set of public keys, $PK=(s_{1}G,s_{2}G\dots,s_{k}G)$. Note that secret keys are not known to the shuffler.
 
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
+\begin{enumerate}
+	\item Shuffler commits to $C=cG$, 
+		$$PK^*=(c(s_{\pi^{-1}(1)}G),c(s_{\pi^{-1}(2)}G),\dots,c({s_{\pi^{-1}(k)}}G))$$
 
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
+	  where $\pi$ is a random permutation.
+Shuffler additionally computes and publishes a zero-knowledge proof about the correctness of the shuffle.
+This proof can be made non-interactive via the Fiat-Shamir heuristic.
+Let us call $C$ as the shuffling constant.
+	\item Assuming the proof verifies users gain new public keys with respect to another generator element, namely $cG$.
+\end{enumerate}
 
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+For verifying the proof one needs to compute $8k+5$ exponentiations, however later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.
 
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
+So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.
+The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.
 
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
+\subsection{Decision Diffie-Hellman Problem and Chaum-Pedersen Protocol}
 
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
+The Decision Diffie-Hellman assumption (DDH) is a standard cryptographic hardness assumption which underlies the security of many cryptographic protocols.
+Roughly speaking DDH states that no efficient algorithm can distinguish between the two distributions $(aG, bG, abG)$ and $(aG, bG, cG)$, where $a,b,c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|}$.
+It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve, which is used to generate accounts and sign transactions in Bitcoin and Ethereum among other cryptocurrencies.
 
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
+Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers.
 
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
+The language $\mathcal{L}_{DDH}$ is defined to be the set of all tuples $(G,aG,bG,abG)$ where $G\in \mathbb{G}$ is of order prime $q$.
+The Chaum-Pedersen protocol enables a prover $\mathcal{P}$ to prove to a verifier $\mathcal{V}$ that $(G,A,B,C)\in\mathcal{L}_{DDH}$ in zero-knowledge for groups of prime order \cite{chaum1992wallet}.
+The protocol is organized as follows:
 
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+\begin{enumerate}
+	\item $\mathcal{V}$: $s\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $commit(s)$ 
+	\item $\mathcal{P}$: $r\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $y_1=rG$, $y_2=rB$.
+	\item $\mathcal{V}$ opens commitment by sending $s$
+	\item $\mathcal{P}$ sends $z=r+as \Mod{q}$
+	\item $\mathcal{V}$ checks $zG=y_{1}+sA \Mod{q} \land zB=y_{2}+sC \Mod{q}$
+\end{enumerate} 
+Note that in the following a non-interactive version of this protocol will only be considered that can be achieved by applying the Fiat-Shamir heuristic.
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\subsection{ECDSA with arbitrary generator element}
+Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth.
+ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}.
+Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.
+
+However, in MixEth, we deploy a somewhat loosened version of ECDSA, where we allow arbitrary generator elements to be used.
+Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
+Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.
+
+In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e.
+no efficient adversary could forge a signature on any given message with non-negligible probability.
+
+\subsection{Ethereum}
+
+Ethereum is a cryptocurrency built on top of a blockchain.
+Similarly to Bitcoin, network participants broadcast transactions in a peer-to-peer network, where transactions are bundled together into blocks that are appended to a public ledger called blockchain.
+Only those specific nodes can append new blocks to the blockchain who previously solved a difficult cryptographic puzzle.
+The state of the system consists of the state of different accounts populating it.
+
+In Ethereum currently there are two types of accounts.
+The first account type is called \textit{externally owned account}.
+It owns an ECDSA keypair controlled by its user.
+Private keys are used to sign transactions.
+On the other hand there are \textit{contract accounts}, often smart contracts, that additionally have persistent storage and contract's code.
+Both of the account types have Ether balances, which is the native currency of the Ethereum network.
+Ether is denominated in wei, where $1\ ETH = 10^ {18}\ wei$.
+
+Transactions can alter the system's state by either creating a contract account or by calling to an existing account.
+Transactions to externally owned accounts can only transfere Ether, while transactions to contract accounts can additionally execute the code associated with them.
+Codes are executed in a quasi-Turing complete execution environment, called Ethereum Virtual Machine (EVM).
+
+EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}.
+In every transaction the sender needs to pay upfront for the execution of the contract's code.
+The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price.
+Therefore the transaction fee is the gas cost multiplied by the gas price.
+One needs to specify a gas limit, meaning that they do not allow their transaction to burn more gas than the limit.
+If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner.
+If there are gas left after successful execution, transaction originator is reimbursed.
+Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block.
+Currently the block gas limit is cca.
+$\num[group-separator={,}]{8000000}$ gas.
+Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees.
+Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.
+
+\subsubsection{State channels} 
+Public blockchain's decentralization comes at an inherent cost in regard to scalability, since currently each full node verifies the full state of the public ledger.
+Often times Bitcoin's ($\smallsim7$ transactions per second (tps)) or Ethereum's ($\smallsim15$ tps) throughput is compared to that of Visa's ($\smallsim\num[group-separator={,}]{45000}$ tps).
+Blockchains' scalability issues became an increasingly growing problem as more and more users adopted the technology.
+One remarkable example was the launch of the Cryptokitties game in 2017, when the Ethereum network was congested for a few hours due to the enormous popularity of the game.
+Therefore several solutions were proposed to alleviate aforementioned scalability issues.
+
+One of the major class of these techniques is called off-chain solutions.
+The insight of these proposals is that it is not needed to conduct all transactions on the blockchain, since participants could lock funds on-chain and afterwards securely issue transactions off-chain, for instance micropayments, with high degree of security and finality.
+Participants only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
+The first implementation of this idea was a payment channel network for Bitcoin called Lightning network \cite{poon2016bitcoin}.
+The advantage of the Lightning network is that participants can issue several payments without sending transactions to the blockchain and paying the sometimes costly transaction fees.
+Furthermore users are guaranteed to have instant finality instead of waiting several blocks to confirm their payments.
+
+State channels are the more general form of payment channels, they can be used not only for payments, but for any arbitrary state updates on a blockchain, like changes inside a smart contract.
+State channels were first described in detail by Jeff Coleman et al.\cite{coleman2018counterfactual}.
+Since then several other frameworks for generalised state channels were elaborated (\cite{dziembowski2017perun},\cite{mccorryyou}).
+Recently a case study of the Battleship game was published by Patrick McCorry, Chris Buckland et al.
+to evaluate how state channels could contribute in scaling blockchain-based applications \cite{mccorryyou}.
+
+Later in this paper, in Section \ref{statechannelimpl} we argue that MixEth can be made more scalable by implementing shuffling in a state channel.
+
+\subsubsection{Ethereum account abstraction}
+Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
+When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they can not do this from a fresh address, since it does not hold any ether.
+Since as of now only the sender of a transaction can pay for the gas fee, users can not withdraw their funds unless they ask someone to fund their fresh address.
+
+Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}.
+EIP86 permits receivers of a transaction paying the gas fee.
+This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses.
+Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
+This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA).
+Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
+
+\section{Threat model}
+\subsection{Participants and interactions}
+In a decentralized tumbler, we have $3$ distinct entities: the tumbling smart contract, a set of senders and a set of receivers.
+A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys.
+In all the following interactions and algorithms we assume that the public state of the tumbler is implicitly given as input.
+Interactions of these entities can be summarized as follows:
+
+$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.
+
+$0/1\leftarrow VerifyDeposit(tx)$: The tumbler contract checks the validity of senders' deposits.
+
+$ProcessDeposit(tx)$: upon receiving a valid deposit transaction, the mixing contract updates its internal state accordingly.
+
+Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
+Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve.
+Anyone is allowed to shuffle the public keys at most once by paying some deposit to the tumbler contract:
+
+$PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
+Let us call $C^{*}_{i}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
+The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period.
+The permutation $\pi$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
+All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.
+
+$0\lor1\leftarrow 
+ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is DDH-tuples: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$.
+If the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
+This proof and checks allow one to be certain that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.
+
+$tx\stackrel{\$}{\leftarrow}WithdrawShufflingDeposit(sk_B)$: after a challenging period a shuffler can withdraw their shuffling deposit from the tumbler contract.
+
+$0\lor1\leftarrow VerifyWitdhrawShufflingDeposit(pk_B)$: if there was no successful challenges against the shuffler, i.e. their deposit is not slashed, they can withdraw their shuffling deposit.
+
+$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*}_{final})$: after the end of the shuffling period users are allowed to withdraw their funds.
+Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}_{final}$, the final shuffling accumulated constant.
+
+$0/1\leftarrow VerifyWithdraw(tx)$: tumbler checks the validity of a recipient's withdrawal transaction.
+
+$ProcessWithdraw(tx)$: upon receiving a valid withdrawal transaction, mixing contract updates its internal state accordingly.
+
+\subsection{Security goals} \label{securitygoals}
+We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
+These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
+
+We are going to assume that at most $n-2$ recipients are malicious ($n$ is the number of recipients).
+Otherwise, no meaningful notion of security can be achieved.
+Furthermore we presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
+Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
+
+In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles.
+CORR enables $\adv$ to corrupt a sender or receiver by learning the secret key of any party $l$ of their choice.
+Oracle access to AD or AW allow $\adv$ to deposit or withdraw respectively from tumbler session $j$.
+Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW.
+In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
+
+These oracles are formally defined as follows:
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cccc}    
+		\begin{minipage}{6cm}
+			\procedure{AD(tx,$j$)}{%
+				b \leftarrow VerifyDeposit(tumblers[j],tx) \\
+				if\ (b) \ ProcessDeposit(tumblers[j],tx) \\
+				\pcreturn b  }
+		\end{minipage}
+		&
+		\begin{minipage}{6cm}
+			\procedure{AW(tx,$j$)}{%
+				b \leftarrow VerifyWithdraw(tumblers[j],tx) \\
+				if\ (b) \  ProcessWithdraw(tumblers[j],tx) \\
+				\pcreturn b  }
+		\end{minipage}
+		&
+		\begin{minipage}{4cm}
+			\procedure{CORR($l$)}{%
+				C=C.push(pk_{B_{l}}) \\
+				\pcreturn sk_{B_l}}
+		\end{minipage}
 	\end{tabular}
-\label{tab1}
-\end{center}
 \end{table}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
+\begin{table}[H]
+	\centering
+	\begin{tabular}{cc}   
+		\begin{minipage}{5cm}
+			\procedure{HD($i$,$j$,$l$)}{%
+				tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}})\\
+				H_{d}=H_{d}.push(tx) \\
+				ProcessDeposit(tumblers[j],tx)\\
+				\pcreturn tx }
+		\end{minipage}
+		&
+		\begin{minipage}{5cm}
+			\procedure{HW($j$,$l$)}{%
+				if\ (pk_{B_{l}} \notin tumblers[j].keys_{B})\ return \ \bot \\
+				tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}}) \\
+				H_{w}=H_{w}.push(j,l,tx) \\
+				ProcessWithdraw(tumblers[j],tx)\\
+				\pcreturn tx }
+		\end{minipage}
+	\end{tabular}
+\end{table}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.
 
-\section*{Acknowledgment}
+\subsubsection{Anonymity} \label{sec:defanonymity}
+\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+\textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
 
-\section*{References}
+\begin{definition}
+	Define $\textbf{Adv}^{d-anon}_{mix,\adv}(\lambda) = 2\Pr[\textsf{G}^{d-anon}_{mix,\adv}(\lambda)]-1\ for\ d \in \{dep, with\}$, where these games are defined as follows:
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{cc}    
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{dep-anon}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_A\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
+					b \stackrel{\$}{\leftarrow} \bin \\
+					(state,j,pk, i_{0},i_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{A}) \\
+					tx \stackrel{\$}{\leftarrow} Deposit(tumblers[j], sk_{A_{{l}_{b}}}, pk) \\
+					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
+					\pcreturn b = b^{’} }
+			\end{minipage}
+			&
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
+					b \stackrel{\$}{\leftarrow} \bin \\
+					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
+					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
+					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
+					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
+					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
+					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
+					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
+					\pcreturn b = b^{’} }		
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+	Then the tumbler satisfies sender or recipient anonymity if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.
+\end{definition}
 
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
+\subsubsection{Availability}
+It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and one but all recipients are compromised.
 
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
+Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient can not withdraw their funds.
 
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+\begin{definition}
+	Define $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{avail}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
 
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{c}    
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{avail}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w} \leftarrow \emptyset\\
+					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
+					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l})) \\
+					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
+					\pcreturn (b=0)\land(pk_{l}\in tumblers[j].keys_{B})}
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+	Then the tumbler satisfies availability if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+\end{definition}
+
+\subsubsection{Theft prevention} \label{sec:theftprevention}
+We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:
+
+\begin{definition}
+	Define $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{theft}_{mix,\adv}(\lambda)]$, where the game is defined as follows:
+
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{c}    
+			\begin{minipage}{7cm}
+				\procedure{MAIN $\textsf{G}^{theft}_{mix,\adv}(\lambda)$}{%
+					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
+					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w}, \textsf{contract} \leftarrow \emptyset\\
+					(\textsf{tx},j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,AW,HW}(1^{\lambda},\textsf{PK}_{B}) \\
+					if(\textsf{tumblers}[j].\textsf{keys}_{B}\not\subset \textsf{PK}_{B}\setminus C)\ return \ 0 \\
+					\pcreturn \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{tx})}
+			\end{minipage}
+		\end{tabular}
+	\end{table}	
+	Then the tumbler satisfies theft prevention if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+\end{definition}
+
+\section{MixEth}
+
+\subsection{Overview}
+MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
+\subsection{Initializing the tumbler}
+
+A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
+
+\subsection{Depositing period}
+Every sender must deposit exactly $amt$ ether to a specific public key.
+Deposits with incorrect ether value or invalid public key are rejected.
+Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.
+
+\subsection{Shuffling period}
+After the depositing round, shuffling and challenging rounds are coming after in turns.
+Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
+If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret exponent $c$ and then permute all the transformed public keys.
+Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
+
+Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+
+\begin{algorithm}
+	\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
+	\begin{algorithmic}[1]
+		\State $PK_{i} \gets []$
+		\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
+		\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
+		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
+		\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
+		\For{$j=0;j<|PK_{i-1}|;j++$}
+		\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
+		\EndFor
+		\State $C^{*}_{i}=cC^{*}_{i-1}$
+
+		\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i})$ 
+	\end{algorithmic}   
+\end{algorithm}
+\subsection{Challenging period}
+Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round.
+These are the actions Bob as a receiver needs to perform to check the correctness of the shuffle at $i$th round if Bob has secret key $s_{B}$.
+In this case Bob should check whether $s_{B}C^{*}_{i} \in PK_{i}$ or not.
+If not, Bob should prove to MixEth that the $i$th round is indeed the first round, where the shuffled public key corresponding to $s_{B}$ is compromised.
+The Chaum-Pedersen proof in the challenge transaction ensures that the integrity of the shuffled public key in round $i-1$st is intact, while shuffled public key is compromised in the $i$th round.
+
+\begin{algorithm}
+	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\begin{algorithmic}[1]
+		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b^*\leftarrow0$
+		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
+		\State $b^*\gets 1$
+		\Else
+		\State $b^*\gets 0$
+		\EndIf
+		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
+	\end{algorithmic}   
+\end{algorithm}
+Note that every recipient should perform this check after each shuffling.
+Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
+This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
+
+\subsection{Withdrawing}
+Let $C^*_{final}$ be the final shuffling accumulated constant.
+For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*_{final}$.
+The recipient can prove to MixEth that she knows secret key $s_{B}$ by signing their public key using a modified ECDSA, which uses $C^*_{final}$ as the generator element instead of the standardized $G$.
+
+\section{Security}
+This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.
+
+\subsection{Recipient anonymity}
+The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$.
+This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds.
+Adversary can only distinguish between honest recipients public keys with negligible probability.
+See reduction proof in Appendix \ref*{appendanon}.
+\subsection{Availability}
+If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
+\subsection{Theft prevention} 
+If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient.
+This contradicts to the assumption that ECDSA is existentially unforgeable.
+Reduction proof is enclosed in Appendix \ref*{appendtheft}.
+\begin{table}[H] 
+	\caption{Security properties achieved by each coin mixing protocol.}
+	\centering 
+	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}
+
+		\toprule
+		\hline
+		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
+		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
+		\hline
+		\midrule
+		\textbf{Centralized} & & \\
+		\midrule
+		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
+		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
+		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
+		\midrule
+		\textbf{Decentralized}      &    &      \\
+		\midrule
+		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
+		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
+		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
+		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
+		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
+		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
+		\bottomrule
+	\end{tabular}
+	\label{table:securityproperties}
+\end{table}
+
+\section{Implementation}
+
+We implemented MixEth with two different approaches.
+The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
+This could lead to unwanted gas costs as the number of corrupted shuffles increases.
+One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible.
+Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
+Both of the implementations allow users to mix Ether or other ERC20-compatible, a popular Ethereum token standard, tokens.
+
+One of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
+A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
+Since the block gas limit is $\num[group-separator={,}]{8000266}$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
+This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
+
+All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts.
+MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions.
+Note that these implementations are only proof-of-concept implementations, expect further improvements.
+All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
+
+\subsection{Fully on-chain implementation} \label{fullyonchainimpl}
+
+Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
+There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender.
+The rest of the protocol happens entirely on-chain.
+
+On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas.
+To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
+Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
+Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}.
+Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.
+We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.
+
+A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets.
+One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time.
+As soon as the anonymity set is large enough a receiver could withdraw their assets.
+The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}.
+A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
+This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
+A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
+However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
+$\num[group-separator={,}]{800}$.
+
+Also note that the on-chain cost of a shuffle transaction could be amortized among participants.
+Specifically if there is a group of senders and/or receivers who trust each other they could collectively charge any of them to shuffle once.
+Since they trust their peer, all the rest of the group does not need to shuffle anymore.
+Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.
+
+\subsection{State channel implementation} \label{statechannelimpl}
+
+We have also adapted MixEth to operate within a state channel.
+We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}.
+This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic.
+Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront.
+In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$.
+To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state.
+The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round.
+In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass.
+In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
+To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.
+
+Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic.
+Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic.
+This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle.
+After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round.
+Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.
+If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur.
+In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain.
+A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.
+Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
+The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}.
+Note that all three $N$s are the same.
+In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.
+
+\begin{table}[H] 
+	\caption{Proof-of-concept implementation gas cost results.
+Expect further improvements.
+MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\centering 
+	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
+		\toprule
+		\hline
+		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
+		\cline{4-5}&&&Shuffle upload&Challenge\\
+		\hline
+		\midrule
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&TBD\\
+		\bottomrule
+	\end{tabular}
+	\label{table:gasproperties}
+\end{table}
+
+\section{Related work}
+Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
+Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability.
+These properties could be used to evaluate and compare existing and future proposals from a security perspective.
+Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
+However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
+No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
+If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
+Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
+When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
+Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.
+
+Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}.
+It uses zkSNARKs to conceal the mapping between depositors and recipients.
+A depositor creates a leaf in a Merkle-tree.
+A depositor needs to exchange the preimage of the leaf with the recipient.
+Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf.
+So called nullifiers enable recipients to withdraw funds once and only once.
+The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
+However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
+Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
+Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
+
+As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
+In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
+\begin{table}[H] 
+	\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
+Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
+	\centering 
+	\begin{tabular}{lcc}
+
+		\toprule
+		&\#Off-chain messages& \#Transactions \\
+		\midrule
+		\textbf{Centralized} & & \\
+		\midrule
+		Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
+		Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
+		TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
+		\midrule
+		\textbf{Decentralized}      &    &      \\
+		\midrule
+		Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
+		Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
+		XIM \cite{bissias2014sybil} & 0      & 7       \\
+		Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
+		Miximus \cite{miximus2018} & 1+MPC & 2 \\
+		MixEth & 1 & 3 \\
+		MixEthChannel  & $\mathcal{O}(n)$ &2 \\
+		\bottomrule
+	\end{tabular}
+	\label{table:communicationcomplexity}
+\end{table}
+
+\subsection{Additional related work}
+Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}.
+Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes.
+Later on Aztec notes can be traded in a join-split style confidential transaction, namely the value of the traded Aztec notes are encrypted and not visible to outsiders.
+A join-split style transaction can have multiple inputs and outputs.
+Aztec applies zero-knowledge proofs and range proofs in order to achieve that the sum of inputs traded in a confidential transaction is greater or equal than the sum of outputs.
+The gas cost of a confidential Aztec transaction is $\num[group-separator={,}]{219000}$+$\num[group-separator={,}]{121000}n$+$\num[group-separator={,}]{41000}m$, where $n$ and $m$ are the numbers of inputs and outputs respectively.
+Although Aztec is not a coin mixer, it can be used not only to provide confidential transaction, but also to increase anonymity.
+On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes.
+Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions.
+For instance on top Aztec one could use MixEth to shuffle Aztec notes.
+
+\section{Extensions and improvements}
+MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround.
+A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant.
+MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.
+
+In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
+This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
+
+\section{Conclusion and Future Work} \label{conclusion}
+We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
+An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
+
+\section{Acknowledgements}
+Chris Buckland is supported by an Ethereum Foundation
+scaling grant and an Ethereum Community Fund grant.
+We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+
+\bibliographystyle{IEEEtran}
+\bibliography{sample}
+
+\begin{appendices}
+
+	\section{Proof of Anonymity} \label{appendanon}
+	Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
+
+	Towards contradiction let us assume that the recipient anonymity does not hold.
+Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(sG,cG,c_{0}G)$.
+Adversary $\bdv$ generates uniformly random public key $c_{1}G$ and invokes $\adv$ with the set $\textsf{PK}_{B}=(c_{0}C^{*}, c_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
+Then a withdrawal transaction occurs from $c_{b}G$.
+After polynomial-time $\adv$ outputs $b^{'}$ and $\bdv$ will output $\lnot b^{'}$.
+If $\adv$ outputs $0$ and $b=b^{'}$, this signals to $\bdv$ that $c_{0}G$ might potentially be of the form $scG=c_{0}G$  i.e.
+it is a DDH tuple, therefore $\bdv$ outputs $1$.
+In all the other cases $\bdv$ outputs a random bit.
+Therefore we have that $\bdv$ has an adventage in their DDH-game if and only if $\adv$ wins their $\textsf{G}^{with, anon}_{mix, \adv}$ security game.
+Since we assumed that recipient anonymity does not hold we have that $$\Pr[\textsf{DDH}_{\bdv}]=\frac{1}{2}+\frac{1}{2}*\Pr[\textsf{G}^{with, anon}_{mix, \adv}]=\frac{1}{2}+\frac{1}{2}*\textsf{non-negl}(\lambda),$$ which contradicts to the DDH assumption.
+
+	\section{Proof of Availability}  \label{appendavail}
+
+	The only possibility for an adversary to threaten the availability of funds for an honest receiver if they create an incorrect shuffle, where honest receiver's shuffled public key is compromised.
+Since the Chaum-Pedersen zero-knowledge protocol is complete, an honest receiver is alway able to create a Chaum-Pedersen proof, which demonstrates to the contract that their shuffled public key is compromised.
+Therefore we have for any PPT $\adv$ and $\forall \lambda \in \mathbb{N}$ that, $$\Pr[\textsf{G}^{avail}_{mix, \adv}]=0<negl(\lambda).$$
+
+	\section{Proof of Theft Prevention} \label{appendtheft}
+
+	Towards contradiction we assume that there exists an adversary $\adv$, who is able to break the theft prevention property introduced in Section \ref{sec:theftprevention} with non-negligible probability.
+Using such an adversary as a subroutine we could create another efficient adversary $\bdv$ who is able to break the existential unforgeability of ECDSA.
+The input of the forgeability game is the security parameter which is forwarded to $\adv$ along with $n$ randomly generated public keys.
+By assumption $\adv$ outputs with non-negligible probability valid withdraw transaction belonging to one of the public keys in the mixer.
+$\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
+$\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
+	$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$.
+This contradicts to the assumption that ECDSA is existentially unforgeable.
+
+\end{appendices}
 

### 2019-02-10 article/IEEE/MixEthIEEESP.tex
IEEE along the way

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[conference, compsoc]{IEEEtran}
 \IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage[noadjust]{cite}
+%\usepackage[noadjust]{cite}
 \usepackage[english]{babel}
@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
 \usepackage{graphicx}
@@
 \usepackage{listings}
-\usepackage[toc,page]{appendix}
 \usepackage{color}
@@
 \and
-\IEEEauthorblockN{Chris Buckland}
+\IEEEauthorblockN{Chris Buckland \thanks{Chris Buckland is supported by an Ethereum Foundation
+		scaling grant and an Ethereum Community Fund grant.}}
 \IEEEauthorblockA{\textit{Department of Computer Science} \\
@@
 \section{Introduction}
-Bitcoin ~\cite{nakamoto2008bitcoin} and other cryptocurrencies are pseudonymous.
-Users' public keys are used as pseudonyms in these systems.
+Bitcoin~\cite{nakamoto2008bitcoin} and other cryptocurrencies are pseudonymous.
+Users' public keys are used as pseudonyms.
 Transactions essentially record a flow of cryptocurrency from one (or more) public keys to another public key (or more).
@@
 Recently several tools and algorithms were proposed to diminish users' privacy (\cite{meiklejohn2013fistful},\cite{moser2013inquiry},\cite{moreno2016listening}).
-Such deanomyzation attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.
+Deanonimization attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.
 
-One of the methods to increase users' privacy is coin mixing or tumbling.
+A prevalent method to increase users' privacy is coin mixing or tumbling.
 This technique provides \textit{k-anonymity} or \textit{plausible deniability}.
@@
 
-There is no doubt that there exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
+There exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
 This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.
@@
 Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases.
-Möbius requires $335714n$ gas ($n$ is the ring size) while Miximus consumes $1903305$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.
 As the Ethereum network is congested, ie.
 blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
-
-Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
 
@@
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
-
-We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
+We implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
 Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back to on-chain.
@@
 
-For verifying the proof one needs to compute $8k+5$ exponentiations, however later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.
+For verifying the proof one needs to compute $8k+5$ exponentiations; later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.
 
@@
 
-\subsection{Decision Diffie-Hellman Problem and Chaum-Pedersen Protocol}
+\subsection{Decision Diffie-Hellman Problem and 
+	Pedersen Protocol}
 
@@
 The language $\mathcal{L}_{DDH}$ is defined to be the set of all tuples $(G,aG,bG,abG)$ where $G\in \mathbb{G}$ is of order prime $q$.
-The Chaum-Pedersen protocol enables a prover $\mathcal{P}$ to prove to a verifier $\mathcal{V}$ that $(G,A,B,C)\in\mathcal{L}_{DDH}$ in zero-knowledge for groups of prime order \cite{chaum1992wallet}.
+The Chaum-Pedersen protocol (ChP) enables a prover $\mathcal{P}$ to prove to a verifier $\mathcal{V}$ that $(G,A,B,C)\in\mathcal{L}_{DDH}$ in zero-knowledge for groups of prime order \cite{chaum1992wallet}.
 The protocol is organized as follows:
@@
 Participants only need to get back on-chain if there is a dispute about what happened precisely off-chain or they would like to lock up funds and redeem them on-chain.
-The first implementation of this idea was a payment channel network for Bitcoin called Lightning network \cite{poon2016bitcoin}.
-The advantage of the Lightning network is that participants can issue several payments without sending transactions to the blockchain and paying the sometimes costly transaction fees.
+The first implementation of this idea was a payment channel network for Bitcoin called Lightning network (LN) \cite{poon2016bitcoin}.
+LN's advantage is that participants can issue several payments without sending transactions to the blockchain and paying the sometimes costly transaction fees.
 Furthermore users are guaranteed to have instant finality instead of waiting several blocks to confirm their payments.
@@
 to evaluate how state channels could contribute in scaling blockchain-based applications \cite{mccorryyou}.
-
-Later in this paper, in Section \ref{statechannelimpl} we argue that MixEth can be made more scalable by implementing shuffling in a state channel.
+In Section \ref{statechannelimpl}, we argue that MixEth can be made more scalable by implementing shuffling in a state channel.
 
@@
 
-Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}.
+Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested\footnote{https://github.com/ethereum/EIPs/blob/master/EIPS/eip-86.md} by Nick Johnson and Vitalik Buterin.
 EIP86 permits receivers of a transaction paying the gas fee.
@@
 Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
-This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA).
+This means that users are no longer required to sign transactions with ECDSA.
 Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
@@
 We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
-These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
+These notions were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
 
@@
 Otherwise, no meaningful notion of security can be achieved.
-Furthermore we presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
+Additionally we presume that participants are on-line during the entire course of mixing in order to be able to monitor and potentially challenge any incorrect shuffle.
 Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
 
-In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles.
+In the security definitions and games adversary $\adv$ might have access to the following oracles.
 CORR enables $\adv$ to corrupt a sender or receiver by learning the secret key of any party $l$ of their choice.
@@
 
-These oracles are formally defined as follows:
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{6cm}
-			\procedure{AD(tx,$j$)}{%
-				b \leftarrow VerifyDeposit(tumblers[j],tx) \\
-				if\ (b) \ ProcessDeposit(tumblers[j],tx) \\
-				\pcreturn b  }
-		\end{minipage}
-		&
-		\begin{minipage}{6cm}
-			\procedure{AW(tx,$j$)}{%
-				b \leftarrow VerifyWithdraw(tumblers[j],tx) \\
-				if\ (b) \  ProcessWithdraw(tumblers[j],tx) \\
-				\pcreturn b  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{CORR($l$)}{%
-				C=C.push(pk_{B_{l}}) \\
-				\pcreturn sk_{B_l}}
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cc}   
-		\begin{minipage}{5cm}
-			\procedure{HD($i$,$j$,$l$)}{%
-				tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}})\\
-				H_{d}=H_{d}.push(tx) \\
-				ProcessDeposit(tumblers[j],tx)\\
-				\pcreturn tx }
-		\end{minipage}
-		&
-		\begin{minipage}{5cm}
-			\procedure{HW($j$,$l$)}{%
-				if\ (pk_{B_{l}} \notin tumblers[j].keys_{B})\ return \ \bot \\
-				tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}}) \\
-				H_{w}=H_{w}.push(j,l,tx) \\
-				ProcessWithdraw(tumblers[j],tx)\\
-				\pcreturn tx }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.
-
 \subsubsection{Anonymity} \label{sec:defanonymity}
 \textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
-
 \textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
@@
 					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
-					\pcreturn b = b^{’} }
-			\end{minipage}
-			&
-			\begin{minipage}{7cm}
-				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
-					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
-					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
-					b \stackrel{\$}{\leftarrow} \bin \\
-					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
-					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
-					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
-					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
-					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
-					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
-					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
 					\pcreturn b = b^{’} }
@@
 
-\subsection{Overview}
-MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
 \subsection{Initializing the tumbler}
@@
 		\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
-		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
+		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract$
 		\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
@@
 	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
 	\begin{algorithmic}[1]
-		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b\leftarrow verifyChP(proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
 		\State $b^*\leftarrow0$
@@
 Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
-This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
+This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds.
+key.
 
@@
 \section{Security}
-This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.
-
-\subsection{Recipient anonymity}
-The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$.
-This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds.
-Adversary can only distinguish between honest recipients public keys with negligible probability.
-See reduction proof in Appendix \ref*{appendanon}.
-\subsection{Availability}
-If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
-\subsection{Theft prevention} 
-If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient.
-This contradicts to the assumption that ECDSA is existentially unforgeable.
-Reduction proof is enclosed in Appendix \ref*{appendtheft}.
-\begin{table}[H] 
+Notions of security introduced in Section \ref{securitygoals} are formally proven in the Appendices. 
+\begin{table*}
 	\caption{Security properties achieved by each coin mixing protocol.}
@@
 	\label{table:securityproperties}
-\end{table}
+\end{table*}
 
@@
 
-We implemented MixEth with two different approaches.
-The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
+We implemented MixEth with two different approaches\footnote{https://github.com/seresistvanandras/MixEth}.
+The first implementation of MixEth does not apply state channels, all transactions are made on-chain.
 This could lead to unwanted gas costs as the number of corrupted shuffles increases.
@@
 As soon as the anonymity set is large enough a receiver could withdraw their assets.
-The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}.
 A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
 This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
-A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
-However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
+Note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
 $\num[group-separator={,}]{800}$.
@@
 Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
-The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}.
-Note that all three $N$s are the same.
 In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.
 
-\begin{table}[H] 
-	\caption{Proof-of-concept implementation gas cost results.
-Expect further improvements.
-MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
+\begin{table}
+	\caption{Implementation gas cost results.
+MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods.
+A shuffling transaction for an anomity set of $n$ burns $\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$ gas, while challenging any shuffle consumes $\num[group-separator={,}]{227563}$ gas.}
 	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
+	\begin{tabular}{@{\extracolsep{6pt}}lcccc@{}} 	
 		\toprule
 		\hline
-		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
-		\cline{4-5}&&&Shuffle upload&Challenge\\
+		&Deployment&Deposit&Withdraw\\
 		\hline
 		\midrule
-		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
-		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&TBD\\
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$ &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&TBD\\
 		\bottomrule
@@
 If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
-Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
-When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
-Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.
 
@@
 However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
-Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+A severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
 If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
-Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
+Although, this issue could be amended via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
 
@@
 	\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
-Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
+Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving and verification keys generation.}
 	\centering 
@@
 
-\section{Extensions and improvements}
-MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround.
-A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant.
-MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.
-
-In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
-This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
-
-\section{Conclusion and Future Work} \label{conclusion}
-We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
-An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
-
 \section{Acknowledgements}
-Chris Buckland is supported by an Ethereum Foundation
-scaling grant and an Ethereum Community Fund grant.
 We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
@@
 
-\begin{appendices}
+\appendix
 
-	\section{Proof of Anonymity} \label{appendanon}
+\subsection{Proof of Anonymity} \label{appendanon}
 Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
@@
 
-	\section{Proof of Availability}  \label{appendavail}
-
+\subsection{Proof of Availability}  \label{appendavail}
 The only possibility for an adversary to threaten the availability of funds for an honest receiver if they create an incorrect shuffle, where honest receiver's shuffled public key is compromised.
@@
 
-	\section{Proof of Theft Prevention} \label{appendtheft}
-
+\subsection{Proof of Theft Prevention} \label{appendtheft}
 Towards contradiction we assume that there exists an adversary $\adv$, who is able to break the theft prevention property introduced in Section \ref{sec:theftprevention} with non-negligible probability.
@@
 $\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
-$\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
-	$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$.
+$\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game: $$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$.
 This contradicts to the assumption that ECDSA is existentially unforgeable.
 
-\end{appendices}
-
 \end{document}

### 2019-02-11 article/IEEE/MixEthIEEESP.tex
IEEE under 10 pages

@@
 There exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}.
-This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.
+This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \footnote{https://blog.cyber.fund/huge-ethereum-mixer-6cf98680ee6c}.
 
@@
 \subsection{Shuffling period}
-After the depositing round, shuffling and challenging rounds are coming after in turns.
-Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
-If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should multiply all the public keys with a secret exponent $c$ and then permute all the transformed public keys.
+After the depositing round, shuffling and potentially challenging rounds follow.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
 Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
@@
 \subsection{Challenging period}
-Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round.
+Every participant should check the correctness of incoming shuffles.
+If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
 These are the actions Bob as a receiver needs to perform to check the correctness of the shuffle at $i$th round if Bob has secret key $s_{B}$.
@@
 \end{algorithm}
-Note that every recipient should perform this check after each shuffling.
-Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
+Note that nobody can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
 This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds.
@@
 \subsection{Additional related work}
-Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}.
+Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol\footnote{https://github.com/AztecProtocol/AZTEC}.
 Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes.

### 2019-02-11 article/IEEE/MixEthIEEESP.tex
Fixed typos in IEEE version

@@
 \begin{abstract}
-Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries.
-These transactions are recorded in an immutable, publicly verifiable ledger.
-Due to the ledger's transparent nature, privacy is notably reduced.
-If the link between users' public key and their physical identity is exposed, their pseudonymity is lost.
-One way to increase users' privacy is to deploy coin mixing services.
-In this paper, we present MixEth, which is a trustless coin mixing service.
-MixEth is more efficient than any proposed trustless coin tumbler.
+Coin mixing is a prevalent privacy-enhancing technology for cryptocurrency users.	
+In this paper, we present MixEth, which is a trustless coin mixing service for Turing-complete blockchains.
+MixEth does not rely on trusted setup and is more efficient than any proposed trustless coin tumbler.
 It requires only 3 on-chain transactions at most per user and 1 off-chain message.
@@
 
-\subsection{Decision Diffie-Hellman Problem and 
-	Pedersen Protocol}
+\subsection{Decision Diffie-Hellman Problem and Chaum-Pedersen Protocol}
 
@@
 ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}.
-Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.
+Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assist usability.
 
@@
 Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements.
-Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying a messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
+Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages gets an additional parameter $G^{'}$, which is not necessarily the standardized generator element.
 Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.
@@
 Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
-This means that users are no longer required to sign transactions with ECDSA.
-Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
+This means that users would no longer be obliged to sign transactions with ECDSA.
 
@@
 $0\lor1\leftarrow 
-ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is DDH-tuples: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$.
+ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is a DDH-tuple: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$.
 If the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected.
@@
 Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW.
-In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
+In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denoted as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
 
@@
 
-A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
+A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether (or tokens) to be mixed.
 
@@
 This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds.
-key.
 
@@
 Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
-However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
-No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
+However the gas cost of the withdrawal transaction increases linearly in the number of receivers ($\num[group-separator={,}]{335714}n$ gas), which limits the size of possible anonymity sets.
+No more than 24 reciever could use Möbius with current cca.
+$\num[group-separator={,}]{8000000}$  block gas limit.
 If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
@@
 The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
-However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
-A severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+However there are disadvantages of this approach; A severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
 If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
@@
 In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
-\begin{table}[H] 
+\begin{table}
 	\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.

### 2019-02-13 test/TestMultiSend.js
Added tests to measure gas costs of multisend withdrawal

@@ -1,0 +1,148 @@
+let MinimumViableMultiSig = artifacts.require("./MinimumViableMultisig");
+let LibSignature = artifacts.require("./LibSignature");
+let MultiSend = artifacts.require("./MultiSend");
+
+let Web3latest = require("web3");
+let web3latest = new Web3latest(new Web3latest.providers.HttpProvider("http://localhost:8545"));
+let MinimumViableMultiSigContract = new web3latest.eth.Contract(MinimumViableMultiSig.abi);
+let LibSignatureContract = new web3latest.eth.Contract(LibSignature.abi);
+let MultiSendContract = new web3latest.eth.Contract(MultiSend.abi);
+
+const sign = async (hash, address, web3) => {
+    const sig = await web3.eth.sign(hash, address);
+    const v = (parseInt(sig.substring(sig.length - 2)) + 27).toString(16);
+    const rest = sig.substring(0, sig.length - 2);
+    const addedSig = rest + v;
+    return addedSig.substring(2);
+};
+
+contract("Gas tests for multisig and multisend", function(accounts) {
+    it("MultiSig", async () => {
+        // init
+        const from = accounts[0];
+        const multiSigSigners = accounts.sort((a, b) => a > b);
+        const to = accounts[1];
+        const sendValue = 2000000;
+
+        const multiSig = await MinimumViableMultiSigContract.deploy({ data: MinimumViableMultiSig.bytecode }).send({
+            from,
+            gas: 1500000
+        });
+
+        // setup
+        const setup = await multiSig.methods.setup(multiSigSigners).send({ from, gas: 6000000 });
+        const deposit = await web3latest.eth.sendTransaction({ from, to: multiSig.options.address, value: 10000000 });
+
+        // prepare tx
+        const calculateHash = await multiSig.methods.getTransactionHash(to, sendValue, "0x", 0).call();
+        let sig = "0x";
+        for (let i = 0; i < multiSigSigners.length; i++) {
+            sig += await sign(calculateHash, multiSigSigners[i], web3latest);
+        }
+
+        // exec tx
+        const execTransactionResult = await multiSig.methods
+            .execTransaction(to, sendValue, "0x", 0, sig)
+            .send({ from, gas: 6000000 });
+        console.log(`Exec transaction for ${multiSigSigners.length} person`, execTransactionResult.gasUsed);
+    });
+
+    it("MultiSend", async () => {
+        // init
+        const from = accounts[0];
[…]

### 2019-02-13 truffle.js

@@ -15,5 +15,11 @@ module.exports = {
       },
       network_id: 1
     }
+  },
+  compilers:{
+    solc:{
+        version: "0.4.24"
+    }
   }
+  
 };

### 2019-02-17 article/IEEE/MixEthIEEESP.tex
Added TEE to Extensions in IEEE version

@@
 
-\author{\IEEEauthorblockN{István András Seres\IEEEauthorrefmark{1},
-		Dániel A. Nagy\IEEEauthorrefmark{2}, Péter Burcsi\IEEEauthorrefmark{3}}
-	\IEEEauthorblockA{Department of Computer Algebra,
-		Eötvös Loránd University\\
-		Budapest, Hungary\\
-		Email: \IEEEauthorrefmark{1}istvanseres@caesar.elte.hu,
-		\IEEEauthorrefmark{2}daniel@ethereum.org,
-		\IEEEauthorrefmark{3}bupe@inf.elte.hu}
-\and
-\IEEEauthorblockN{Chris Buckland \thanks{Chris Buckland is supported by an Ethereum Foundation
-		scaling grant and an Ethereum Community Fund grant.}}
-\IEEEauthorblockA{\textit{Department of Computer Science} \\
-	\textit{King's College London}\\
-	London, United Kingdom \\
-	cpbuckland88@gmail.com }
-}
+%\author{\IEEEauthorblockN{István András Seres\IEEEauthorrefmark{1},
+%		Dániel A. Nagy\IEEEauthorrefmark{2}, Péter Burcsi\IEEEauthorrefmark{3}}
+%	\IEEEauthorblockA{Department of Computer Algebra,
+%		Eötvös Loránd University\\
+%		Budapest, Hungary\\
+%		Email: \IEEEauthorrefmark{1}istvanseres@caesar.elte.hu,
+%		\IEEEauthorrefmark{2}daniel@ethereum.org,
+%		\IEEEauthorrefmark{3}bupe@inf.elte.hu}
+%\and
+%\IEEEauthorblockN{Chris Buckland \thanks{Chris Buckland is supported by an Ethereum Foundation
+%		scaling grant and an Ethereum Community Fund grant.}}
+%\IEEEauthorblockA{\textit{Department of Computer Science} \\
+%	\textit{King's College London}\\
+%	London, United Kingdom \\
+%	cpbuckland88@gmail.com }
+%}
 
@@
 In this paper, we present MixEth, which is a trustless coin mixing service for Turing-complete blockchains.
-MixEth does not rely on trusted setup and is more efficient than any proposed trustless coin tumbler.
+MixEth does not rely on a trusted setup and is more efficient than any proposed trustless coin tumbler.
 It requires only 3 on-chain transactions at most per user and 1 off-chain message.
@@
 The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys.
-This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.
+This powerful technique gives users superior privacy and anonymity since their new received coins can not be linked to them.
 
@@
 The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}.
-Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases.
-As the Ethereum network is congested, ie.
-blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
+Both of them burn tremendous amounts of gas to withdraw funds, i.e., they do not support large anonymity sets, which could be prohibitive for many use cases.
+Efficiency is also crucial from a scalibility point of view.
+As the Ethereum network is congested, i.e., blocks were full during 2018\footnote{https://etherscan.io/chart/gasused}, we argue that it is essential for the network scalability to aim to create protocols and applications that burn as few gas as possible.
+Moreover Miximus relies on a trusted setup to generate the proving and verification keys for the zkSNARK.
 
@@
 
-To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
+To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency and trusted setup issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
@@
 
-In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e.
-no efficient adversary could forge a signature on any given message with non-negligible probability.
+In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e., no efficient adversary could forge a signature on any given message with non-negligible probability.
 
@@
 	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\textbf{Input}$(PK_{i}, PK_{i-1}, proof_{ChP}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
 	\begin{algorithmic}[1]
@@
 
-We implemented MixEth with two different approaches\footnote{https://github.com/seresistvanandras/MixEth}.
+We implemented MixEth with two different approaches.
 The first implementation of MixEth does not apply state channels, all transactions are made on-chain.
@@
 \begin{table}
-	\caption{Implementation gas cost results.
+	\caption{Implementation gas cost results per participants.
 MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods.
@@
 		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&TBD\\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&$\num[group-separator={,}]{26749}$\\
 		\bottomrule
@@
 The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
-However there are disadvantages of this approach; A severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+However there are disadvantages of this approach; A severe limitation of Miximus is the trusted setup required for generating the proving and verification keys for the zkSNARK.
 If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
@@
 On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes.
-Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions.
-For instance on top Aztec one could use MixEth to shuffle Aztec notes.
+Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonymity and confidential transactions.
+For instance on top of Aztec one could use MixEth to shuffle Aztec notes.
+
+\section{Extensions and improvements}
+One might effectively minimize the number of necessary shuffling rounds to $1$.
+If a Trusted Execution Environment (TEE), e.g., Intel SGX is used to generate the shuffling transaction, then even a single shuffling transaction would suffice to provide the same level of anonymity as if every participant shuffles the public keys.
+Any of the participants could upload the TEE-generated shuffling transaction, while the MixEth contract could check that indeed the shuffling transaction was generated by a TEE.
+Such a shortcut would make our scheme even more practical and efficient, however it would subsume trust in Intel regarding the security and confidentiality of the TEE.
 
 \section{Acknowledgements}
-We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+We would like to thank Liam Horne for helping with the state channel implementation, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 

### 2019-03-30 article/main.tex
Revised article, fixed typos, added clarifications

--- 2018-12-29 article/main.tex
@@
 \begin{abstract}
-Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries.
-These transactions are recorded in an immutable, publicly verifiable ledger.
-Due to the ledger's transparent nature, privacy is notably reduced.
-If the link between users' public key and their physical identity is exposed, their pseudonymity is lost.
-One way to increase users' privacy is to deploy coin mixing services.
-In this paper, we present MixEth, which is a trustless coin mixing service.
-MixEth is more efficient than any proposed trustless coin tumbler.
-It requires only $3$ on-chain transactions at most per user and $1$ off-chain message.
+Coin mixing is a prevalent privacy-enhancing technology for cryptocurrency users.
+In this paper, we present MixEth, which is a trustless coin mixing service for Turing-complete blockchains.
+MixEth does not rely on a trusted setup and is more efficient than any proposed trustless coin tumbler.
+It requires only 3 on-chain transactions at most per user and 1 off-chain message.
 It achieves strong notions of anonymity and is able to resist denial-of-service attacks.
-Furthermore the underlying protocol can also be used to efficiently shuffle ballots, cyphertexts in a trustless and decentralized manner.
+Furthermore the underlying protocol can also be used to efficiently shuffle ballots, ciphertexts in a trustless and decentralized manner.
 \end{abstract}
@@
 Moreover, coherent public keys, which are used by the same user, can be clustered merely by analyzing the ledger.
-Recently several tools and algorithms were proposed to diminish users' privacy (\cite{meiklejohn2013fistful},\cite{moser2013inquiry}, \cite{moreno2016listening}).
+Recently several tools and algorithms were proposed to diminish users' privacy \cite{meiklejohn2013fistful,moser2013inquiry,moreno2016listening}.
 Such deanomyzation attacks are extremely harmful to user privacy, especially in the case when any of the users' pseudonyms, public keys, are linked to their real world identity.
@@
 The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys.
-This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.
-
-Several coin mixing protocols were proposed in the literature both centralized (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}, \cite{heilman2017tumblebit}) and decentralized (\cite{maxwell2013coinjoin}, \cite{ruffing2014coinshuffle}, \cite{miximus2018}, \cite{meiklejohn2018mobius}, \cite{bissias2014sybil}).
-A major drawback of centralized coin mixing is that the availability of the tumbler is entirely dependent on the trusted party and in most cases theft prevention can not be guaranteed (\cite{bonneau2014mixcoin}, \cite{valenta2015blindcoin}).
+This powerful technique gives users superior privacy and anonimity since their new received coins cannot be linked to them.
+
+Several coin mixing protocols were proposed in the literature both centralized \cite{bonneau2014mixcoin,valenta2015blindcoin,heilman2017tumblebit} and decentralized \cite{maxwell2013coinjoin,ruffing2014coinshuffle,miximus2018,meiklejohn2018mobius,bissias2014sybil}.
+A major drawback of centralized coin mixing is that the availability of the tumbler is entirely dependent on the trusted party and in most cases theft prevention cannot be guaranteed \cite{bonneau2014mixcoin,valenta2015blindcoin}.
 On the other hand decentralized tumblers achieve availability, theft prevention and satisfy strong notions of anonymity although they are considerably heavier computationally.
@@
 
-Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
+Even though (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.
 
 \textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains.
-This protocol can be used to shuffle cyphertexts, ballots or public keys.
-The protocol have many use cases: shuffling ElGamal-cyphertexts, decentralized mixnets, e-voting.
-
-To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}).
+This protocol can be used to shuffle ciphertexts, ballots or public keys.
+The protocol have many use cases: shuffling ElGamal-ciphertexts, decentralized mixnets, e-voting.
+
+To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals \cite{meiklejohn2018mobius,miximus2018}.
 MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.
 
+The intuition behind MixEth is to apply Neff's verifiable shuffles \cite{neff2001verifiable} in the context of coin mixing.
+Participants of the tumbler shuffle their public keys in order to break links between sender and recipient public keys.
+The key insight is that verifying on-chain a Neff proof about the correctness of a shuffle would be too gas-inefficient, therefore we require receivers to be online to issue fraud proofs, if and only if an incorrect shuffle was made.
+Whenever recipients consider that enough shuffling was executed, they can withdraw their funds from the mixer.
+
 We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.
-Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back to on-chain.
+Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back on-chain.
 
@@
 So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well.
-The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.
+The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succinct proofs for the incorrectness of the shuffle, if applicable.
 
@@
 
- Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if possesses the multipliers.
+ Although it is hard to decide whether a triplet is a DDH-triplet without knowing the multipliers, one could convince anyone in zero-knowledge that a tuple is indeed a DDH-tuple if one possesses the multipliers.
 
@@
 
+Note that although Ethereum does not support natively the verification of ECDSA signatures with respect to arbitrary generators, however it can easily be implemented in a smart contract.
+
 \subsection{Ethereum}
@@
 
-EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}.
+EVM is quasi-Turing complete, since smart contract's code cannot run indefinitely due to the so called \textit{gas mechanism}.
 In every transaction the sender needs to pay upfront for the execution of the contract's code.
@@
 If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner.
-If there are gas left after successful execution, transaction originator is reimbursed.
+If there is gas left after successful execution, transaction originator is reimbursed.
 Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block.
@@
 $\num[group-separator={,}]{8000000}$ gas.
-Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees.
+Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as little as possible on transactions fees.
 Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.
@@
 State channels were first described in detail by Jeff Coleman et al.\cite{coleman2018counterfactual}.
-Since then several other frameworks for generalised state channels were elaborated (\cite{dziembowski2017perun},\cite{mccorryyou}).
+Since then several other frameworks for generalised state channels were elaborated \cite{dziembowski2017perun,mccorryyou}.
 Recently a case study of the Battleship game was published by Patrick McCorry, Chris Buckland et al.
@@
 Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
-When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they can not do this from a fresh address, since it does not hold any ether.
-Since as of now only the sender of a transaction can pay for the gas fee, users can not withdraw their funds unless they ask someone to fund their fresh address.
+When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they cannot do this from a fresh address, since it does not hold any ether.
+Since as of now only the sender of a transaction can pay for the gas fee, users cannot withdraw their funds unless they ask someone to fund their fresh address.
 
@@
 A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys.
+The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
 In all the following interactions and algorithms we assume that the public state of the tumbler is implicitly given as input.
@@
 
-$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.
+$tx\stackrel{\$}{\leftarrow}Deposit(tumblers,sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.
 
@@
 Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW.
-In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.
+In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively.
 
@@
 \subsubsection{Anonymity} \label{sec:defanonymity}
-\textit{Sender} anonymity is achieved if an adversary can not determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
+\textit{Sender} anonymity is achieved if an adversary cannot determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
 
@@
 	\end{table}	
-Then the tumbler satisfies sender or recipient anonymity if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.
+Then the tumbler satisfies sender or recipient anonymity if for all PPT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.
 \end{definition}
@@
 \subsubsection{Availability}
-It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and one but all recipients are compromised.
-
-Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient can not withdraw their funds.
+It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and all but one recipients are compromised.
+
+Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient cannot withdraw their funds.
 
@@
 	\end{table}	
-	Then the tumbler satisfies availability if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+	Then the tumbler satisfies availability if for all PPT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
 \end{definition}
@@
 	\end{table}	
-	Then the tumbler satisfies theft prevention if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
+	Then the tumbler satisfies theft prevention if for all PPT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
 \end{definition}
@@
 
-\subsection{Overview}
 MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
-\subsection{Initializing the tumbler}
+\subsection{Initializing the tumbler and depositing period}
 
 A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
-
-\subsection{Depositing period}
 Every sender must deposit exactly $amt$ ether to a specific public key.
@@
 Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
-If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should multiply all the public keys with a secret exponent $c$ and then permute all the transformed public keys.
+If a challenge is accepted, then shuffler's deposit is lost and given to the challenger, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
 Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
 
-Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+Computing the shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
 
@@
 	\begin{algorithmic}[1]
-		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i})$ 
+		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i}))$ 
 		\State $b^*\leftarrow0$
@@
 
+In Procedure \ref{verifyingshufflingoffchain} $verifyChaumPedersen(proof_{DDH})$ denotes a deterministic polynomial-time algorithm which verifies the correctness of a Chaum-Pedersen zero-knowledge proof.
+The algorithm outputs $1$ if the proof is verified, otherwise $0$.
+
 \subsection{Withdrawing}
@@
 \subsection{Availability}
-If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
+If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who cannot send any transactions to honest Ethereum peers.
 \subsection{Theft prevention} 
@@
 \end{table}
-
+\newpage
 \section{Implementation}
@@
 This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
+
+Although MixEth is more gas-efficient than Möbius or Miximus, it incurs a higher time-complexity, ie.
+recipients need to expect longer delays for funds to arrive since each challenging period lasts a few blocks of time.
+Furthermore MixEth requires users to be online during the course of mixing, in some scenarios this might be a demanding requirement.
 
@@
 
-On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas.
+On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element then storing only consumes $\num[group-separator={,}]{5000}$ gas.
 To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
@@
 A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
-However note that the gas complexity of shuffling transactions grow linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
+However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
 $\num[group-separator={,}]{800}$.
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&TBD&TBD&0&0&TBD\\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&$\num[group-separator={,}]{26749}$\\
 		\bottomrule
@@
 No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
-If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
+If more people tried to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
 Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
@@
 
-Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}.
+Miximus is a zkSNARK-based mixer for Ethereum\cite{miximus2018}.
 It uses zkSNARKs to conceal the mapping between depositors and recipients.
@@
 
-\section{Conclusion and Future Work} \label{conclusion}
-We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance.
-An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.
-
 \section{Acknowledgements}
@@
 scaling grant and an Ethereum Community Fund grant.
-We would like to thank Liam Horne for helping with the state channel implementation, Patrick McCorry for proofreading, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
+We would like to thank Liam Horne for helping with the state channel implementation, Barry WhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
 
@@
 Let us assume that the challenge to the DDH-adversary $\bdv$ is of the form $(sG,cG,c_{0}G)$.
+In a DDH-game the adversary's goal is to decide whether $c_{0}G$ is a random group element or it equals to $scG$.
+At the end of the DDH-game adversary outputs $1$ if $c_{0}G=scG$ and $0$ otherwise.
 Adversary $\bdv$ generates uniformly random public key $c_{1}G$ and invokes $\adv$ with the set $\textsf{PK}_{B}=(c_{0}C^{*}, c_{1}C^{*})$, then $\bdv$ forwards $\textsf{PK}_{B}$ to $\adv$.
@@
 By assumption $\adv$ outputs with non-negligible probability valid withdraw transaction belonging to one of the public keys in the mixer.
-$\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
+A valid withdraw transaction is a $(tx,\sigma_{tx})$ pair, where $\sigma_{tx}$ is a valid signature on transaction $tx$.
+Adversary $\bdv$ outputs the withdraw transaction and the ECDSA signature on it.
 $\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:

### 2019-04-01 article/main.tex
Fixed errors and typos in article

@@
 
+\date{}
 \makeatletter
@@
 \end{abstract}
-\keywords{Cryptography, Verifiable shuffle, Cryptocurrency, Ethereum, Coin mixer, State Channel}
+\keywords{Cryptography, Verifiable shuffle, Anonymity, Cryptocurrency, Ethereum, Coin mixer, State Channel}
 
@@
 
-Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed.
+Let $PK_{0}$ denote the set of public keys to be mixed after the depositing period.
+Generally $PK_{i}$ will denote the set of shuffled public keys after $i$ shuffling round.
 Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve.
-Anyone is allowed to shuffle the public keys at most once by paying some deposit to the tumbler contract:
-
-$PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
-Let us call $C^{*}_{i}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
+Similarly $C^{*}_{i}$ denotes the shuffling accumulated constant after the $i$th shuffling round.
+Shuffles are computed off-chain, the outputs of the algorithm are written into the on-chain mixer contract.
+Anyone is allowed to shuffle the public keys by paying some deposit to the tumbler contract.
+
+$PK_{i+1},C_{i+1}^{*},proof_{DDH}(G,c_{i}G,C^{*}_{i},C^{*}_{i+1})\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$.
+The new shuffling accumulated constant $C^{*}_{i+1}$ can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$.
 The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period.
-The permutation $\pi$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
+The permutation $\pi_{i}$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled.
 All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.
+
+Note that we need an additional Chaum-Pedersen proof from the shuffler in order to prove that the shuffler knows a secret multiplier between the new and the previous shuffling accumulated constants.
+If we did not require such proof, a malicious shuffler could break anonymity just by uploading a random shuffle of the original public keys, the set $PK_{0}$.
+
+ $0\lor1\leftarrow ProcessShuffle(PK_{i+1},C_{i+1}^{*},proof_{DDH}(G,c_{i}G,C^{*}_{i},C^{*}_{i+1}))$.
+If the mixing contract is in a shuffling period and the Chaum-Pedersen proof is verified, then $(PK_{i+1},C_{i+1})$ is written into the contract state, otherwise shuffling transactions is reverted.
 
@@
 Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
-If a challenge is accepted, then shuffler's deposit is lost and given to the challenger, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
+If a challenge is accepted, then shuffler's deposit is lost and given to the challenger, the incorrect shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
 In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
-Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.
-
-Computing the shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys along with a Chaum-Pedersen proof, proving the correctness of the new shuffling accumulated constant.
+
+Computing the shuffle is done off-chain, see Procedure \ref{shufflingoffchain}, however the new set of shuffled public keys, the updated shuffling accumulated constant and the Chaum-Pedersen proof are loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+In Procedure \ref{shufflingoffchain} the function $generateChaumPedersen(G,A,B,C)$ denotes a PPT algorithm, which generates a Chaum-Pedersen proof, proving that $\log_{G}(A)=\log_{B}(C)$.
+The mixing contract accepts a shuffling transaction if and only if the contract is in a shuffling period and the Chaum-Pedersen proof is verified, otherwise rejects.
 
@@
 	\State $C^{*}_{i}=cC^{*}_{i-1}$
-
-\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i})$ 
+	\State $proof_{DDH}=generateChaumPedersen(G,cG,C^{*}_{i-1},C^{*}_{i})$
+
+\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i},proof_{DDH})$ 
 \end{algorithmic}   
@@
 \end{table}
-\newpage
+
 \section{Implementation}
@@
 A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
-However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than cca.
-$\num[group-separator={,}]{800}$.
+However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than a few hundreds.
 
@@
 		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{366216}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
 		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&$\num[group-separator={,}]{26749}$\\

### 2019-04-08 article/OASIcs/MixEth_Seres_Nagy_Buckland_Burcsi_2019.tex
OASIcs version of paper added

--- 2019-04-01 article/main.tex
@@
-\documentclass[a4paper]{article}
-
-%% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{authblk}
+\documentclass[a4paper,UKenglish,cleveref, autoref]{oasics-v2019}
+%This is a template for producing OASIcs articles. 
+%See oasics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+%for section-numbered lemmas etc., use "numberwithinsect"
+%for enabling cleveref support, use "cleveref"
+%for enabling cleveref support, use "autoref"
+
 \usepackage{booktabs}
-\usepackage{ae,aecompl}
-%% Sets page size and margins
-\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-%% Useful packages
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 \usepackage{pgfplots}
@@
 \usepackage[colorinlistoftodos]{todonotes}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
 
@@
 
-\title{MixEth: efficient, trustless coin mixing service for Ethereum}
-\author[1]{István András Seres}
-\author[1]{Dániel A. Nagy}
-\author[2]{Chris Buckland}
-\author[1]{Péter Burcsi}
-\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
-\affil[2]{King's College London}
+\title{MixEth: efficient, trustless coin mixing service for Ethereum} %TODO Please add
+
+\titlerunning{MixEth: efficient, trustless coin mixing service for Ethereum}%optional, please use if title is longer than one line
+
+\author{István András Seres\footnote{Corresponding author: István András Seres, istvanseres@caesar.elte.hu}}{Eötvös Loránd University, Hungary \and \url{http://istvanseres.web.elte.hu/} }{istvanseres@caesar.elte.hu}{https://orcid.org/0000-0003-0143-4057}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+Please provide at least the name of the affiliation and the country.
+The full address is optional
+
+\author{Dániel A. Nagy}{Eötvös Loránd University, Hungary}{daniel@ethereum.org}{}{}
+\author{Chris Buckland}{King's College London, United Kingdom}{cpbuckland88@gmail.com}{}{is supported by an Ethereum Foundation scaling grant and an Ethereum Community Fund grant.}
+\author{Péter Burcsi}{Eötvös Loránd University, Hungary}{bupe@inf.elte.hu}{https://orcid.org/0000-0003-3306-6500}{}
+
+\authorrunning{I.\,A. Seres and D.\,A. Nagy and C. Buckland and P. Burcsi}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{István András Seres and Dániel A.
+Nagy and Chris Buckland and Péter Burcsi}%TODO mandatory, please use full first names.
+OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc{Theory of computation~Cryptographic protocols}
+%\ccsdesc[100]{Theory of Computation~Computational complexity and cryptography~Cryptographic protocols}
+%\ccsdesc[100]{Cryptographic protocols}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Cryptography, Verifiable shuffle, Anonymity, Cryptocurrency, Ethereum, Coin mixer, State Channel}%TODO mandatory; please add comma-separated list of keywords
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\relatedversion{A full version of the paper is available at \url{...}.}
+
+\supplement{\url{https://github.com/seresistvanandras/MixEth}}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+\funding{The research at Eötvös Loránd University was partially supported by the European Union, co-financed by the European Social Fund (EFOP-3.6.2-16-2017-00012).}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{We would like to thank Liam Horne for helping with the state channel implementation, Barry Whitehat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%\hideOASIcs  %uncomment to remove references to OASIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\EventEditors{John Q. Open and Joan R. Access}
+%\EventNoEds{2}
+%\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+%\EventShortTitle{CVIT 2016}
+%\EventAcronym{CVIT}
+%\EventYear{2016}
+%\EventDate{December 24--27, 2016}
+%\EventLocation{Little Whinging, United Kingdom}
+%\EventLogo{}
+%\SeriesVolume{42}
+%\ArticleNo{23}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{Vincent Danos, Maurice Herlihy, Maria Potop-Butucaru, Julien Prat, and Sara Tucci-Piergiovanni}
+\EventNoEds{5}
+\EventLongTitle{International Conference on Blockchain Economics, Security and Protocols (Tokenomics 2019)}
+\EventShortTitle{Tokenomics 2019}
+\EventAcronym{Tokenomics}
+\EventYear{2019}
+\EventDate{May 6--7, 2019}
+\EventLocation{Paris, France}
+\EventLogo{}
+\SeriesVolume{71}
+\ArticleNo{11}
+
 \begin{document}
+
 \maketitle
 
+%TODO mandatory: add short abstract of the document
 \begin{abstract}
@@
 \end{abstract}
-\keywords{Cryptography, Verifiable shuffle, Anonymity, Cryptocurrency, Ethereum, Coin mixer, State Channel}
 
@@
 
-\subsubsection{Ethereum account abstraction}
-Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
-When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they cannot do this from a fresh address, since it does not hold any ether.
-Since as of now only the sender of a transaction can pay for the gas fee, users cannot withdraw their funds unless they ask someone to fund their fresh address.
-
-Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}.
-EIP86 permits receivers of a transaction paying the gas fee.
-This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses.
-Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
-This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA).
-Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
-
 \section{Threat model}
@@
 We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention.
-These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.
+These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in the Appendices for sake of self-containedness.
 
@@
 Finally we assume that honest recipients will always exercise their rights to shuffle and they do not disclose any private information used in their shuffles.
+
+Hereby we only give intuition for the notions of security, for formal definitions the astute reader is referred to the Appendices.
+
+\subsubsection{Anonymity} \label{sec:defanonymity}
+\textit{Sender} anonymity is achieved if an adversary cannot determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
+
+\textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
+
+\subsubsection{Availability}
+It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and all but one recipients are compromised.
+
+Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient cannot withdraw their funds.
+
+\subsubsection{Theft prevention} \label{sec:theftprevention}
+We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.
+
+\section{MixEth}
+
+MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
+\subsection{Initializing the tumbler and depositing period}
+
+A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
+Every sender must deposit exactly $amt$ ether to a specific public key.
+Deposits with incorrect ether value or invalid public key are rejected.
+Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.
+
+\subsection{Shuffling period}
+After the depositing round, shuffling and challenging rounds are coming after in turns.
+Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
+If a challenge is accepted, then shuffler's deposit is lost and given to the challenger, the incorrect shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
+In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
+Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys along with a Chaum-Pedersen proof, proving the correctness of the new shuffling accumulated constant.
+
+Computing the shuffle is done off-chain, see Procedure \ref{shufflingoffchain}, however the new set of shuffled public keys, the updated shuffling accumulated constant and the Chaum-Pedersen proof are loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
+In Procedure \ref{shufflingoffchain} the function $generateChaumPedersen(G,A,B,C)$ denotes a PPT algorithm, which generates a Chaum-Pedersen proof, proving that $\log_{G}(A)=\log_{B}(C)$.
+The mixing contract accepts a shuffling transaction if and only if the contract is in a shuffling period and the Chaum-Pedersen proof is verified, otherwise rejects.
+
+\begin{algorithm}
+	\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
+	\begin{algorithmic}[1]
+		\State $PK_{i} \gets []$
+		\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
+		\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
+		\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
+		\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
+		\For{$j=0;j<|PK_{i-1}|;j++$}
+		\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
+		\EndFor
+		\State $C^{*}_{i}=cC^{*}_{i-1}$
+		\State $proof_{DDH}=generateChaumPedersen(G,cG,C^{*}_{i-1},C^{*}_{i})$
+
+		\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i},proof_{DDH})$ 
+	\end{algorithmic}   
+\end{algorithm}
+\subsection{Challenging period}
+Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round.
+These are the actions Bob as a receiver needs to perform to check the correctness of the shuffle at $i$th round if Bob has secret key $s_{B}$.
+In this case Bob should check whether $s_{B}C^{*}_{i} \in PK_{i}$ or not.
+If not, Bob should prove to MixEth that the $i$th round is indeed the first round, where the shuffled public key corresponding to $s_{B}$ is compromised.
+The Chaum-Pedersen proof in the challenge transaction ensures that the integrity of the shuffled public key in round $i-1$st is intact, while shuffled public key is compromised in the $i$th round.
+
+\begin{algorithm}
+	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
+	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
+	\begin{algorithmic}[1]
+		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i}))$ 
+		\State $b^*\leftarrow0$
+		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
+		\State $b^*\gets 1$
+		\Else
+		\State $b^*\gets 0$
+		\EndIf
+		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
+	\end{algorithmic}   
+\end{algorithm}
+Note that every recipient should perform this check after each shuffling.
+Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
+This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
+
+In Procedure \ref{verifyingshufflingoffchain} $verifyChaumPedersen(proof_{DDH})$ denotes a deterministic polynomial-time algorithm which verifies the correctness of a Chaum-Pedersen zero-knowledge proof.
+The algorithm outputs $1$ if the proof is verified, otherwise $0$.
+
+\subsection{Withdrawing}
+Let $C^*_{final}$ be the final shuffling accumulated constant.
+For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*_{final}$.
+The recipient can prove to MixEth that she knows secret key $s_{B}$ by signing their public key using a modified ECDSA, which uses $C^*_{final}$ as the generator element instead of the standardized $G$.
+
+\section{Security}
+Notions of security are proven in the Appendices.
+
+\section{Implementation}
+
+We implemented MixEth with two different approaches.
+The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
+This could lead to unwanted gas costs as the number of corrupted shuffles increases.
+One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible.
+Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
+Both of the implementations allow users to mix Ether or other ERC20-compatible, a popular Ethereum token standard, tokens.
+
+One of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
+A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
+Since the block gas limit is $\num[group-separator={,}]{8000266}$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
+This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
+
+Although MixEth is more gas-efficient than Möbius or Miximus, it incurs a higher time-complexity, ie.
+recipients need to expect longer delays for funds to arrive since each challenging period lasts a few blocks of time.
+Furthermore MixEth requires users to be online during the course of mixing, in some scenarios this might be a demanding requirement.
+
+All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts.
+All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
+
+\subsection{Fully on-chain implementation} \label{fullyonchainimpl}
+Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
+There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender.
+The rest of the protocol happens entirely on-chain.
+
+On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element then storing only consumes $\num[group-separator={,}]{5000}$ gas.
+To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
+Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
+Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract.
+Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.
+
+A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets.
+One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time.
+As soon as the anonymity set is large enough a receiver could withdraw their assets.
+A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
+This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
+A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
+However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than a few hundreds.
+
+\subsection{State channel implementation} \label{statechannelimpl}
+
+We have also adapted MixEth to operate within a state channel.
+We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}.
+This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic.
+Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront.
+In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$.
+To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state.
+The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round.
+In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass.
+In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
+To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.
+
+Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic.
+Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic.
+This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle.
+After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round.
+Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.
+If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur.
+In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain.
+A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.
+Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
+
+\begin{table}[H] 
+	\caption{Proof-of-concept implementation gas cost results.
+Expect further improvements.
+MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
+	\centering 
+	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
+		\toprule
+		\hline
+		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
+		\cline{4-5}&&&Shuffle upload&Challenge\\
+		\hline
+		\midrule
+		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
+		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
+		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{366216}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
+		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&$\num[group-separator={,}]{26749}$\\
+		\bottomrule
+	\end{tabular}
+	\label{table:gasproperties}
+\end{table}
+
+\section{Related work}
+Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
+Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability.
+These properties could be used to evaluate and compare existing and future proposals from a security perspective.
+Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
+However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
+No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
+If more people tried to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
+
+Miximus is a zkSNARK-based mixer for Ethereum\cite{miximus2018}.
+It uses zkSNARKs to conceal the mapping between depositors and recipients.
+A depositor creates a leaf in a Merkle-tree.
+A depositor needs to exchange the preimage of the leaf with the recipient.
+Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf.
+So called nullifiers enable recipients to withdraw funds once and only once.
+The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
+However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
+Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
+If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
+Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
+
+As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
+In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
+\begin{table}[H] 
+	\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
+Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
+	\centering 
+	\begin{tabular}{lcc}
+
+		\toprule
+		&\#Off-chain messages& \#Transactions \\
+		\midrule
+		\textbf{Centralized} & & \\
+		\midrule
+		Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
+		Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
+		TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
+		\midrule
+		\textbf{Decentralized}      &    &      \\
+		\midrule
+		Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
+		Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
+		XIM \cite{bissias2014sybil} & 0      & 7       \\
+		Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
+		Miximus \cite{miximus2018} & 1+MPC & 2 \\
+		MixEth & 1 & 3 \\
+		MixEthChannel  & $\mathcal{O}(n)$ &2 \\
+		\bottomrule
+	\end{tabular}
+	\label{table:communicationcomplexity}
+\end{table}
+
+\newpage
+\bibliographystyle{plainurl}% the mandatory bibstyle
+\bibliography{sample}
+
+\newpage
+\begin{appendices}
+
+\section{Formal definitions of security}
+
+Hereby we formally define the notions of security MixEth is aiming to achieve.
 
@@
 
-From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.
-
-\subsubsection{Anonymity} \label{sec:defanonymity}
-\textit{Sender} anonymity is achieved if an adversary cannot determine to whom honest senders are sending funds, assuming that honest senders' deposits are indistinguishable.
-
-\textit{Recipient} anonymity is achieved if honest recipients withdrawal transactions are indistinguishable.
-
+\subsection{Anonymity} \label{appenddefanonymity}
 \begin{definition}
@@
 \end{definition}
-
-\subsubsection{Availability}
-It is essential for a coin mixer to provide availability, meaning that honest recipients can always withdraw their money from the mixer, even if senders and all but one recipients are compromised.
-
-Adversary $\adv$ wins the availability security game if they manage to get the tumbler into a state where honest recipient cannot withdraw their funds.
-
+\subsection{Availability} \label{appenddefavailability}
 \begin{definition}
@@
 \end{definition}
-
-\subsubsection{Theft prevention} \label{sec:theftprevention}
-We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:
-
+\subsection{Theft prevention} \label{appenddeftheftprevention}
 \begin{definition}
@@
 
-\section{MixEth}
-
-MixEth is a coin mixing smart contract allowing parties to efficiently tumble coins in a trustless manner on Ethereum.
-\subsection{Initializing the tumbler and depositing period}
-
-A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
-Every sender must deposit exactly $amt$ ether to a specific public key.
-Deposits with incorrect ether value or invalid public key are rejected.
-Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.
-
-\subsection{Shuffling period}
-After the depositing round, shuffling and challenging rounds are coming after in turns.
-Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone.
-If a challenge is accepted, then shuffler's deposit is lost and given to the challenger, the incorrect shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle.
-In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys.
-Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys along with a Chaum-Pedersen proof, proving the correctness of the new shuffling accumulated constant.
-
-Computing the shuffle is done off-chain, see Procedure \ref{shufflingoffchain}, however the new set of shuffled public keys, the updated shuffling accumulated constant and the Chaum-Pedersen proof are loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.
-In Procedure \ref{shufflingoffchain} the function $generateChaumPedersen(G,A,B,C)$ denotes a PPT algorithm, which generates a Chaum-Pedersen proof, proving that $\log_{G}(A)=\log_{B}(C)$.
-The mixing contract accepts a shuffling transaction if and only if the contract is in a shuffling period and the Chaum-Pedersen proof is verified, otherwise rejects.
-
-\begin{algorithm}
-\caption{Off-chain public key shuffling algorithm for the $i$th shuffling round}\label{shufflingoffchain}
-\begin{algorithmic}[1]
-	\State $PK_{i} \gets []$
-	\State $c\stackrel{\$}{\leftarrow}\mathbb{Z}_n$
-	\State $C^{*}_{i-1}\leftarrow read\ from\ MixEth\ contract$
-	\State $PK_{i-1}\leftarrow read\ from\ MixEth\ contract\ the\ current\ sequence\ of\ shuffled\ public\ keys$
-	\State $\pi\stackrel{\$}{\leftarrow}S_{|PK_{i-1}|}$ 
-	\For{$j=0;j<|PK_{i-1}|;j++$}
-	\State $PK_{i}[\pi(j)]=c*PK_{i-1}[j]$ 
-	\EndFor
-	\State $C^{*}_{i}=cC^{*}_{i-1}$
-	\State $proof_{DDH}=generateChaumPedersen(G,cG,C^{*}_{i-1},C^{*}_{i})$
-
-\hspace*{\algorithmicindent} \textbf{Output:} $(PK_{i},C^{*}_{i},proof_{DDH})$ 
-\end{algorithmic}   
-\end{algorithm}
-\subsection{Challenging period}
-Every participant should check the correctness of incoming shuffles, therefore sufficient time should be provided for each challenging round.
-These are the actions Bob as a receiver needs to perform to check the correctness of the shuffle at $i$th round if Bob has secret key $s_{B}$.
-In this case Bob should check whether $s_{B}C^{*}_{i} \in PK_{i}$ or not.
-If not, Bob should prove to MixEth that the $i$th round is indeed the first round, where the shuffled public key corresponding to $s_{B}$ is compromised.
-The Chaum-Pedersen proof in the challenge transaction ensures that the integrity of the shuffled public key in round $i-1$st is intact, while shuffled public key is compromised in the $i$th round.
-
-\begin{algorithm}
-	\caption{On-chain verification algorithm of incoming shuffle challenges}\label{verifyingshufflingoffchain}
-	\hspace*{\algorithmicindent} \textbf{Input}$(PK_{i}, PK_{i-1}, proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1},C^{*}_{i},s_{B}C^{*}_{i})$ \\
-	\begin{algorithmic}[1]
-		\State $b\leftarrow verifyChaumPedersen(proof_{DDH}(C^{*}_{i-1},s_{B}C^{*}_{i-1}, C^{*}_{i},s_{B}C^{*}_{i}))$ 
-		\State $b^*\leftarrow0$
-		\If {$b \land s_{B}C^{*}_{i-1}\in PK_{i-1}\land s_{B}C^{*}_{i} \notin PK_{i}$}
-		\State $b^*\gets 1$
-		\Else
-		\State $b^*\gets 0$
-		\EndIf
-		\hspace*{\algorithmicindent} \textbf{Output:} $b^{*}$ 
-	\end{algorithmic}   
-\end{algorithm}
-Note that every recipient should perform this check after each shuffling.
-Noone can check the inclusion and correctness of shuffled public keys for recipients other than themselves.
-This task is non-outsourcable unless one reveals her own private key, which would obviously lead to loss of funds at the end of the MixEth protocol, since anyone can claim the funds knowing the corresponding secret key.
-
-In Procedure \ref{verifyingshufflingoffchain} $verifyChaumPedersen(proof_{DDH})$ denotes a deterministic polynomial-time algorithm which verifies the correctness of a Chaum-Pedersen zero-knowledge proof.
-The algorithm outputs $1$ if the proof is verified, otherwise $0$.
-
-\subsection{Withdrawing}
-Let $C^*_{final}$ be the final shuffling accumulated constant.
-For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*_{final}$.
-The recipient can prove to MixEth that she knows secret key $s_{B}$ by signing their public key using a modified ECDSA, which uses $C^*_{final}$ as the generator element instead of the standardized $G$.
-
-\subsection{MixEth formal specification}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{5.5cm}
-			\procedure{\textsf{Deposit}($sk_A, pk_{B}$)}{%
-				\pcreturn \textsf{FormTx}(sk_A,id_{\textsf{contract}}, amt, pk_{B}) }
-		\end{minipage}
-		&
-		\begin{minipage}{5.4cm}
-			\procedure{\textsf{VerifyDeposit}(tx)}{%
-				if\ (tx[amt] \neq id_{\textsf{contract}}[amt]) \ return\ 0 \\
-				if\ (pk_{B} \notin \mathbb{G}) \ return\ 0 \\
-				\pcreturn \textsf{VerifyTx(tx)}  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{\textsf{ProcessDeposit(tx)}}{%
-				add\ \textsf{addr(tx[pk]) to initPubKeys[]}}
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{5cm}
-			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
-				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
-				C^{'*} \leftarrow cC^{*} \\
-				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
-				\pcreturn (PK^{'},C^{'*}) }
-		\end{minipage}
-		&
-		\begin{minipage}{5.7cm}
-			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
-				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{ccc}
-		\begin{minipage}{6.3cm}
-			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, PK^{'}$)}{%
-				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
-				if\ (sC^{*} \notin PK) \ return\ 0 \\
-				delete (C^{'},PK^{'})\\
-				slashDeposit(shuffler(C^{'},PK^{'}))\\
-				\pcreturn 1  }
-		\end{minipage}
-		&
-		\begin{minipage}{4.6cm}
-			\procedure{\textsf{WithdrawShufflingDeposit($sk_{A}$)}}{%
-				\pcreturn \textsf{FormTx($sk_{A}, id_{contract},0$)} }
-		\end{minipage}
-		&
-		\begin{minipage}{4.6cm}
-			\procedure{\textsf{VerifyWithdrawShufflingDeposit($pk_{A}$)}}{%
-				\pcreturn shufflingDepositSlashed(pk_{A}) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\begin{tabular}{cccc}    
-		\begin{minipage}{4.7cm}
-			\procedure{\textsf{Withdraw($s,C^{*}$)}}{%
-				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
-				\pcreturn \textsf{FormTx($s,C^{*}, id_{\textsf{contract}, 0}, \sigma$)} }
-		\end{minipage}
-		&
-		\begin{minipage}{6.3cm}
-			\procedure{\textsf{VerifyWithdraw(tx)}}{%
-				if\ (sC^{*} \notin id_{\textsf{contract}}[lastShuffle] ) \ return\ 0 \\
-				if\ (\lnot\verify(C^{*}, sC^{*},\sigma, sC^{*}||tx.sender)) \ return\ 0 \\
-				\pcreturn \textsf{VerifyTx(tx)}  }
-		\end{minipage}
-		&
-		\begin{minipage}{4cm}
-			\procedure{\textsf{ProcessWithdraw(tx)})}{%
-				delete\ sC^{*} from\ id_{\textsf{contract}}[lastShuffle]   \\
-				tx^{'}\stackrel{\$}{\leftarrow} \textsf{FormTx}(id_{contract}, tx.sender, amt) }
-		\end{minipage}
-	\end{tabular}
-\end{table}
-
-\section{Security}
-This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.
+\section{Proofs of security}
+
+This section provides informal ideas to the security proofs for the notions of security introduced formally above and informally in Section \ref{securitygoals}.
 
@@
 Reduction proof is enclosed in Appendix \ref*{appendtheft}.
-\begin{table}[H] 
-	\caption{Security properties achieved by each coin mixing protocol.}
-	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}
-
-		\toprule
-		\hline
-		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
-		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
-		\hline
-		\midrule
-		\textbf{Centralized} & & \\
-		\midrule
-		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
-		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
-		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
-		\midrule
-		\textbf{Decentralized}      &    &      \\
-		\midrule
-		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
-		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
-		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
-		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
-		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
-		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
-		\bottomrule
-	\end{tabular}
-	\label{table:securityproperties}
-\end{table}
-
-\section{Implementation}
-
-\begin{wrapfigure}{r}{0.7\textwidth}
-	\centering
-	\includegraphics[scale=0.7]{./withdrawalComplexity.jpg}
-	\captionsetup{justification=centering}
-	\caption{Gas complexity of withdraw transactions for various trustless Ethereum coin mixers}
-\end{wrapfigure}
-
-We implemented MixEth with two different approaches.
-The first implementation of MixEth does not apply state channels, all the transactions are made on-chain.
-This could lead to unwanted gas costs as the number of corrupted shuffles increases.
-One of our main motivation with MixEth is to provide an efficient and scalable coin mixing protocol which uses as little blockchain resources, storage and gas, as possible.
-Therefore we also implement and evaluate MixEth applying state channels, namely shuffling and challenging a shuffle occurs off-chain and only deposit and withdrawal transactions happen on-chain.
-Both of the implementations allow users to mix Ether or other ERC20-compatible, a popular Ethereum token standard, tokens.
-
-One of the main bottlenecks of coin mixing protocols is the withdrawal transactions' gas costs.
-A Miximus withdrawal transaction burns $\num[group-separator={,}]{1903305}$ gas, regardless of the number of participating parties.
-Since the block gas limit is $\num[group-separator={,}]{8000266}$ as of 2018, October 24 only 4 Miximus withdrawal transactions could fit in one Ethereum block.
-This is even worse for Möbius, since the gas cost for withdrawing coins from a Möbius mixer contract linearly increases with the numbers of participants.
-
-Although MixEth is more gas-efficient than Möbius or Miximus, it incurs a higher time-complexity, ie.
-recipients need to expect longer delays for funds to arrive since each challenging period lasts a few blocks of time.
-Furthermore MixEth requires users to be online during the course of mixing, in some scenarios this might be a demanding requirement.
-
-All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts.
-MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions.
-Note that these implementations are only proof-of-concept implementations, expect further improvements.
-All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.
-
-\subsection{Fully on-chain implementation} \label{fullyonchainimpl}
-
-\begin{wrapfigure}{r}{0.3\textwidth}
-	\centering
-\begin{tikzpicture}[shorten >=1pt,node distance=3cm,on grid,auto] 
-\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
-\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
-\node[state] (q_challenge) [below=of q_shuffle ] {$q_{challenge}$};
-\node[state, accepting below, below=of q_challenge] (q_withdraw) {$q_{withdraw_{k}}$};
-\path[->]
-(q_deposit) edge [loop right] node {$i+1$} ()
-(q_deposit) edge node {$i=N$} (q_shuffle)		
-(q_shuffle) edge node {} (q_challenge)
-(q_challenge) edge [bend right, swap] node {$noFraud, j+1$} (q_shuffle)
-(q_challenge) edge [bend left] node {$fraud, j-1$} (q_shuffle)
-(q_challenge) edge node {$j=N^{'}$} (q_withdraw)
-(q_withdraw) edge [loop right] node {$k+1$} ();
-\end{tikzpicture}
-\captionsetup{justification=centering}
-\caption{Shuffle-and-challenge paradigm implemented for the fully on-chain version of MixEth}
-\label{fig:shuffleandchallenge}
-\end{wrapfigure}
-
-Conceivably mixers would like to minimize off-chain coordination, therefore in our first implementation of the MixEth protocol, we assumed that all transactions will take place on-chain.
-There is only a single off-chain message from receiver to sender, where receiver delivers their public key to the sender.
-The rest of the protocol happens entirely on-chain.
-
-On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element then storing only consumes $\num[group-separator={,}]{5000}$ gas.
-To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage.
-Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against.
-Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract, see Figure \ref{fig:shuffleandchallenge}.
-Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol.
-We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.
-
-A great advantage of the fully on-chain version of MixEth is that it allows dynamic anonymity sets.
-One could potentially deposit funds to the contract and shuffle public keys and leave funds in the mixing contract for indefinite amount of time.
-As soon as the anonymity set is large enough a receiver could withdraw their assets.
-The whole process is represented as a finite automata as shown in Figure \ref{fig:shuffleandchallenge}.
-A receiver in a MixEth contract with $N$ senders could withdraw their funds after $N^{'}$ shuffling rounds, where $N^{'}$ is arbitrary.
-This dynamic nature of the contract could even lead to a single monolithic MixEth contract instead of having multiple MixEth contracts with significantly fragmented anonymity sets.
-A single MixEth contract is able to support the mixing of ether and ERC-20 compatible tokens as well.
-However note that the gas complexity of shuffling transactions grows linearly in the number of participants, therefore the fully on-chain implementation is not capable to support extremely large anonymity sets with participants more than a few hundreds.
-
-Also note that the on-chain cost of a shuffle transaction could be amortized among participants.
-Specifically if there is a group of senders and/or receivers who trust each other they could collectively charge any of them to shuffle once.
-Since they trust their peer, all the rest of the group does not need to shuffle anymore.
-Later non-shufflers could reimburse the only shuffler for their services either on-chain or off-chain.
-
-\begin{wrapfigure}{r}{0.4\textwidth}
-	\centering
-	\begin{tikzpicture}[shorten >=1pt,node distance=4cm,on grid,auto] 
-	\node[state,initial above,initial text=] (q_deposit) {$q_{deposit_{i}}$}; 
-	\node[state] (q_shuffle) [below=of q_deposit ] {$q_{shuffle_{j}}$};
-	\node[state, below=of q_shuffle] (q_no_fraud) {$q_{noFraud_j}$};	\node[state, accepting, right=of q_no_fraud] (q_fraud) {$q_{fraud}$};
-	\node[state, accepting below, below=of q_no_fraud] (q_withdraw) {$q_{withdraw_{k}}$};
-	\path[->]
-	(q_deposit) edge [loop left] node {$i+1$} ()
-	(q_deposit) edge node {$i=N$} (q_shuffle)		
-	(q_shuffle) edge [loop left] node {$j+1$} ()
-	(q_shuffle) edge node {$j=N$} (q_no_fraud)
-	(q_no_fraud) edge node {$j=N$} (q_withdraw)
-	(q_no_fraud) edge [loop left] node {$j+1$} ()
-	(q_no_fraud) edge node {} (q_fraud)
-	(q_withdraw) edge [loop left] node {$k+1$} ();
-	\end{tikzpicture}
-	\captionsetup{justification=centering}
-	\caption{Shuffle-then-challenge paradigm implemented for the channelised version of MixEth}
-	\label{fig:shufflethenchallenge}
-\end{wrapfigure}
-
-\subsection{State channel implementation} \label{statechannelimpl}
-
-We have also adapted MixEth to operate within a state channel.
-We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}.
-This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic.
-Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront.
-In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$.
-To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state.
-The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round.
-In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass.
-In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations.
-To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.
-
-Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic.
-Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic.
-This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle.
-After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round.
-Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.
-If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur.
-In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain.
-A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.
-Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.
-The modified procedure of the MixEth protocol is illustrated as a finite automate in Figure \ref{fig:shufflethenchallenge}.
-Note that all three $N$s are the same.
-In a channelised MixEth contract there are exactly $N$ depositors, $N$ shufflers and $N$ receivers.
-
-\begin{table}[H] 
-	\caption{Proof-of-concept implementation gas cost results.
-Expect further improvements.
-MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
-	\centering 
-	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
-		\toprule
-		\hline
-		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
-		\cline{4-5}&&&Shuffle upload&Challenge\\
-		\hline
-		\midrule
-		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
-		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
-		MixEth&$\num[group-separator={,}]{5395945}$&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{366216}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
-		MixEthChannel&$\num[group-separator={,}]{672276}$&$\num[group-separator={,}]{21000}$&0&0&$\num[group-separator={,}]{26749}$\\
-		\bottomrule
-	\end{tabular}
-	\label{table:gasproperties}
-\end{table}
-
-\section{Related work}
-Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}.
-Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability.
-These properties could be used to evaluate and compare existing and future proposals from a security perspective.
-Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction.
-However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets.
-No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit.
-If more people tried to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit.
-Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract.
-When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient.
-Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.
-
-Miximus is a zkSNARK-based mixer for Ethereum\cite{miximus2018}.
-It uses zkSNARKs to conceal the mapping between depositors and recipients.
-A depositor creates a leaf in a Merkle-tree.
-A depositor needs to exchange the preimage of the leaf with the recipient.
-Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf.
-So called nullifiers enable recipients to withdraw funds once and only once.
-The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants.
-However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction.
-Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK.
-If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer.
-Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.
-
-As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$.
-In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}.
-\begin{table}[H] 
-\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol.
-Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
-\centering 
-\begin{tabular}{lcc}
-
-	\toprule
-	&\#Off-chain messages& \#Transactions \\
-	\midrule
-	\textbf{Centralized} & & \\
-	\midrule
-	Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
-	Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
-	TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
-	\midrule
-	\textbf{Decentralized}      &    &      \\
-	\midrule
-	Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
-	Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
-	XIM \cite{bissias2014sybil} & 0      & 7       \\
-	Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
-	Miximus \cite{miximus2018} & 1+MPC & 2 \\
-	MixEth & 1 & 3 \\
-	MixEthChannel  & $\mathcal{O}(n)$ &2 \\
-	\bottomrule
-\end{tabular}
-\label{table:communicationcomplexity}
-\end{table}
-
-\subsection{Additional related work}
-Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}.
-Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes.
-Later on Aztec notes can be traded in a join-split style confidential transaction, namely the value of the traded Aztec notes are encrypted and not visible to outsiders.
-A join-split style transaction can have multiple inputs and outputs.
-Aztec applies zero-knowledge proofs and range proofs in order to achieve that the sum of inputs traded in a confidential transaction is greater or equal than the sum of outputs.
-The gas cost of a confidential Aztec transaction is $\num[group-separator={,}]{219000}$+$\num[group-separator={,}]{121000}n$+$\num[group-separator={,}]{41000}m$, where $n$ and $m$ are the numbers of inputs and outputs respectively.
-Although Aztec is not a coin mixer, it can be used not only to provide confidential transaction, but also to increase anonymity.
-On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes.
-Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions.
-For instance on top Aztec one could use MixEth to shuffle Aztec notes.
-
-\section{Extensions and improvements}
-MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround.
-A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant.
-MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.
-
-In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
-This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
-
-\section{Acknowledgements}
-Chris Buckland is supported by an Ethereum Foundation
-scaling grant and an Ethereum Community Fund grant.
-We would like to thank Liam Horne for helping with the state channel implementation, Barry WhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
-
-\bibliographystyle{plain}
-\bibliography{sample}
-
-\begin{appendices}
 
 	\section{Proof of Anonymity} \label{appendanon}
-Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
+	Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in Section~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.
 
@@
 $\bdv$ wins the forgeability game if and only if $\adv$ wins their $\textsf{G}^{theft}_{mix,\adv}$ game:
-$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$. This contradicts to the assumption that ECDSA is existentially unforgeable.
+	$$\Pr[\textsf{Forge}_{ECDSA,\bdv}]=\Pr[\textsf{G}^{theft}_{mix, \adv}]=\frac{1}{\lambda^\alpha}, $$ for some fixed $\alpha$.
+This contradicts to the assumption that ECDSA is existentially unforgeable.
+
+\section{Extensions and improvements}
+MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround.
+A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant.
+MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.
+
+In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments.
+This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.
+
+\subsubsection{Ethereum account abstraction}
+Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum.
+When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they cannot do this from a fresh address, since it does not hold any ether.
+Since as of now only the sender of a transaction can pay for the gas fee, users cannot withdraw their funds unless they ask someone to fund their fresh address.
+
+Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}.
+EIP86 permits receivers of a transaction paying the gas fee.
+This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses.
+Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms.
+This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA).
+Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.
+
+\subsection{Minimizing shuffle transactions with trusted execution environments}
+One might effectively minimize the number of necessary shuffling rounds to $1$.
+If a Trusted Execution Environment (TEE), e.g., Intel SGX is used to generate the shuffling transaction, then even a single shuffling transaction would suffice to provide the same level of anonymity as if every participant shuffles the public keys.
+Any of the participants could upload the TEE-generated shuffling transaction, while the MixEth contract could check that indeed the shuffling transaction was generated by a TEE.
+Such a shortcut would make our scheme even more practical and efficient, however it would subsume trust in Intel regarding the security and confidentiality of the TEE.
 

### 2019-04-08 article/main.tex
OASIcs version of paper added

@@
 	\begin{tabular}{cccc}    
-		\begin{minipage}{5cm}
+		\begin{minipage}{8cm}
 			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
 				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
-				C^{'*} \leftarrow cC^{*} \\
+				C^{*}_{new} \leftarrow cC^{*} \\
 				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
-				\pcreturn (PK^{'},C^{'*}) }
+				proof_{ChP}\stackrel{\$}{\leftarrow} generateChaumPedersen(G,cG,C^{*},C^{*}_{new})\\
+				\pcreturn (PK^{'},C^{*}_{new},proof_{ChP}) }
 		\end{minipage}
@@
 		\begin{minipage}{5.7cm}
-			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
-				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
+			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*},proof_{ChP}$)}}{%
+				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*},proof_{ChP})) }
 		\end{minipage}
@@
 
+\subsection{Minimizing shuffling transactions with trusted execution environments}
+One might effectively minimize the number of necessary shuffling rounds to $1$.
+If a Trusted Execution Environment (TEE), e.g., Intel SGX is used to generate the shuffling transaction, then even a single shuffling transaction would suffice to provide the same level of anonymity as if every participant shuffles the public keys.
+Any of the participants could upload the TEE-generated shuffling transaction, while the MixEth contract could check that indeed the shuffling transaction was generated by a TEE.
+Such a shortcut would make our scheme even more practical and efficient, however it would subsume trust in Intel regarding the security and confidentiality of the TEE.
+
 \section{Acknowledgements}
@@
 
+\newpage
 \begin{appendices}
